### 2021-03-05 paper_1.tex
add Bibliography and paper_1

\section{A Unified Framework for Salient Structure Detection by Contour-Guided Visual Search}

\begin{center}
    \author{
    Kai Fu Yang,
    Hui Li,
    Chao-Yi Li,
    and Young-Jie Li,
   \emph{Member}, 
    IEEE
}
\end{center}

\emph{IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL. 25, NO. 8, AUGUST 2016}

### 2021-03-05 paper_1.tex
introduction paper_1

@@
 \emph{IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL. 25, NO. 8, AUGUST 2016}
+
+\subsection{Introduction}
+
+Al fine di poter ridurre la complessità nell’analisi di una scena, viene introdotto un metodo utili a poter rilevare potenziali informazioni , come regioni o oggetti, in maniera  simultanea.
+Tale metodo è detto ”Visual saliency”.
+Prima di introdurre l’argomento, bisogna spiegare quattro tipi di concetti: (1) Fissazioni: riguardano la scena inquadrata dall’occhio umano e vengono utilizzate per confrontare i metodi di previsione delle fissazioni.
+(2) ROI: ogni regione contiene informazioni in cui vi è la difficoltà di separare gli oggetti, come per esempio quelli chiari.
+(3) Oggetti salienti: animali, persone, automobili etc.
+(4) Contorno degli oggetti salienti.
+Il metodo proposto si basa nell’effettuare una Salient Structure (SS) Detection, utile a poter identificare le quattro proprietà precedenti, sia in scene disordinate che in quelle semplici.
+Il framework proposto è nominato CGVS (contour-guided visual search): questo strumento di ricerca visiva individua i target utilizzando due tipi di percorsi: (1) percorso selettivo: vengono rilevati i contorni di ogni oggetto utile per stimare la posizione e le dimensioni delle ROI: (2) percorso non selettivo: possono essere proprietà come il colore, luminaria, consistenza etc.
+Questa strategia di ricerca effettua un’elaborazione parallela su entrambi i percorsi, estrapolando informazioni globali e locali.
+Infine viene applicata un’inferenza Bayesiana per integrare la contour based spatial prior (CBSP), metodo utile a poter estrarre le informazioni sui contorni, e le informazioni locali per poter identificare la salienza di ciascun pixel.

### 2021-03-05 paper_1.tex
paper_1

--- 2021-03-05 paper_1.tex
@@
 \emph{IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL. 25, NO. 8, AUGUST 2016}
+
+\subsection{Introduction}
+In order to reduce the complexity in the analysis of a scene, a useful method is introduced to be able to detect potential information, such as regions or objects, simultaneously.
+This method is called "Visual saliency".
+Before introducing the topic, four types of concepts must be explained: (1) Fixations: they concern the scene framed by the human eye and are used to compare the methods of forecasting fixations.
+(2) ROI: each region contains information where there is difficulty in separating objects, such as clear ones.
+(3) Salient objects: animals, people, cars etc.
+(4) Outline of salient objects.
+The proposed method is based on carrying out a Salient Structure (SS) Detection, useful for identifying the four previous properties, both in disordered and simple scenes.
+The proposed framework is called CGVS (contour-guided visual search): this visual search tool identifies the targets using two types of paths: (1) selective path: the contours of each object are detected, useful for estimating the position and size of the ROI: (2) non-selective path: it can be properties such as color, luminary, texture etc.
+This search strategy carries out parallel processing on both paths, extracting global and local information.
+Finally, a Bayesian inference is applied to integrate the contour based spatial prior (CBSP), a useful method for extracting information on the contours, and local information in order to identify the salience of each pixel.

### 2021-03-05 paper_1.tex
update paper_1

--- 2021-03-05 paper_1.tex
@@
 \emph{IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL. 25, NO. 8, AUGUST 2016}
+
+\subsection{Introduction}
+In order to reduce the complexity in the analysis of a scene, a useful method 
+is introduced to be able to detect potential information, such as regions or 
+objects, simultaneously. This method is called "Visual saliency". Before introducing
+the topic, four types of concepts must be explained: (1)\emph{Fixations}: 
+they concern the scene framed by the human eye and are used to compare 
+the methods of forecasting fixations. (2)\emph{ROI}: each region contains information 
+where there is difficulty in separating objects, such as clear ones.(3)\emph{Salient objects}: 
+animals, people, cars etc. (4) Outline of salient objects. The proposed 
+method is based on carrying out a \emph{Salient Structure (SS) Detection},
+useful for identifying the four previous properties, both in disordered and 
+simple scenes. The proposed framework is called CGVS (contour-guided visual 
+search): this visual search tool identifies the targets using two types of 
+paths: (1)\emph{selective path}: the contours of each object are detected, useful 
+for estimating the position and size of the ROI: (2)\emph{non-selective path}: it 
+can be properties such as color, luminary, texture etc. This search strategy 
+carries out parallel processing on both paths, extracting global and local 
+information. Finally, a Bayesian inference is applied to integrate the contour 
+based spatial prior (CBSP), a useful method for extracting information on 
+the contours, and local information in order to identify the salience of each 
+pixel.

### 2021-03-05 paper_1.tex
update paper_1

--- 2021-03-05 paper_1.tex
@@
 \subsection{Introduction}
-In order to reduce the complexity in the analysis of a scene, a useful method is introduced to be able to detect potential information, such as regions or objects, simultaneously.
-This method is called "Visual saliency".
-Before introducing the topic, four types of concepts must be explained: (1) Fixations: they concern the scene framed by the human eye and are used to compare the methods of forecasting fixations.
-(2) ROI: each region contains information where there is difficulty in separating objects, such as clear ones.
-(3) Salient objects: animals, people, cars etc.
-(4) Outline of salient objects.
-The proposed method is based on carrying out a Salient Structure (SS) Detection, useful for identifying the four previous properties, both in disordered and simple scenes.
-The proposed framework is called CGVS (contour-guided visual search): this visual search tool identifies the targets using two types of paths: (1) selective path: the contours of each object are detected, useful for estimating the position and size of the ROI: (2) non-selective path: it can be properties such as color, luminary, texture etc.
-This search strategy carries out parallel processing on both paths, extracting global and local information.
-Finally, a Bayesian inference is applied to integrate the contour based spatial prior (CBSP), a useful method for extracting information on the contours, and local information in order to identify the salience of each pixel.
+In order to reduce the complexity in the analysis of a scene, a useful method 
+is introduced to detect potential information, such as regions or 
+objects, simultaneously. This method is called "\emph{Visual Saliency}". Before introducing
+the topic, four types of concepts must be explained: (1)\emph{Fixations}: 
+they concern the scene framed by the human eye. They are used to compare 
+the methods of forecasting fixations. (2)\emph{ROI}: each region contains information, 
+such as light or dark objects, which is intended to be separated.(3)\emph{Salient objects}: 
+animals, people, cars etc. (4)\emph{Salient edges}: boundary of each object. The proposed 
+method is based on carrying out a \emph{Salient Structure (SS) Detection},
+useful for identifying the four previous properties, both in cluttered and 
+simple scenes. The proposed framework is called \emph{CGVS (contour-guided visual 
+search)}. This visual search tool identifies the targets using two types of 
+paths: (1)\emph{selective path}: the boundaries of each object are detected, useful 
+for estimating the position and size of the ROI: (2)\emph{non-selective path}: it 
+can be properties such as color, luminary, texture etc. This search strategy 
+carries out parallel processing on both paths, extracting global and local 
+information. Finally, a Bayesian inference is applied to integrate the contour 
+based spatial prior (CBSP), a useful method for extracting information on 
+the boundaries, and local information in order to identify the salience of each 
+pixel.

### 2021-03-06 paper_1.tex
update paper_1
Fixation Prediction

@@
 
-\begin{center}
+\begin{flushright}
     \author{
@@
 }
+\end{flushright}
+
+\begin{center}
+    \emph{IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL. 25, NO. 8, AUGUST 2016}
 \end{center}
-
-\emph{IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL. 25, NO. 8, AUGUST 2016}
 
@@
 pixel.
+
+\subsubsection{\emph{Fixation Prediction}}
+Fixation prediction models aim to calculate salience maps, which are used to 
+identify ROIs. Fixation prediction models provide smooth regions of interest 
+rather than uniform regions that highlight all salient objects. These models 
+only offer the ability to detect the position of potential objects while excluding 
+other features such as surfaces or shapes, which are useful for object 
+detection and recognition. The methods proposed to obtain a salience map 
+are varied and range from the use of Bayesian Framework, to including those 
+for machine learning.

### 2021-03-06 paper_1.tex
salient Object Detection

@@
 for machine learning.
+
+\subsubsection{\emph{Salient Object Detection}}
+Existing methods, useful for extracting salient objects from a scene, rely on 
+the contrast of the local or global region. Object detection is an operation 
+related to the "object proposal" operation which attempts to generate a set 
+of all objects in the scene, regardless of their salience. In this paper Bayesian 
+inference is used to accomplish this task.
+
+\subsubsection{\emph{Bridging the Two Tasks}}

### 2021-03-06 paper_1.tex
add images and any updates

@@
 
-\subsection{Introduction}
+\subsection{INTRODUCTION}
 In order to reduce the complexity in the analysis of a scene, a useful method 
@@
 
+\subsection{RELATED WORK}
+
 \subsubsection{\emph{Fixation Prediction}}
@@
 \subsubsection{\emph{Bridging the Two Tasks}}
+Unlike the existing methods, the proposed one is able to obtain more detailed 
+salient structures in terms of resolution, moreover it is able to operate in 
+conditions in which the scene is simple or complex. Both tasks do not need 
+specific tuning.
+
+\subsection{CONTOUR-GUIDED VISUAL SEARCH MODEL}
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/selective and non-selective pathways.png}
+    \centering
+    \caption{The flowchart of the porposed system}
+    \label{fid: flowchart}
+\end{figure}
+
+The research of the possible potential positions, of the salient structures, is 
+carried out with the help of the contour-based spatial prior (CBSP) process, 
+which uses the contours detected in a non-selective path. At the same time, 
+in the selective path, the local characteristics concerning color, luminance 
+and texture are extracted. The information obtained from the CBSP is inserted 
+into the Bayesian framework for the prediction of the salient structure. 
+Finally, the output of the Bayesian framework will represent the salient structure 
+which will be improved through an iterative procedure applied on the 
+CBSP process. The flowchart of the proposed method is summarized in Fig. 1.
+
+\subsubsection{\emph{Contour-Based Spatial Prior (CBSP)}}

### 2021-03-06 paper_1.tex
CBSP
LLFE

@@
 which will be improved through an iterative procedure applied on the 
-CBSP process. The flowchart of the proposed method is summarized in Fig. 1.
+CBSP process. The flowchart of the proposed method is summarized in Fig. \ref{fid: flowchart}.
 
 \subsubsection{\emph{Contour-Based Spatial Prior (CBSP)}}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/CBSP.png}
+    \centering
+    \caption{CBSP reconstruction}
+    \label{fid: CBSP}
+\end{figure}
+Within the non-selective path, the crucial operation is to calculate the 
+approximate spatial weights of salience based on the distribution of the previously 
+detected contours. In this path there is the problem of determining 
+the local information of each object. The solution to the problem is based 
+on an operation that fills the regions delimited by these contours. A very 
+efficient method proposed in \cite{07478155} result is used for the extraction of the contours.
+An example of CBSP reconstruction is shown in Fig. \ref{fid: CBSP}. Each pixel 
+has a direction represented by a radius $ d_r $ which is equal to $d_r = min (H, W) / 3$, where 
+\emph{H} and \emph{W} correspondingly indicate the width and height of the entire image.
+The diameter divides the circle into two parts where, on each of these, for 
+each pixel belonging to the edge, the average response of the edge (AER) will 
+be calculated. This calculation is useful in deciding which of the two halves 
+will belong to the salient region. Each spatial weight of salience is denoted 
+by $ S_e $, while the added bias is denoted by $ S_c $ and both are normalized in the 
+range of [0,1]. The value, which in turn will be normalized, of CBSP is given by: $$ S_w = S_e + S_c $$
+
+\subsubsection{Low-Level Feature Extraction}
+Features such as color (rgb), luminance (flum) and texture are extracted in 
+parallel. There are complicated regions in a texture that can be represented. 
+For this purpose, the texture channel ($ {f_{ed}} $)  has been introduced, which is 
+useful to better represent the salient regions using the contour density (ED). 
+The texture channel is calculated by using an 11x11 filter that smooths the 
+edges.

### 2021-03-07 paper_1.tex
update
Points

@@
 edges.
+
+\subsubsection{Bayesian Inference With Contour Guidance}
+Bayesian inference gives the possibility to calculate the probability that a 
+pixel x may belong to a salient structure s. This probability is computed as:
+$$ p(x|s) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
+Where $ p(x|s) $ is the probability of a pixel belonging to a salient structure, 
+$ p(x|b) $ is the probability that a pixel belongs to the background, $ p(b)=1-p(s) $,
+finally $ p(s)=Sw $ represents the CBSP value. The implementation 
+details are as follows.
+\begin{enumerate}
+    \item \emph{Predict the size of Potential Structure}: useful for obtaining $ p(x|s) $ and 
+    $ p(x|b) $. This procedure, through a binarization of the map obtained 
+    from $ p(s) $, separates the salient structures from the background, all 
+    through the use of a threshold. This threshold is calculated using the 
+    local parameters (color, luminance, etc.), a percentage not greater than 
+    50\% useful to denote the size of the salient structure, an initial weight 
+    and finally two sets of pixels corresponding to the background and the 
+    foreground (salient structure).
+    \item \emph{Evaluate the Importance of Each Feature}:  
+\end{enumerate}

### 2021-03-09 paper_1.tex
start Experiments

--- 2021-03-06 paper_1.tex
@@
 edges.
+
+\subsubsection{Bayesian Inference With Contour Guidance}
+Bayesian inference gives the possibility to calculate the probability that a 
+pixel x may belong to a salient structure s. This probability is computed as:
+$$ p(s|x) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
+Where $ p(x|s) $ is the probability of a pixel belonging to a salient structure, 
+$ p(x|b) $ is the probability that a pixel belongs to the background, $ p(b)=1-p(s) $,
+finally $ p(s)=Sw $ represents the CBSP value. The implementation 
+details are as follows.
+\begin{enumerate}
+    \item \emph{Predict the size of Potential Structure}: this procedure, through a binarization of the map obtained 
+    from $ p(s) $, separates the salient structures from the background, all 
+    through the use of a threshold. This threshold is calculated using the 
+    local parameters (color, luminance, etc.), a percentage not greater than 
+    50\% useful to denote the size of the salient structure, an initial weight 
+    and finally two sets of pixels corresponding to the background and the 
+    foreground (salient structure).
+    \item \emph{Evaluate the Importance of Each Feature}: a feature is considered important 
+    when the difference between the average pixel values of its 
+    salient structure and those of the background is large enough, i.e. when \emph{$ w_i $} 
+    takes on a satisfiable value.
+    \item \emph{Calculate the Observation Likelihood}:in order to calculate the observed 
+    probabilities, the different color channels \emph{($ f_{lum}, f_{rg}, f_{by}, f_{ed} $)} are used, 
+    and the distribution functions $ p(x_i | S_{T_{opt}}) $ and $ p(x_i | B_{T_{opt}}) $ where $ S_{T_{opt}} $ 
+    represents the set of pixels belonging to the structure salient, while 
+    $ B_{T_{opt}} $ represents the set of pixels belonging to the background.
+    $$ p(x|s) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | S_{T_{opt}}))^{w_i}} $$
+    $$ p(x|b) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | B_{T_{opt}}))^{w_i}} $$
+    \item \emph{Enhance the Salient Structure by Iterating}: the salient structures, at 
+    each instant \emph{t}, with $ t = t_0,…, t_n $, are iteratively improved by applying 
+    a median filter on each of them. In addition, the weight attributed to 
+    the importance of each feature is changed. Finally, the CGVS model 
+    will operate on a set of instants \emph{t}, thus forming the contour-guided 
+    visual search.
+
+\end{enumerate}

### 2021-03-09 paper_1.tex
update Bib

@@
 on an operation that fills the regions delimited by these contours. A very 
-efficient method proposed in \cite{07478155} result is used for the extraction of the contours.
+efficient method proposed in \cite{0747815500} result is used for the extraction of the contours.
 An example of CBSP reconstruction is shown in Fig. \ref{fid: CBSP}. Each pixel 
@@
     visual search.
+\end{enumerate}
 
-\end{enumerate}
+\subsection{EXPERIMENTS}
+The proposed method was evaluated on different datasets. For the fixation 
+prediction the datasets are \cite{0747815530} \cite{0747815531} \cite{0747815579}, while for the salient object detection ..

### 2021-03-09 paper_1.tex
update Bib

@@
 The proposed method was evaluated on different datasets. For the fixation 
-prediction the datasets are \cite{0747815530} \cite{0747815531} \cite{0747815579}, while for the salient object detection ..
+prediction the datasets are \cite{0747815530} \cite{0747815531} \cite{0747815579}, while for the salient object detection \cite{0747815506} \cite{0747815508} \cite{0747815518}

### 2021-03-11 paper_1.tex
next

--- 2021-03-09 paper_1.tex
@@
 The proposed method was evaluated on different datasets. For the fixation 
-prediction the datasets are \cite{0747815530} \cite{0747815531} \cite{0747815579}, while for the salient object detection ..
+prediction the datasets are \cite{0747815530} \cite{0747815531} \cite{0747815579}, while for the salient object detection \cite{0747815506} \cite{0747815508} \cite{0747815518}.
+
+\subsubsection{\emph{Basic Property of the Proposed Model}}
+The proposed system allows to carry out a multiple search of objects. In 
+comparison to the work of Itti et al. \cite{0747815505} the proposed system is able to detect, 
+after several iterations, the region and therefore the salient object.
+
+\subsubsection{\emph{Fixation Prediction}}
+Several proposed methods, such as the CA, in order to increase the ROC 
+index, aim to have a first fixation that is limited to having a central prior 
+in the scene. On the other hand, this method will lose information on surrounding 
+objects. In the proposed method, the computation of the CBSP 
+takes into account this center prior, without however losing the information 
+on the other objects in the scene.

### 2021-03-11 paper_1.tex
update

@@
 \subsubsection{\emph{Fixation Prediction}}
+The prediction of fixation indicates the likelihood with which a human is 
+looking at a given position in the scene. There are several metrics that are 
+used to evaluate the prediction such as Natural Scanpath Saliency (NSS) 
+and ROC (AUC). In the following article the ROC method is mainly used, 
+on three types of datasets, to compare the proposed system with o already 
+existing at the state of the art, as shown in Fig. \ref{fig: ROC}.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/ROC.png}
+    \centering
+    \caption{ROC comparison}
+    \label{fig: ROC}
+\end{figure}
+
 Several proposed methods, such as the CA, in order to increase the ROC 
@@
 on the other objects in the scene.
+
+\subsubsection{\emph{Salient Object Detection}}

### 2021-03-11 paper_1.tex
update Bib

@@
 
-Several proposed methods, such as the CA, in order to increase the ROC 
+Several proposed methods, such as the CA \cite{0747815502}, in order to increase the ROC 
 index, aim to have a first fixation that is limited to having a central prior 

### 2021-03-11 paper_1.tex
finish Salient Object Detection

@@
     \centering
-    \includegraphics[width = 0.8\linewidth]{images/selective and non-selective pathways.png}
+    \includegraphics[width = 0.8\linewidth]{images/paper1/selective and non-selective pathways.png}
     \centering
@@
     \centering
-    \includegraphics[width = 0.8\linewidth]{images/CBSP.png}
+    \includegraphics[width = 0.8\linewidth]{images/paper1/CBSP.png}
     \centering
@@
     \centering
-    \includegraphics[width = 1 \linewidth]{images/ROC.png}
+    \includegraphics[width = 1 \linewidth]{images/paper1/ROC.png}
     \centering
@@
 \subsubsection{\emph{Salient Object Detection}}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper1/metrics.png}
+    \centering
+    \caption{Metrics comparison}
+    \label{fig: metrics}
+\end{figure}
+To compare the performance of the salient object detection, metrics such 
+as Precision, Recall, F-score, Weighted F-score and MAE (Mean Absolute 
+Error) were used on three types of datasets (ASD, ECSSD, PASCALS). The 
+results showed that for the first two metrics (P-R), systems such as HS and 
+RF are the best, while for the F-score the proposed method is able to consider 
+a greater range of thresholds. As it can be seen, in these two metrics the 
+proposed system (CGVS (t2)) considers the central bias unlike the others. 
+If the central bias were not considered, the results decrease but are still 
+satisfactory (CGVS ''). However, in the remaining two metrics, the proposed 
+system is the best, except in the PASCALS dataset where the best is the RF 
+method.

### 2021-03-12 paper_1.tex
1.4.4

@@
 a greater range of thresholds. As it can be seen, in these two metrics the 
-proposed system (CGVS (t2)) considers the central bias unlike the others. 
+proposed system (\emph{CGVS($ t_2 $)}) considers the central bias unlike the others. 
 If the central bias were not considered, the results decrease but are still 
-satisfactory (CGVS ''). However, in the remaining two metrics, the proposed 
+satisfactory (\emph{CGVS''}). However, in the remaining two metrics, the proposed 
 system is the best, except in the PASCALS dataset where the best is the RF 
 method.
+
+\subsubsection{\emph{Between Saliency Map and Salient Object}}
+Most fixation prediction methods perform poorly when used to detect salient 
+objects. To solve this problem, a two-dimensional Gaussian distribution is 
+applied to each salience map derived from any method. The derived output 
+will be used as an initial CBSP from which the salient objects can be 
+extracted with the previously proposed calculations. The metrics, used to 
+measure the performance of the different methods, improve if the methods 
+replace their salience map with CBSP.

### 2021-03-12 paper_1.tex
1.4.5

@@
 replace their salience map with CBSP.
+
+\subsubsection{\emph{Extended Saliency-Related Applications}}
+The peculiarity of the proposed method also lies in the search for salient 
+edges. This process is possible by replacing the four color components with 
+three luminance gradients and two color-opponent channels. The system also 
+proves to be capable of being able to detect text as well.

### 2021-03-12 paper_1.tex
1.4.6

@@
 proves to be capable of being able to detect text as well.
+
+\subsubsection{\emph{Robustness to Parameters}}
+In order to test the robustness of the model, parameters $ d_r $ and $ \sigma_c $ were used 
+in various ranges of $ \{ 1/2, 1/3, 1/4, 1/5, 1/6 \} * min(W,H) $,useful to obtain the 
+CBSP. Parameter changes do not cause performance degradation, but show 
+that the model is robust across different datasets. Threshold-based selection 
+of the object size is a method that still needs to be adapted to the type of 
+scene.

### 2021-03-12 paper_1.tex
End paper1

--- 2021-03-12 paper_1.tex
@@
     \centering
-    \caption{CBSP reconstruction}
+    \caption{CBSP reconstruction.}
     \label{fid: CBSP}
@@
     \centering
-    \caption{ROC comparison}
+    \caption{ROC comparison.}
     \label{fig: ROC}
@@
     \centering
-    \caption{Metrics comparison}
+    \caption{Metrics comparison.}
     \label{fig: metrics}
@@
 proves to be capable of being able to detect text as well.
+
+\subsubsection{\emph{Robustness to Parameters}}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 0.6 \linewidth]{images/paper1/bad threshold.png}
+    \centering
+    \caption{Incorrect estimation.}
+    \label{fig: Incorrect}
+\end{figure}
+In order to test the robustness of the model, parameters $ d_r $ and $ \sigma_c $ were used 
+in various ranges of $ \{ 1/2, 1/3, 1/4, 1/5, 1/6 \} * min(W,H) $,useful to obtain the 
+CBSP. Parameter changes do not cause performance degradation, but show 
+that the model is robust across different datasets. However, the 
+selection of the object size, based on the threshold, is a method that still 
+needs to be adapted to the type of scene. A wrong choice of value could lead 
+to not considering some important parts of the objects (Fig.\ref{fig: Incorrect}).
+
+\subsection{DISCUSSION}
+The proposed model searches for salient structures and associated objects 
+without using tools, such as the superpixel technique, adopted by other methods. 
+The system can be extended by introducing other local features such as 
+(e.g., depth, motion, etc.) to be used also in video processing. It is possible 
+to carry out an analysis of the scene using unsupervised learning methods. 
+Finally, this method offers a dual use. In a cluttered scene with no dominant 
+objects, the system will function as a fixation prediction model. On the other 
+hand, with simple scenes, the system reveals the existing dominant objects.

### 2021-03-12 paper_1.tex
End paper1

@@
 the topic, four types of concepts must be explained: (1)\emph{Fixations}: 
-they concern the scene framed by the human eye. They are used to compare 
-the methods of forecasting fixations. (2)\emph{ROI}: each region contains information, 
-such as light or dark objects, which is intended to be separated.(3)\emph{Salient objects}: 
+they concern the scene framed by the human eye (ground-truth), used to benchmark 
+fixation prediction methods. (2)\emph{ROI}: each region contains information, such 
+as light or dark objects, which is intended to be separated.(3)\emph{Salient objects}: 
 animals, people, cars etc. (4)\emph{Salient edges}: boundary of each object. The proposed 
@@
 search)}. This visual search tool identifies the targets using two types of 
-paths: (1)\emph{selective path}: the boundaries of each object are detected, useful 
-for estimating the position and size of the ROI: (2)\emph{non-selective path}: it 
+pathsways: (1)\emph{selective pathway}: the boundaries of each object are detected, useful 
+for estimating the position and size of the ROI: (2)\emph{non-selective pathway}: it 
 can be properties such as color, luminary, texture etc. This search strategy 
@@
 information. Finally, a Bayesian inference is applied to integrate the contour 
-based spatial prior (CBSP), a useful method for extracting information on 
-the boundaries, and local information in order to identify the salience of each 
-pixel.
+based spatial prior (CBSP), and local information in order to identify 
+the salience of each pixel.
 
@@
     \centering
-    \caption{The flowchart of the porposed system}
+    \caption{The flowchart of the porposed system.}
     \label{fid: flowchart}
@@
 the local information of each object. The solution to the problem is based 
-on an operation that fills the regions delimited by these contours. A very 
-efficient method proposed in \cite{0747815500} result is used for the extraction of the contours.
+on an operation that fills the regions delimited by these contours \cite{0747815567}. A very 
+efficient method proposed in \cite{0747815570} result is used for the extraction of the contours.
 An example of CBSP reconstruction is shown in Fig. \ref{fid: CBSP}. Each pixel 
@@
 will belong to the salient region. Each spatial weight of salience is denoted 
-by $ S_e $, while the added bias is denoted by $ S_c $ and both are normalized in the 
-range of [0,1]. The value, which in turn will be normalized, of CBSP is given by: $$ S_w = S_e + S_c $$
+by $ S_e $, while the added center-bias, which is modeled by a Gussian 
+mask having standard deviation as $ \sigma_c = min (H, W) / 3 $, is denoted by $ S_c $ and 
+both are normalized in the range of [0,1]. The value, which in turn will be 
+normalized, of CBSP is given by: $$ S_w = S_e + S_c $$
 
 \subsubsection{Low-Level Feature Extraction}
-Features such as color (rgb), luminance (flum) and texture are extracted in 
-parallel. There are complicated regions in a texture that can be represented. 
-For this purpose, the texture channel ($ {f_{ed}} $)  has been introduced, which is 
-useful to better represent the salient regions using the contour density (ED). 
-The texture channel is calculated by using an 11x11 filter that smooths the 
-edges.
+In the selective path, features such as complementary colors ($ f_{rg} = r-g$, 
+$ f_{by} = b-(r+g)/2 $), luminance ($ f_{lum} = (r+g+b)/3 $) and texture are 
+extracted. In addition, the density of the edges ($ f_{ed} $) is extracted, useful to 
+represent the level of density of the edges, smoothed by a median filter of 
+11x11 pixels.
 
@@
 Bayesian inference gives the possibility to calculate the probability that a 
-pixel x may belong to a salient structure s. This probability is computed as:
+pixel \emph{x} may belong to a salient structure \emph{s}. This probability is computed as:
 $$ p(s|x) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
@@
 \begin{enumerate}
-    \item \emph{Predict the size of Potential Structure}: this procedure, through a binarization of the map obtained 
-    from $ p(s) $, separates the salient structures from the background, all 
-    through the use of a threshold. This threshold is calculated using the 
-    local parameters (color, luminance, etc.), a percentage not greater than 
-    50\% useful to denote the size of the salient structure, an initial weight 
-    and finally two sets of pixels corresponding to the background and the 
-    foreground (salient structure).
+    \item \emph{Predict the size of Potential Structure}: this procedure, through a binarization 
+    of the map obtained from $ p(s) $, separates the salient structures 
+    from the background, all through the use of a threshold. This 
+    threshold is calculated using local parameters (color, luminance, etc.), 
+    a threshold $ T_k $ no greater than 50\% of the size of the entire image, useful 
+    for denoting the size of the salient structure, an initial non-zero 
+    weight and finally two sets of pixels ($ B_{T_k}$ , $ S_{T_k}$) corresponding to the background 
+    and foreground (salient structure).
     \item \emph{Evaluate the Importance of Each Feature}: a feature is considered important 
     when the difference between the average pixel values of its 
-    salient structure and those of the background is large enough, i.e. when \emph{$ w_i $} 
+    salient structure and those of the background is large enough, i.e. when $ w_i $ 
     takes on a satisfiable value.
@@
 \subsubsection{\emph{Basic Property of the Proposed Model}}
-The proposed system allows to carry out a multiple search of objects. In 
-comparison to the work of Itti et al. \cite{0747815505} the proposed system is able to detect, 
-after several iterations, the region and therefore the salient object.
+In comparison to the work of Itti et al. \cite{0747815505} the proposed system is able to:
+\begin{enumerate}
+    \item Automatically select the size of potential salient structures and assign them a weight;
+    \item Detect multiple objects in a scene;
+    \item Include an iterative process that improves research;
+\end{enumerate}
 
 \subsubsection{\emph{Fixation Prediction}}
-The prediction of fixation indicates the likelihood with which a human is 
+The fixation prediction indicates the likelihood with which a human is 
 looking at a given position in the scene. There are several metrics that are 
@@
 and ROC (AUC). In the following article the ROC method is mainly used, 
-on three types of datasets, to compare the proposed system with o already 
+on three types of datasets, to compare the proposed system with others already 
 existing at the state of the art, as shown in Fig. \ref{fig: ROC}.
@@
 \subsubsection{\emph{Salient Object Detection}}
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width = 1 \linewidth]{images/paper1/metrics.png}
-    \centering
-    \caption{Metrics comparison.}
-    \label{fig: metrics}
-\end{figure}
 To compare the performance of the salient object detection, metrics such 
@@
 system is the best, except in the PASCALS dataset where the best is the RF 
-method.
+method (Fig. \ref{fig: metrics}).
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper1/metrics.png}
+    \centering
+    \caption{Metrics comparison.}
+    \label{fig: metrics}
+\end{figure}
 
@@
 will be used as an initial CBSP from which the salient objects can be 
-extracted with the previously proposed calculations. The metrics, used to 
-measure the performance of the different methods, improve if the methods 
-replace their salience map with CBSP.
+extracted with the previously proposed calculations.
 
@@
 three luminance gradients and two color-opponent channels. The system also 
-proves to be capable of being able to detect text as well.
+provide excellent text detection.
 
@@
 \subsection{DISCUSSION}
-The proposed model searches for salient structures and associated objects 
-without using tools, such as the superpixel technique, adopted by other methods. 
-The system can be extended by introducing other local features such as 
-(e.g., depth, motion, etc.) to be used also in video processing. It is possible 
-to carry out an analysis of the scene using unsupervised learning methods. 
-Finally, this method offers a dual use. In a cluttered scene with no dominant 
-objects, the system will function as a fixation prediction model. On the other 
-hand, with simple scenes, the system reveals the existing dominant objects.
+The proposed model is able to search for different salient structures and the 
+objects inside them, without using tools, such as the superpixel technique, 
+adopted by other methods. The system can be extended by introducing 
+other local features such as (e.g., depth, motion, etc.) to be used also 
+in video processing. It is possible to carry out an analysis of the scene 
+using unsupervised learning methods. Finally, this method offers a dual use. In 
+a cluttered scene with no dominant objects, the system will function as a 
+fixation prediction model. Finally, on the other hand, with simple scenes, 
+the system detects existing relevant objects.

### 2021-03-12 paper_1.tex
End seriously paper1

@@
 \subsubsection{Low-Level Feature Extraction}
-In the selective path, features such as complementary colors ($ f_{rg} = r-g$, 
-$ f_{by} = b-(r+g)/2 $), luminance ($ f_{lum} = (r+g+b)/3 $) and texture are 
-extracted. In addition, the density of the edges ($ f_{ed} $) is extracted, useful to 
-represent the level of density of the edges, smoothed by a median filter of 
-11x11 pixels.
+In the selective path, features such as complementary colors ($ f_{rg}, f_{by}$), luminance 
+($ f_{lum} $) and texture are extracted. In addition, the density of the 
+edges ($ f_{ed} $) is extracted, useful to represent the level of density of the edges, 
+smoothed by a median filter of 11x11 pixels.
+$$ f_{rg} = r-g $$
+$$ f_{by} = b-(r+g)/2 $$
+$$ f_{lum} = (r+g+b)/3 $$
 
@@
     and foreground (salient structure).
+    $$ T_{opt} = \argmax\limits_{T_k} \sqrt{\sum_{i} (\omega_i^0*(\tilde{S}^i_{T_{k}}) - (\tilde{B}^i_{T_{k}}))^2} $$
     \item \emph{Evaluate the Importance of Each Feature}: a feature is considered important 
     when the difference between the average pixel values of its 
-    salient structure and those of the background is large enough, i.e. when $ w_i $ 
+    salient structure and those of the background is large enough, i.e. when $ \omega_i $ 
     takes on a satisfiable value.
+    $$ \omega_i = \frac{1}{\mu} * | \tilde{S}^i_{T_{opt}} - \tilde{B}^i_{B_{opt}} |$$
     \item \emph{Calculate the Observation Likelihood}:in order to calculate the observed 

### 2021-03-14 slides.tex
add Slides

\documentclass{beamer}
\usepackage{graphicx}

\title[short]{INTELLIGENT SYSTEMS}
\author{Flavio Forenza}\vspace{10pt}
\institute{mat. 938367}

\date{}

\usetheme{Darmstadt}
\begin{document}

\begin{frame}
    \maketitle
    \begin{center}
        \includegraphics[width = 0.4\linewidth ]{images/logoUnimi.png}   
    \end{center}
\end{frame}

\begin{frame}
    %\frametitle{Roadm}
    ciao  
\end{frame}

\end{document}

### 2021-03-15 slides.tex
layout slides
start paper1

@@
 \usepackage{graphicx}
+\graphicspath{{images/}}
+
+\setbeamertemplate{footline}[frame number]
+\setbeamertemplate{page number in head/foot}[appendixframenumber]
+
+\usetheme{Darmstadt}
 
 \title[short]{INTELLIGENT SYSTEMS}
-\author{Flavio Forenza}\vspace{10pt}
-\institute{mat. 938367}
+\author[Flavio Forenza]{Flavio Forenza \\ \tiny flavio.forenza@studenti.unimi.it\\[5mm] \includegraphics[scale = 0.06]{logoUnimi2.png}}
+\institute{Department of Computer Science,\\ University of Milan, Italy}
+\date{\tiny \today}
 
-\date{}
-
-\usetheme{Darmstadt}
 \begin{document}
@@
     \maketitle
-    \begin{center}
-        \includegraphics[width = 0.4\linewidth ]{images/logoUnimi.png}   
-    \end{center}
 \end{frame}
 
+\logo{\includegraphics[width=0.1\linewidth]{logoUnimi2.png}}
+\section{Paper 1}
+\subsection{\emph{"A Unified Framework for Salient StructureDetection by Contour-Guided Visual Search"}}
 \begin{frame}
-    %\frametitle{Roadm}
-    ciao  
+    \frametitle{INTRODUCTION}
+
 \end{frame}

### 2021-03-15 slides.tex
try to add bib

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{bibentry}
+
 \graphicspath{{images/}}
-
 \setbeamertemplate{footline}[frame number]
 \setbeamertemplate{page number in head/foot}[appendixframenumber]
-
 \usetheme{Darmstadt}
@@
     \frametitle{INTRODUCTION}
+    The purpose of the paper is to introduce a new method, in the 
+    state of the art, which is able to identify regions and salient objects 
+    within a scene simultaneously. The proposed system attempts to 
+    bridge the gap between the two highly related tasks of \emph{"human 
+    fixation"} prediction and \emph{"salient object detection"}, with a general 
+    framework.
+\end{frame}
 
+\begin{frame}{RELATED WORK}
+    To obtain the final result, two pathways are crossed (Fig.\ref{fid: flowchart}):
+    \begin{enumerate}
+        \item Selective
+        \item Non-Selective
+    \end{enumerate}
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 0.8\linewidth]{images/paper1/selective and non-selective pathways.png}
+        \centering
+        \caption{The flowchart of the porposed system.}
+        \label{fid: flowchart}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{CONTOUR-GUIDED VISUAL SEARCH MODEL}
+    In Non-Selective pathway are computed:
+    \begin{enumerate}
+        \item \emph{Contours} $\footnotemark $
+        \item \emph{Contour-Based Spatial Prior} $ \rightarrow d_r = min (H, W) / 3$
+    \end{enumerate}
+    \bibliographystyle{abbrv}
+    \bibliography{Bibliography}
+    \footnotetext{\cite{0747815518}}
 \end{frame}

### 2021-03-15 slides.tex
ok cites in same slide
update slide

@@
-\documentclass{beamer}
+\documentclass[10pt]{beamer}
 \usepackage{graphicx}
@@
 \usepackage{bibentry}
+\usepackage{biblatex}
+\setbeamertemplate{caption}[numbered]
+\bibliography{Bibliography}
 
@@
 
-\begin{frame}{CONTOUR-GUIDED VISUAL SEARCH MODEL}
-    In Non-Selective pathway are computed:
+\begin{frame}[t]{CONTOUR-GUIDED VISUAL SEARCH MODEL pt1}
+    In \emph{Non-Selective} pathway are computed:
     \begin{enumerate}
-        \item \emph{Contours} $\footnotemark $
-        \item \emph{Contour-Based Spatial Prior} $ \rightarrow d_r = min (H, W) / 3$
+        \item \emph{Boundary} \footfullcite{0747815570}
+        \item \emph{Contour-Based Spatial Prior (CBSP)} $ \rightarrow S_w = S_e + S_c $
     \end{enumerate}
-    \bibliographystyle{abbrv}
-    \bibliography{Bibliography}
-    \footnotetext{\cite{0747815518}}
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 0.5\linewidth]{images/paper1/CBSP.png}
+        \centering
+        \caption{CBSP reconstruction.}\vspace{0mm}
+        \label{fid: CBSP}
+    \end{figure}
+    In \emph{Selective} pathway are computed the basic low-level features:
+    \begin{enumerate}
+        \item \emph{Luminance} $ \rightarrow f_{lum} = (r+g+b)/3 $
+        \item \emph{Color-Opponent} $ \rightarrow f_{rg} = r-g , f_{by} = b-(r+g)/2 $
+        \item \emph{Texture Channel} ($ f_{ed} $)
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}[t]{CONTOUR-GUIDED VISUAL SEARCH MODEL pt2}
+    \begin{block}{Bayesian inference}
+        All the previous informations are used to compute the Bayesian inference:
+        $$ p(s|x) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
+    \end{block}
+    Where:
+    \begin{enumerate}
+        \item $ p(x|s) \rightarrow $ likelihood of a pixel at \emph{x} belonging to a salient structure \emph{s}
+        \item $ p(x|b) \rightarrow $ likelihood of a pixel at \emph{x} belonging to the background \emph{b}
+        \item $ p(s) \mbox{ and } p(b)=1-p(s) \rightarrow $ prior probabilities of a pixel at x belonging to a salient structure and the background, respectively.
+    \end{enumerate}
 \end{frame}

### 2021-03-15 slides.tex
finish contour

@@
     \frametitle{INTRODUCTION}
-    The purpose of the paper is to introduce a new method, in the 
+    The purpose of the paper is to introduce a new method, called CGVS in the 
     state of the art, which is able to identify regions and salient objects 
@@
 
+\begin{frame}{CONTOUR-GUIDED VISUAL SEARCH MODEL pt3}
+    To compute the prior probabilities, we need:
+    \begin{enumerate}
+        \item \emph{Predict the Size of Potential Structure}: using a optimal threshold ($ T_{opt} $) 
+        useful for separating the background from the foreground (salient structures).
+        \item \emph{Evaluate the Importance of Each Feature}: weighing every salient structure.
+        \item \emph{Calculate the Observation Likelihood:} both $ p(x|s) \mbox{ and } p(x|b) $
+        \item \emph{Enhance the Salient Structure by Iterating}: we re-initialize the prior 
+        function with the smoothed version of $ p(s|x) $ (by median filtering 
+        with a size of 21 × 21 pixels)
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}{EXPERIMENTS}
+
+\end{frame}
+
 \end{document}

### 2021-03-15 slides.tex
finish slides paper1

@@
 
-\begin{frame}{EXPERIMENTS}
+\begin{frame}[t]{EXPERIMENTS}
+    The results obtained on different datasets \footfullcite{PASCAL-S, ECSSD, ASD}, were compared with those 
+    btained by the systems already existing at the state of the art.
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 0.8 \linewidth]{/paper1/metrics.png}
+        \centering
+        \caption{Metrics comparison.}
+        \label{fig: metrics}
+    \end{figure}
+\end{frame}
 
+\begin{frame}{DISCUSSION}
+    It is necessary to say that the results obtained by the proposed method 
+    are obtained using the center bias, which if removed places the system 
+    performance under those of systems such as \emph{RF} \footfullcite{0747815518} and \emph{HS}\footfullcite{0747815508} (which do not 
+    use the central bias). This method offers a dual use. In 
+    a cluttered scene with no dominant objects, the system will function as a 
+    fixation prediction model. Finally, on the other hand, with simple scenes, 
+    the system detects existing relevant objects.
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 0.7 \linewidth]{paper1/SystemsComp.png}
+        \centering
+        \label{fig: metrics}
+    \end{figure}
 \end{frame}

### 2021-03-15 slides.tex
prova

@@
 \subsection{\emph{"A Unified Framework for Salient StructureDetection by Contour-Guided Visual Search"}}
-\begin{frame}
-    \frametitle{INTRODUCTION}
+\begin{frame}{INTRODUCTION}
     The purpose of the paper is to introduce a new method, called CGVS in the 
@@
 
+\section{Paper 2}
+\begin{frame}
+
+\end{frame}
+
 \end{document}

### 2021-03-17 paper_2.tex
start paper_2

\section{Linear Spectral Clustering Superpixel}

\begin{flushleft}
    \author{
    Jiansheng Chen, 
    \emph{Member, IEEE}, 
    Zhengqin Li,
    \emph{Student Member, IEEE}, 
    Bo Huang 
}
\end{flushleft}

### 2021-03-17 paper_2.tex
finish introduction

@@
 \end{flushleft}
+
+\begin{center}
+    \emph{IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL. 26, NO. 7, JULY 2017}
+\end{center}
+
+\subsection{INTRODUCTION}
+The introduced technique is called SUPERPIXEL. Widely used in image 
+processing for particular tasks such as image segmentation, image analysis, 
+image classification, target tracking, 3D reconstruction, surface retrieval and 
+object proposal. The purpose of this technique is to be able to group the 
+pixels into groups that delimit the edges of an object in order to be able 
+to extract its content. Compared to other methods already existing in the 
+state of the art, characteristics such as size, number of superpixels and shape 
+are not considered. The purpose of the elaborate story is to reduce the 
+computational complexity. The three targets that must be satisfied by each 
+superpixel algorithm are:
+\begin{enumerate}
+    \item Adhere well to the edges without forming overlaps on objects;
+    \item Have a pre-processing technique useful to improve efficiency;
+    \item Consider global information.
+\end{enumerate}
+The proposed system, called Linear Spectral Clustering (LSC), manages to 
+satisfy all the previous points with a high memory efficiency. In LSC, each 
+pixel is mapped to a point within a ten-dimensional space of characteristics 
+in which the weighted K-means is applied for segmentation.

### 2021-03-18 paper_2.tex
finish Mathematical Backgrounds

@@
 in which the weighted K-means is applied for segmentation.
+
+\subsection{LSC SUPERPIXEL}
+The task of LSC is to discover the relationships that exist between the objective 
+functions ($ F_{N_{cuts}} $) (\ref{FNcuts}), of the normalized cuts, and the objective functions 
+of the weighted K-means ($ F_{km}$) (\ref{Fkm}). 
+\begin{equation} \label{Fkm}
+    F_{km} = \sum_{k=1}^K\sum_{p\in\pi_k}\omega(p)= || \phi(p)-m_k ||^2 
+\end{equation}
+\begin{equation} \label{Centroid}
+    m_k = \frac{\sum_{q\in\pi_k}\omega(q)\phi(q)}{\sum_{q\in\pi_k}\omega(q)}
+\end{equation}
+\begin{equation} \label{FNcuts}
+    F_{N_{cuts}} = \frac{1}{K}\sum_{k=1}^K\frac{\sum_{p\in\pi_k}\sum_{q\in\pi_k}W(p,q)}{\sum_{p\in\pi_k}\sum_{q\in{V}}W(p,q)}
+\end{equation}
+Where $ m_k $ (\ref{Centroid}) represent the average point, or centroid, of each cluster. Within 
+the formulation of normalized cuts, each data Point corresponds to a node 
+within a graph \emph{G = (V, E, W)} where \emph{V} is the set of all nodes, \emph{E} represents 
+the set of all edges connected and \emph{W} represents the result returned by a 
+similarity function between nodes. The criterion of normalized cuts is based 
+on maximizing the $ F_{N_{cuts}} $ function. The minimization or maximization problems 
+are called \emph{optimization problems} which can be solved by using a positive kernel of 
+a matrix. To see the relationship between the two functions, the Dhillon's concept \cite{0781426526} is extended, to obtain {\bfseries Corollary 1}:
+
+\begin{corollary} 
+    Optimizations of the objective functions of the weighted K-means
+    and the normalized cuts are mathematically equivalent if (\ref{eq4}) and (\ref{eq5}) 
+    hold simultaneously. The symbol $ \cdot $ stands for inner product.
+\end{corollary}
+
+\begin{equation} \label{eq4}
+    \omega(p)\pi(p) \cdot \omega(q)\pi(q) = W(p,q), \forall p,q \in V
+\end{equation}
+
+\begin{equation} \label{eq5}
+    w(p) = \sum_{q \in V} W(p,q), \forall p \in V
+\end{equation}
+
+After making various derivative calculations, $ F_{km} $ can be seen as: 
+\begin{equation}
+    F_{km} = C - K * F_{N_{cuts}} 
+\end{equation}
+
+From the above definition it is possible to note that the minimization of 
+$ F_{km} $ is equivalent to the maximization of $ F_{N_{cuts}} $. Specifically, both $ F_{km} $ and 
+$ F_{km} $ perform an identical partitioning of the n-dimensional space defined by 
+the function $ \phi $.

### 2021-03-18 paper_2.tex
fix Corollary

@@
 are called \emph{optimization problems} which can be solved by using a positive kernel of 
-a matrix. To see the relationship between the two functions, the Dhillon's concept \cite{0781426526} is extended, to obtain {\bfseries Corollary 1}:
+a matrix. To see the relationship between the two functions, the Dhillon's concept \cite{0781426526} is extended, to obtain {\bfseries Corollary \ref{Corollary1}}:
 
-\begin{corollary} 
+\begin{corollary} \label{Corollary1}
     Optimizations of the objective functions of the weighted K-means

### 2021-03-18 paper_2.tex
fix introduction LSC SUP

@@
 \subsection{LSC SUPERPIXEL}
+The study focuses on the relationships between the results returned by the 
+optimization functions, and those returned by two other equations. If the results 
+are equivalent, then weighted k-means clustering can replace the highly 
+complex eigen based method.
+
+\subsubsection{Mathematical Backgrounds}
 The task of LSC is to discover the relationships that exist between the objective 
@@
 the function $ \phi $.
+
+\subsubsection{LSC Algorithm}

### 2021-03-26 paper_2.tex
2 paper continue

@@
 \subsubsection{LSC Algorithm}
+The purpose of LSC is to find the correct positive function W (p, q) in order 
+to satisfy {\emph{Corollary \ref{Corollary1}}}. To achieve this, the Euclidean distance calculation 
+was used as an index of similarity between two pixels. Each pixel \emph{p} is represented 
+by five dimensional vectors \emph{(l, a, b, x, y)} in the CIELAB color space, where \emph{l} 
+epresents brightness, \emph{a} and \emph{b} represent opposite colors and \emph{x} and \emph{y} represent
+the coordinates of the plane. The similarity function, in order to satisfy 
+the positivity condition required by (\ref{eq4}), is extended as a convergent Fourier series:
+
+\begin{multline}
+    W(p,q) = C_s^2(\cos \frac{\pi}{2}(x_p-x_q)+\cos\frac{\pi}{2}(y_p-y_q)) \\
+    \leftarrow + C_c^2(\cos \frac{\pi}{2}(l_p-l_q)+\cos\frac{\pi}{2}(\alpha_p-\alpha_q) \\
+    + \cos\frac{\pi}{2}(\beta_p-\beta_q)x2.55^2) 
+\end{multline}

### 2021-03-26 paper_2.tex
finish intro 2.3

@@
 the positivity condition required by (\ref{eq4}), is extended as a convergent Fourier series: 
+\begin{equation}
+    \begin{split}
+        W(p,q) = C_s^2(\cos \frac{\pi}{2}(x_p-x_q)+\cos\frac{\pi}{2}(y_p-y_q)) \\
+        + C_c^2(\cos \frac{\pi}{2}(l_p-l_q)+\cos\frac{\pi}{2}(\alpha_p-\alpha_q) \\
+        + \cos\frac{\pi}{2}(\beta_p-\beta_q)x2.55^2)
+    \end{split}
+\end{equation}
+The mapping function that maps a point in a ten-dimensional space is as follows:
+\begin{equation}
+    \begin{split}
+        \phi(p) = \frac{1}{\omega(p)}[C_c\cos\frac{\pi}{2}l_p, C_c\sin\frac{\pi}{2}l_p, 2.55C_c\cos\frac{\pi}{2}\alpha_p \\
+        x 2.55C_c\sin\frac{\pi}{2}\alpha_p, 2.55C_c\cos\frac{\pi}{2}\beta_p, 2.55C_c\sin\frac{\pi}{2}\alpha_p, \\
+        x C_s\cos\frac{\pi}{2}x_p, C_s\sin\frac{\pi}{2}x_p, C_s\cos\frac{\pi}{2}y_p, C_s\sin\frac{\pi}{2}x_p]
+    \end{split}
+\end{equation}
+In the defined space, the weighted K-mean clustering as well as being 
+equivalent to the Fncuts optimization function, creates the optimal context to 
+optimize it. The LCS algorithm takes two parameters as input; The image 
+to be segmented and the preferred K number of superpixels that the 
+algorithm will have to produce. Each \emph{K} pixel represents the central search point 
+and its vector will be used as the weighted initial vector of the corresponding 
+cluster. Each pixel is assigned to te cluster for which the weightedd mean 
+is closet to the picel's vector in the ten-dimensional feature space. At each 
+assignment, the weighted average and the central point will be updated until 
+the system convergence. Each cluster will form a superpixel and each of 
+these, if considered spatially small, can be joined to other clusters to form 
+a larger cluster. The total complexity achieved by LSC is \emph{O(kN + nZ)}, where 
+\emph{k} represents the number of iterations, \emph{N} the number of pixels, \emph{n} the average 
+number of adjacent neighbors and \emph{z} represents the number of small 
+isolated superpixels to be joined. This complexity, when compared with that 
+achieved by other superpixel systems, is the lowest, therefore LSC is the 
+fastest superpixel segmentation algorithms.
 
-\begin{multline}
-    W(p,q) = C_s^2(\cos \frac{\pi}{2}(x_p-x_q)+\cos\frac{\pi}{2}(y_p-y_q)) \\
-    \leftarrow + C_c^2(\cos \frac{\pi}{2}(l_p-l_q)+\cos\frac{\pi}{2}(\alpha_p-\alpha_q) \\
-    + \cos\frac{\pi}{2}(\beta_p-\beta_q)x2.55^2) 
-\end{multline}
+\subsection{COMPARATIVE EXPERIMENTS}
+In order to evaluate the quantitative goodness of the proposed algorithm, 
+three comparison metrics are used: under segmentation error (\emph{UE}) \cite{0781426514}, boundary 
+recreation (\emph{BR}) and achievable segmentation accuracy (\emph{ASA}) \cite{0781426508}. The goal 
+is to have high values in all three metrics. A low percentuage of UE indicates 
+that the boundarye isn't costituted only by the pixels that form it, but is 
+also made up of pixels that belong to other objects. A segmentation is correct 
+when at least two boundary pixel fall from at least one superpixel boundary 
+point. A high BR index indicates that the better segmentation is obtained. 
+On the other hand, the ASA metric indicates the level of accurancy achieved 
+in the segmentation pashe of contour, obtained thanks to the various labels 
+(ground-truth) placed on each superpixel. A high ASA value indicates that 
+superpixel adapt well to objects. The experiments were conducted on a set 
+of 300 images belonging to the Barkeley Segmentation Database \cite{0781426515}.
+
+\subsubsection{Parameter Selection}

### 2021-03-26 paper_2.tex
finish 2.3.1

@@
 \end{equation}
-The mapping function that maps a point in a ten-dimensional space is as follows:
+Where $ C_s $ and $ C_c $ are used to control the relative significance of
+color and spatial information. The mapping function that maps a point in a ten-dimensional
+space is as follows:
 \begin{equation}
@@
 \subsubsection{Parameter Selection}
+When the ratio $ r = C_s / C_c $ is high, then the neighboring pixels tend to 
+be aggregated into a single cluster, forming superpixels with a regular shape 
+and therefore potentially incorrect. On the other hand, when \emph{r} is small, then 
+it means that the pixels tend to have similar colors, therefore both will be 
+grouped into a single cluster, forming irregular superpixels. Therefore \emph{r} 
+can be used as a correction parameter. In order to control the search range 
+of the K-means cluster algorithm, a $ \tau $ parameter is used which is equal to at 
+least 0.5. This value will be multiplied by the spatial components, vertical 
+($ v_x $) and horizontal ($ v_y $), of the vector belonging to each point in space. Clearly, 
+as this parameter increases, the size of each superpixel generated and the 
+general $ O(N) $ complexity will increase. In the experiments conducted, $ \tau $ 
+is set to 1.

### 2021-03-27 paper_2.tex
finish table paper2

@@
 isolated superpixels to be joined. This complexity, when compared with that 
-achieved by other superpixel systems, is the lowest, therefore LSC is the 
-fastest superpixel segmentation algorithms.
+achieved by other superpixel systems, is the lowest.
 
@@
 is set to 1.
+
+\subsubsection{Comparison With State-of-the-Art}
+The proposed system is compared with other existing superpixels algorithms 
+in the state of the art. A comparison, in terms of boundary adherence and 
+speed in segmentation, is shown in table () when the number of superpixels 
+\emph{K} generated is 400. With a relatively high \emph{K} number, LSC achieves 
+the best performance.
+
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{*{9}{|c}|}%%{|c|c|c|c|c|c|c|c|c|}
+        \hline
+        & EneOpt0 & SEEDS & ERS & Lattices & NCuts & SLIC & Turbo & LSC \\
+        \hline
+        \bfseries{ADERENCE TO BOUNDARY} & & & & & & & & \\
+        \emph{Under segmentation error} & 0.230 & 0.197 & 0.198 & 0.303 & 0.220 & 0.213 & 0.277 & \bfseries{0.190}\\
+        \emph{Boundary recall} & 0.765 & 0.918 & 0.920 & 0.811 & 0.789 & 0.837 & 0.739 & \bfseries{0.926}\\
+        \emph{Achievable segmentation accuracy} & 0.950 & 0.960 & 0.959 & 0.933 & 0.956 & 0.956 & 0.943 & \bfseries{0.962}\\
+        \hline
+        \bfseries{SEGMENTATION SPEED} & & & & & & & & \\
+        \emph{Computational complexity} & $ O(N^3/K^2) $ & $ O(N) $ & $ O(N^2 \lg{N}) $ & $ O(N^{\frac{3}{2}} \lg{N}) $ & $ O(N^{\frac{3}{2}}) $ & $ O(N) $ & $ O(N) $ & $ O(N) $\\
+        \emph{Average time per image} & 3.35s & \bfseries{0.0935}s & 0.969s & 0.284s & 93.4s & 0.125s & 6.61s & 0.334s\\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Performance metrics superpixel segmentation algorithms at K=400}
+    \label{table superpixels}
+\end{table}

### 2021-03-27 paper_2.tex
finish 2.3.2

@@
 three comparison metrics are used: under segmentation error (\emph{UE}) \cite{0781426514}, boundary 
-recreation (\emph{BR}) and achievable segmentation accuracy (\emph{ASA}) \cite{0781426508}. The goal 
-is to have high values in all three metrics. A low percentuage of UE indicates 
-that the boundarye isn't costituted only by the pixels that form it, but is 
-also made up of pixels that belong to other objects. A segmentation is correct 
-when at least two boundary pixel fall from at least one superpixel boundary 
-point. A high BR index indicates that the better segmentation is obtained. 
-On the other hand, the ASA metric indicates the level of accurancy achieved 
-in the segmentation pashe of contour, obtained thanks to the various labels 
-(ground-truth) placed on each superpixel. A high ASA value indicates that 
-superpixel adapt well to objects. The experiments were conducted on a set 
-of 300 images belonging to the Barkeley Segmentation Database \cite{0781426515}.
+recall (\emph{BR}) and achievable segmentation accuracy (\emph{ASA}) \cite{0781426508}. The 
+goal is to have a low UE value, while it is preferable to have high values in BR 
+and ASA. A low percentage of UE indicates that the detected boundary is made 
+up of a small amount of pixels not belonging to the object to be delimited. 
+A segmentation is correct when at least two boundary pixel fall from at least 
+one superpixel boundary point. A high BR index indicates that the better 
+segmentation is obtained. On the other hand, the ASA metric indicates the 
+level of accurancy achieved in the segmentation pashe of contour, obtained 
+thanks to the various labels (ground-truth) placed on each superpixel. A 
+high ASA value indicates that superpixel adapt well to objects. The experiments 
+were conducted on a set of 300 images belonging to the Barkeley 
+Segmentation Database \cite{0781426515}.
 
 \subsubsection{Parameter Selection}
-When the ratio $ r = C_s / C_c $ is high, then the neighboring pixels tend to 
-be aggregated into a single cluster, forming superpixels with a regular shape 
-and therefore potentially incorrect. On the other hand, when \emph{r} is small, then 
-it means that the pixels tend to have similar colors, therefore both will be 
-grouped into a single cluster, forming irregular superpixels. Therefore \emph{r} 
-can be used as a correction parameter. In order to control the search range 
-of the K-means cluster algorithm, a $ \tau $ parameter is used which is equal to at 
-least 0.5. This value will be multiplied by the spatial components, vertical 
-($ v_x $) and horizontal ($ v_y $), of the vector belonging to each point in space. Clearly, 
+When the ratio $ r = C_s / C_c $ is high, then the neighboring pixels tend to be 
+aggregated into a single cluster, forming superpixels with a regular shape 
+and therefore potentially incorrect. On the other hand, when \emph{r} is small, 
+then it means that the pixels tend to have similar colors, therefore both 
+will be grouped into a single cluster, forming irregular superpixels. In order to 
+choose an optimal r value, it is necessary to introduce a metric that calculates 
+the average  values of shape regularity. The average value of shape regularity 
+is measured with a metric called superpixel compactness \emph{(CP)} \cite{0781426533} which is 
+inversely proportional to the BR index. So as CP increases, the likelihood 
+of regular shapes being created is greater and at the same time worse segmentation 
+will be generated as BR decreases. The r value will be chosen 
+when the value resulting from $ (1-BR / CP) $ is the lowest. Therefore \emph{r} can be 
+used as a correction parameter. In order to control the search range of the 
+K-means cluster algorithm, a $ \tau $ parameter is used which is equal to at least 
+0.5. This value will be multiplied by the spatial components, vertical ($ v_x $) 
+and horizontal ($ v_y $), of the vector belonging to each point in space. Clearly, 
 as this parameter increases, the size of each superpixel generated and the 
-general $ O(N) $ complexity will increase. In the experiments conducted, $ \tau $ 
-is set to 1.
+general $ O(N) $ complexity will increase. In the experiments conducted, $ \tau $ is 
+set to 1.
 
@@
 in the state of the art. A comparison, in terms of boundary adherence and 
-speed in segmentation, is shown in table () when the number of superpixels 
-\emph{K} generated is 400. With a relatively high \emph{K} number, LSC achieves 
-the best performance.
+speed in segmentation (Table \ref{table superpixels}), when the number of superpixels \emph{K} generated 
+is 400. With a relatively high \emph{K} number, LSC achieves the best 
+performance.
 
@@
 \end{table}
+As we can see from the results, the worst algorithm, in terms of time, 
+is \emph{NCuts}, while a good algorithm, which ranks second before \emph{LSC}, is \emph{SLIC}. 
+Unlike the algorithm studied, SLIC uses an iterative K-means clustering 
+performed inside different feature spaces, based only on local characteristics. 
+On the other hand, LSC is able to use local and global features thanks to the 
+$ \phi $  mapping function, all to have a better segmentation. Looking at the data 
+in the table, this makes us understand how LSC is able to have a better BR 
+value despite having a higher CP value than the previous algorithms, this 
+represents the strength of this algorithm.

### 2021-03-27 paper_2.tex
fix 2.3.2

@@
 three comparison metrics are used: under segmentation error (\emph{UE}) \cite{0781426514}, boundary 
-recall (\emph{BR}) and achievable segmentation accuracy (\emph{ASA}) \cite{0781426508}. The 
+recall (\emph{BR}) and achievable segmentation accuracy (\emph{ASA}). The 
 goal is to have a low UE value, while it is preferable to have high values in BR 
@@
 On the other hand, LSC is able to use local and global features thanks to the 
-$ \phi $  mapping function, all to have a better segmentation. Looking at the data 
+$ \phi $  mapping function, all to have a better segmentation. However, when 
+K = 400, the CP value of the \emph{ERS} \cite{0781426508} and \emph{SEEDS} \cite{0781426509} algorithms are 0.151 
+and 0.280 respectively, while the CP value of LSC is 0.366. Looking at the data 
 in the table, this makes us understand how LSC is able to have a better BR 
@@
 represents the strength of this algorithm.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper2/superpixelsComparison.png}
+    \centering
+    \caption{Superpixel results from different algorithms. (a) SEEDS. (b) NCuts. (c) SLIC. (d) ERS. (e) LSC.}
+    \label{fig: superpixelsComparison}
+\end{figure}

### 2021-03-28 paper_2.tex
finish 2.4.1

@@
 \end{figure}
+
+\subsection{APPLICATIONS}
+\subsubsection{Class Segmentation}
+An SVM-based multi-class object classifier trained on the histograms of the generated 
+superpixels was used. In order for similar superpixels to have the same 
+label, a conditional random field (CRF) is used to refine the segmentation. 
+Thanks to this model, the prediction made by the classifier will also 
+take into account the neighbors superpixels to the one to be labeled. The 
+method used is that proposed in \cite{0781426534} where the main unit of measurement is 
+that of the superpixel. In \cite{0781426534} the quick shift (\emph{QS}) algorithm is used for the 
+generation of superpixels. The experiments were conducted on the \emph{Graz-02} 
+database \cite{0781426535} containing already labeled objects. The accuracy achieved by 
+the QS, ERS, SLIC and LSC algorithms is that shown in the Table \ref{table accuracy}, while 
+the various segmentations, obtained from each of these, are visible in the 
+figure \ref{fig: superpixelSegmentation}. As you can see, LSC performs a better segmentation than the other 
+methods, this happens because the information obtained from the histograms 
+belonging to the SIFT of different superpixel generated are used. In this way 
+there is a better adherence to the boundary of each object in addition the 
+superpixels take on a highly irregular shape for objects in the foreground and 
+more regular for the background.
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{*{5}{|c}|}%%{|c|c|c|c|c|}
+        \hline
+        & QS & ERS & SLIC & LSC\\
+        \hline
+        bike & 72.2 & 74.2 & 76.3 & \bfseries{76.9}\\
+        cars & 72.2 & 74.7 & 72.5 & \bfseries{76.8}\\
+        person & 66.3 & 66.5 & 66.7 & \bfseries{67.0}\\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Accuracy using different superpixels algorithms.}
+    \label{table accuracy}
+\end{table}
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper2/superpixelAlgo.png}
+    \centering
+    \caption{Segmentation using different superpixels algorithms. (a) Original Image. (b) QS. (c) ERS. (d) SLIC. (e) LSC. (f)Ground Truth.}
+    \label{fig: superpixelSegmentation}
+\end{figure}

### 2021-03-28 paper_2.tex
finish 2.4.2

@@
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
     \centering
@@
 \end{figure}
+
+\subsubsection{Weakly Supervised Semantic Segmentation}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 0.4 \linewidth]{images/paper2/semanticSegmentation.png}
+    \centering
+    \caption{Weakly supervised semantic segmentation.
+(a) A training image with bounding boxes.
+(b) Output of soft-max layer of $ FCN_c $.
+(c) Coarse semantic segmentation result.
+(d) Superpixels with higher probability of foreground.
+(e) Fore-/Background segmentation result after iterative optimization.
+(f) Refined semantic segmentation result.}
+    \label{fig: flowchartSemanticSegmentation}
+\end{figure}
+As the title suggests, the LSC algorithm is able to improve semantic segmentation 
+with a weakly supervised method. The images of the PASCAL 
+VOC2012 database \cite{0781426538} are used as tests, in which there are 1449 images
+containing labeled objects and the remaining 10582 images containing only 
+bounding boxes used for training and validation. The flow chart of the proposed 
+method can be seen in figure (\ref{fig: flowchartSemanticSegmentation}). The steps are as follows: coarse 
+semantic segmentation, fore-/background segmentation and refined semantic 
+segmentation. In the first step there is a completely convolutional network, 
+called $ FCN_c $, trained with images containing only the bounding boxes which 
+will be restricted in order to eliminate the border pixels that seem to be 
+irrelevant. These new squares are used as positive examples, while the cut 
+parts are used as negative examples. For each superpixel \emph{p} generated within 
+each bounding box $ i_{th} $, we set $ c_p^i $ as the average value of the colors of each 
+pixel within the superpixel and then we set $ l_p^i $ as the label to be estimated (0 
+backgroud, 1 foreground). The separation of the background from the 
+foreground is seen as an optimization problem
+\begin{equation}
+    \begin{split}
+        \argmax\limits_{l} \sum_i\sum_p(E_a(l_p^i,c_p^i) + \lambda_1E_c(l_p^i, FCN_c)\\
+        + \lambda_2\sum_{q\in N(p)}E_s(l_p^i,c_p^i,l_q^i,c_q^i)) 
+    \end{split}
+\end{equation}
+Where $ E_s $ is useful for capturing the smoothness prior produced by a covariance 
+matrix, $ E_c $ represents the probability that the superpixel belongs 
+to the foreground, while $ E_a $, also called the appearance model, represents 
+the probability that a superpixel belongs to the background or foreground. 
+After several iterations, which have the purpose of updating the foreground 
+and background labels of the superpixels, a correct segmentation will be 
+obtained. The segmentation obtained will be used to train a convolutional 
+network called $ FCN_r $ which is combined with a dense CRF model useful for 
+formulating the final semantic segmentation model. This system is also 
+called $ Joint_{sp} $. The model is compared with other supervivided methods \cite{0781426541}, 
+a strong one, called \emph{Strong}, and a weak one called \emph{Bbox-seg}, the results of 
+which can be seen in figure \ref{fig: semanticSegmentation}.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 0.6 \linewidth]{images/paper2/segmentationAlgo.png}
+    \centering
+    \caption{Semantic segmentation. (a) Input image. (b) Strong. (c) Bbox-seg. (d) $ Joint_{sp} $ (LSC) }
+    \label{fig: semanticSegmentation}
+\end{figure}
+
+While the accuracy, measured with the intersection over-union (\emph{IOU}), 
+achieved by the systems mentioned is visible in the table \ref{table accuracy semantic segmentation}.
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{*{4}{|c}|}%%{|c|c|c|c|}
+        \hline
+        Strong & Bbox-seg & $ Joint_{sp} $ \\
+        \hline
+        62.5 & 60.6 & \bfseries{64.0} \\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Semantic segmentation accuracy in terms of Mean IOU (\%)}
+    \label{table accuracy semantic segmentation}
+\end{table}

### 2021-03-28 paper_2.tex
finish paper2

@@
 \subsubsection{Weakly Supervised Semantic Segmentation}
-\begin{figure}[htbp]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width = 0.4 \linewidth]{images/paper2/semanticSegmentation.png}
+    \includegraphics[width = 0.6 \linewidth]{images/paper2/semanticSegmentation.png}
     \centering
@@
 a strong one, called \emph{Strong}, and a weak one called \emph{Bbox-seg}, the results of 
-which can be seen in figure \ref{fig: semanticSegmentation}.
+which can be seen in figure \ref{fig: semanticSegmentation}. While the accuracy, measured with the intersection 
+over-union (\emph{IOU}), achieved by the systems mentioned is visible in the 
+table \ref{table accuracy semantic segmentation}.
+
 \begin{figure}[htbp]
     \centering
-    \includegraphics[width = 0.6 \linewidth]{images/paper2/segmentationAlgo.png}
+    \includegraphics[width = 0.8 \linewidth]{images/paper2/segmentationAlgo.png}
     \centering
@@
 
-While the accuracy, measured with the intersection over-union (\emph{IOU}), 
-achieved by the systems mentioned is visible in the table \ref{table accuracy semantic segmentation}.
 \begin{table}[h!]
@@
 \end{table}
+
+\subsection{CONCLUSIONS}
+Like all superpixel algorithms, there are still two problems that need to be 
+solved. The first concerns the number K of superpixels to be generated. Unfortunately, 
+this parameter still has to be entered manually and today there 
+is no stable method that can establish a specific K number of superpixels on 
+each type of image. The second, on the other hand, concerns the study of 
+new similarity techniques, instead of the one already used in this article 
+($ W(p,q) $), useful for improving the performance, in terms of segmentation, 
+of LSC.

### 2021-03-28 slides.tex
start paper_2
LSC algorithm pt2 start

@@
 \usepackage{biblatex}
+\setbeamertemplate{navigation symbols}{}
 \setbeamertemplate{caption}[numbered]
@@
 \section{Paper 2}
-\begin{frame}
+\subsection{\emph{"Linear Spectral Clustering Superpixel"}}
+\begin{frame}{INTRODUCTION}
+    The introduced technique is called SUPERPIXEL. Widely used in image 
+    processing for particular tasks such as image segmentation, image analysis, 
+    image classification, target tracking, 3D reconstruction, surface retrieval and 
+    object proposal. The purpose of the elaborate story is to reduce the 
+    computational complexity through a superpixel system called LSC (Linear Spectral
+    Clustering).
+\end{frame}
+
+\begin{frame}{LSC SUPERPIXEL pt1}
+    Goal: optimization (max/min) of two objective functions to create clusters of pixels called superpixels:
+    \begin{block}{Objective Function 1: Weighted K-Means}
+        $$ F_{km} = \sum_{k=1}^K\sum_{p\in\pi_k}\omega(p)= || \phi(p)-m_k ||^2 $$
+    \end{block}
+    \begin{block}{Objective Function 2: Normalized cuts}
+        $$ F_{N_{cuts}} = \frac{1}{K}\sum_{k=1}^K\frac{\sum_{p\in\pi_k}\sum_{q\in\pi_k}W(p,q)}{\sum_{p\in\pi_k}\sum_{q\in{V}}W(p,q)} $$
+    \end{block}
+    Problem: extremely high computational!
+\end{frame}
+
+\begin{frame}{LSC SUPERPIXEL pt2}
+    If corollary 1 is satisfied, then  \emph{weghted K-means clustering} can be used 
+    for segmentation and for creation of superpixel regions, instead of the 
+    eigen-vector based method.
+    \begin{block}{\bfseries{Corollary 1}}
+        Optimizations of the objective functions of the weighted K-means
+        and the normalized cuts are mathematically equivalent if (1) and (2) 
+        hold simultaneously. The symbol $ \cdot $ stands for inner product.
+    \end{block}
+
+    \begin{block}{Equation (1)}
+           $$ \omega(p)\phi(p) \cdot \omega(q)\phi(q) = W(p,q), \forall p,q \in V $$
+    \end{block}
+
+    \begin{block}{Equation (2)}
+        $$ \omega(p) = \sum_{q \in V} W(p,q), \forall p \in V $$
+    \end{block}
+\end{frame}
+
+\begin{frame}{LSC Algorithm pt1}
+    Problem? $ \rightarrow $ Find the correct positive similarity function $ W (p,q) $, 
+    between two data points \emph{p} and \emph{q} to solve equation 1.
+    \begin{block}{Similarity Function}
+        \begin{equation}\small
+            \begin{split}
+                W(p,q) = C_s^2(\cos \frac{\pi}{2}(x_p-x_q)+\cos\frac{\pi}{2}(y_p-y_q)) \\
+                + C_c^2(\cos \frac{\pi}{2}(l_p-l_q)+\cos\frac{\pi}{2}(\alpha_p-\alpha_q) \\
+                + \cos\frac{\pi}{2}(\beta_p-\beta_q)x2.55^2)
+            \end{split}
+        \end{equation}
+    \end{block}
+
+    \begin{block}{Mapping Function}
+        \begin{equation}\small
+            \begin{split}
+                \phi(p) = \frac{1}{\omega(p)}[C_c\cos\frac{\pi}{2}l_p, C_c\sin\frac{\pi}{2}l_p, 2.55C_c\cos\frac{\pi}{2}\alpha_p \\
+                x 2.55C_c\sin\frac{\pi}{2}\alpha_p, 2.55C_c\cos\frac{\pi}{2}\beta_p, 2.55C_c\sin\frac{\pi}{2}\alpha_p, \\
+                x C_s\cos\frac{\pi}{2}x_p, C_s\sin\frac{\pi}{2}x_p, C_s\cos\frac{\pi}{2}y_p, C_s\sin\frac{\pi}{2}x_p]
+            \end{split}
+        \end{equation} 
+    \end{block}
 
@@
 
+\begin{frame}{LSC Algorithm pt2}
+    Assuming that equation 1 exists, LSC method takes two parameters as 
+    input; The image to be segmented and the preferred K number of 
+    superpixels that the algorithm will have to produce.
+\end{frame}
+
 \end{document}

### 2021-03-29 slides.tex
finish applications paper2 slide

@@
 \usepackage{biblatex}
+\usepackage{adjustbox}
+\usepackage[font=scriptsize]{caption}
+\usepackage{subcaption}
+\captionsetup[figure]{labelsep=period}
+\captionsetup[subfigure]{labelformat=simple} % default is 'parens'
+\renewcommand\thesubfigure{\thefigure.\alph{subfigure}.}
+
 \setbeamertemplate{navigation symbols}{}
@@
     input; The image to be segmented and the preferred K number of 
-    superpixels that the algorithm will have to produce.
+    superpixels that the algorithm will have to produce. The number K 
+    corresponds to the number of centroids and each of these will be useful 
+    for grouping the neighbors pixels, in a range of $ \tau v_x \ x \ \tau v_y $, with $ \tau>0.5 $, 
+    using a distance comparison.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 0.7 \linewidth]{paper2/slide1.png}
+        \centering
+        \caption{Sample images segmented with K = 1000/500/200 superpixels using LSC.}
+        \label{fig: metrics}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{COMPARATIVE EXPERIMENTS}
+    \begin{table}[htbp!]
+        \centering
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{*{9}{|c}|}%%{|c|c|c|c|c|c|c|c|c|}
+            \hline
+            & EneOpt0 & SEEDS\footfullcite{0781426509} & ERS\footfullcite{0781426508} & Lattices & NCuts & SLIC\footfullcite{0781426514} & Turbo & LSC \\
+            \hline
+            \bfseries{ADERENCE TO BOUNDARY} & & & & & & & & \\
+            \emph{Under segmentation error} & 0.230 & 0.197 & 0.198 & 0.303 & 0.220 & 0.213 & 0.277 & \bfseries{0.190}\\
+            \emph{Boundary recall} & 0.765 & 0.918 & 0.920 & 0.811 & 0.789 & 0.837 & 0.739 & \bfseries{0.926}\\
+            \emph{Achievable segmentation accuracy} & 0.950 & 0.960 & 0.959 & 0.933 & 0.956 & 0.956 & 0.943 & \bfseries{0.962}\\
+            \hline
+            \bfseries{SEGMENTATION SPEED} & & & & & & & & \\
+            \emph{Computational complexity} & $ O(N^3/K^2) $ & $ O(N) $ & $ O(N^2 \lg{N}) $ & $ O(N^{\frac{3}{2}} \lg{N}) $ & $ O(N^{\frac{3}{2}}) $ & $ O(N) $ & $ O(N) $ & $ O(N) $\\
+            \emph{Average time per image} & 3.35s & \bfseries{0.0935}s & 0.969s & 0.284s & 93.4s & 0.125s & 6.61s & 0.334s\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Performance metrics superpixel segmentation algorithms at K=400}
+        \label{table superpixels}
+    \end{table}
+    Best performance: low "Under segmentation Error" (\emph{UE}), high 
+    "Boundary Recall" (\emph{BR}) and high "Achievable segmentation accuracy 
+    (\emph{ASA}).
+\end{frame}
+
+\begin{frame}{APPLICATIONS: Class segmentation}
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 1 \linewidth]{images/paper2/superpixelAlgo.png}
+        \centering
+        \caption{Segmentation using different superpixels algorithms. (a) Original Image. (b) QS. (c) ERS. (d) SLIC. (e) LSC. (f)Ground Truth.}
+        \label{fig: superpixelSegmentation}
+    \end{figure}
+
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=4cm}
+        \begin{tabular}{*{5}{|c}|}%%{|c|c|c|c|c|}
+            \hline
+            & QS & ERS & SLIC & LSC\\
+            \hline
+            bike & 72.2 & 74.2 & 76.3 & \bfseries{76.9}\\
+            cars & 72.2 & 74.7 & 72.5 & \bfseries{76.8}\\
+            person & 66.3 & 66.5 & 66.7 & \bfseries{67.0}\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Accuracy using different superpixels algorithms.}
+        \label{table accuracy}
+    \end{table}
+\end{frame}
+
+\begin{frame}{APPLICATIONS: Weakly Supervised Semantic Segmentation}
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[H]
+                \includegraphics[width = 0.7 \linewidth]{images/paper2/semanticSegmentation.png}
+                \caption{Weakly supervised semantic segmentation.
+(a) A training image with bounding boxes.
+(b) Output of soft-max layer of $ FCN_c $.
+(c) Coarse semantic segmentation result.
+(d) Superpixels with higher probability of foreground.
+(e) Fore-/Background segmentation result after iterative optimization.
+(f) Refined semantic segmentation result.}
+            \end{figure}
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[htbp]
+                \centering
+                \includegraphics[width = 1 \linewidth]{images/paper2/segmentationAlgo.png}
+                \centering
+                \caption{Semantic segmentation. (a) Input image. (b) Strong. (c) Bbox-seg. (d) $ Joint_{sp} $ (LSC) }
+            \end{figure}
+            \begin{table}[H]
+                \begin{adjustbox}{max width=4cm}
+                    \begin{tabular}{*{3}{|c}|}%%{|c|c|c|}
+                        \hline
+                        Strong\footnotemark[1]& Bbox-seg\footnotemark[1] & $ Joint_{sp} $ \\
+                        \hline
+                        62.5 & 60.6 & \bfseries{64.0} \\
+                        \hline
+                    \end{tabular}
+                \end{adjustbox}
+                \caption{Semantic segmentation accuracy in terms of Mean IOU (\%)}
+            \end{table}
+        \end{minipage}
+    \end{minipage}
+    \footnotetext[1]{\tiny G. Papandreou, L. Chen, K. Murphy, and A. Yuille, “Weakly-and semi-
+    supervised learning of a deep convolutional network for semantic image
+    segmentation,” in Proc. ICCV, pp. 1742–1750, Dec. 2015}
+
 \end{frame}

### 2021-03-29 slides.tex
finish slides paper2

@@
     \footnotetext[1]{\tiny G. Papandreou, L. Chen, K. Murphy, and A. Yuille, “Weakly-and semi-
-    supervised learning of a deep convolutional network for semantic image
-    segmentation,” in Proc. ICCV, pp. 1742–1750, Dec. 2015}
+    supervised learning of a deep convolutional network for semantic image segmentation,” in Proc. ICCV, pp. 1742–1750, Dec. 2015}
+\end{frame}
 
+\begin{frame}{CONCLUSIONS}
+    The LSC algorithm seems to be the best in terms of adherence to the 
+    boundary and in the creation of superpixels with increasingly regular 
+    shape, but there are still two problems to solve:
+    \begin{enumerate}
+        \item The number k of superpixels entered manually
+        \item New similarity techniques to improve performance
+    \end{enumerate}
 \end{frame}

### 2021-03-29 paper_3.tex
start paper3

\section{An End-to-End Compression Framework Based
on Convolutional Neural Networks}

\begin{flushleft}
    \author{
    Feng Jiang, 
    Wen Tao, 
    Shaohui Liu, 
    Jie Ren, 
    Xun Guo, 
    Debin Zhao, 
    \emph{Member, IEEE}
    }
\end{flushleft}

\begin{center}
    \emph{IEEE TRANSACTIONS ON CIRCUIT AND SYSTEMS FOR VIDEO THECNOLOGY, VOL. 28, NO. 11, OCTOBER 2018}
\end{center}

\subsection{INTRODUCTION}

### 2021-03-29 paper_3.tex
finish introduction

@@
 \subsection{INTRODUCTION}
+In recent years, within the field of computer vision, remarkable results have 
+been achieved with regard to image compression. The purpose of compression 
+is to be able to transmit, or save, the entire image at low bit rates. As far as 
+decompression is concerned, deblocking and denoising techniques have been 
+developed that are useful for obtaining good images. Further pre-processing 
+steps have been found to negatively impact in system performance. Therefore 
+the proposed method uses a framework composed of two convolutional 
+networks (\emph{CNNs}). The first network, called compact convolutional neural 
+newtork (\emph{comCNN}), is used for compression and uses the JPEG, JPEG2000 
+and BPG encoding codecs. The second network, called reconstruction convolutional 
+neural network (\emph{RecCNN}), is used for image decompression. A 
+first example of the work carried out by the proposed framework is visible in 
+the Fig. \ref{fig:output}.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.6 \linewidth]{images/paper3/output .png}
+    \centering
+    \caption{Left: the JPEG-coded image. Right: the decoded image.}
+    \label{fig:output}
+\end{figure}

### 2021-03-29 paper_3.tex
finish 3.2.1

@@
 \end{figure}
+
+\subsection{RELATED WORK}
+\subsubsection{Image Deblocking and Artifacts Reduction}
+Going back to talking about the deblocking technique, this is useful for removing 
+all those blocks that visually worsen the appearance of each image. 
+The various restoration techniques model the distortion created in the compression 
+phase in order to reduce artifacts. Many methods already proposed 
+in the state of the art use techniques that have a great impact on performance 
+when they adopt iterative restoration processes. Therefore, the proposed 
+method tries to obtain the same result but with a lower computational 
+cost.

### 2021-03-29 paper_3.tex
finish 3.2.2

@@
 cost.
+
+\subsubsection{Image Super-Resolution Based on Deep Learning}
+Convolutional neural networks (\emph{CNNs}) have been used for super resolution 
+(\emph{SR}) images especially when residual learning and gradient-based optimization 
+algorithms have been proposed to train a deep network. According to 
+some studies, the depth of a network doesn't always lead to good performance. 
+Other researchers, on the other hand, claim the opposite.
+
+\subsubsection{Image Compression Based on Deep Learning}

### 2021-03-29 paper_3.tex
finish 3.2.3

@@
 \subsubsection{Image Compression Based on Deep Learning}
+Deep learning was used for lossy and loseless compressions achieving good 
+performance. There have been some methods that have prevailed over others. 
+However, all of these methods ignore compatibility with various image codecs, 
+thus limiting their use in some existing systems. The proposed framework 
+solves this problem by operating with different image codecs, also taking into 
+account the compression performance.

### 2021-03-30 paper_3.tex
update 3.3.1

@@
 account the compression performance.
+
+\subsection{THE PROPOSED COMPRESSION FRAMEWORK}
+\subsubsection{Architecture of End-to-End Compression Framework}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 0.8 \linewidth]{images/paper3/framework.png}
+    \centering
+    \caption{The proposed novel compression framework.}
+    \label{fig:framework}
+\end{figure}
+As mentioned, the first \emph{ComCNN} convolutional network is used to generate 
+a compact representation of the input image which preserves the structural 
+information and facilitates the reconstruction of image in high quality. The 
+second convolutional network, \emph{RecCNN}, is used to improve the quality of the 
+decoded image. In particular:
+\begin{enumerate}
+    \item \emph{Compact Representation Convolutional Neural Network (ComCNN)}: 
+    This network is made up of three weighted layers. The first layer is 
+    used to perform the extraction and representation of patches from the 
+    input image. 64 filters are used, each 3x3xc in size where c indicates 
+    the number of image channels. Thanks to these filters, 64 feature maps 
+    are generated. The second layer has the task of downscaling and improving 
+    the features with convolutional operations having stride equal to 2 
+    and 64 filters of 3x3x64 size. In the last layer, \emph{c} filters, of 3x3x64 
+    size, are used to reconstruct the compact representation.
+    \item \emph{Reconstruction Convolutional Neural Network (RecCNN)}: The layers 
+    are identical to those of the \emph{ComCNN} network, unlike the number. To 
+    speed up training, as well as performance, methods such as residual 
+    learning and batch normalization \cite{0799924133} are used. Finally, the image will be upsampled to its original size, using a cubic interpolation.
+\end{enumerate}

### 2021-03-31 paper_3.tex
update paper3

@@
     speed up training, as well as performance, methods such as residual 
-    learning and batch normalization \cite{0799924133} are used. Finally, the image will be upsampled to its original size, using a cubic interpolation.
+    learning and batch normalization \cite{0799924133} are used. Finally, the image will 
+    be upsampled to its original size, using a cubic interpolation.
 \end{enumerate}
+
+\subsubsection{Learning Algotrithm}
+In order for both networks to have good training, their parameters must be 
+optimized (weights and bias). To achieve this, the following formulas will 
+have to be optimized iteratively:
+\begin{equation}
+    \hat{\theta_1} = \argmin\limits_{\theta_1}||Re(\hat{\theta_2},Cr(\theta_1,x))-x||^2
+\end{equation}
+\begin{equation}
+    \hat{\theta_2} = \argmin\limits_{\theta_2}||Re(\hat{\theta_2},\hat{x}_m)-x||^2
+\end{equation}
+Where:
+\begin{enumerate}
+    \item \emph{x} represents the original image
+    \item $ \hat{\theta_1} $ and $ \hat{\theta_2} $ are the parameters of \emph{ComcCNN} and \emph{RecCNN}
+    \item $ C_r(\cdot) $ and $ R_e() $ represent the \emph{ComcCNN} and \emph{RecCNN}
+\end{enumerate}
+
+\subsubsection{Loss Functions}

### 2021-03-31 paper_3.tex
finish 3.3.3

@@
 Where:
-\begin{enumerate}
+\begin{itemize}
     \item \emph{x} represents the original image
@@
     \item $ C_r(\cdot) $ and $ R_e() $ represent the \emph{ComcCNN} and \emph{RecCNN}
-\end{enumerate}
+    \item $ \hat{x}_m $ is th e decoded compact representation of \emph{x}
+\end{itemize}
 
 \subsubsection{Loss Functions}
+For ComCNN training: as a loss function, we use the mean square error (\emph{MSE}):
+\begin{equation}
+    L_1(\theta_1) = \frac{1}{2N}\sum_{k=1}^N||Re(\hat{\theta_2}, C_r(\theta1,x_k))-x_k||^2
+\end{equation}
+Where \emph{N} and $ \theta_1 $ represent the batch size and the trainable parameter.
+For REcCNN training: after obtaining a set of compact $ x_m $ images from 
+\emph{ComCNN} and the original \emph{x} images, we also use the mean square error 
+(\emph{MSE}) here:
+\begin{equation}
+    L_2(\theta_2) = \frac{1}{2N}\sum_{k=1}^N||res(Co(\hat{x}_{mk}), \theta_2) - (Co(\hat{x}_{mk})-x_k)||^2
+\end{equation}
+Where $ \theta_2 $ are the trained parameters of the network while $ res(\cdot) $ represent 
+the residual learning of the \emph{RecCNN}.

### 2021-03-31 paper_3.tex
finish 3.4.2

@@
 the residual learning of the \emph{RecCNN}.
+
+\subsection{EXPERIMENTS}
+In order to evaluate the performance of the proposed framework, the results 
+obtained were compared with six deblocking methods and two denoising 
+methods. In order to train the network, the \emph{MatConvNet} \cite{0799924138} package is 
+used.
+
+\subsubsection{Datasets for Training and Testing}
+For training, 400 images of 180x180 size are used. The patches used are in 
+total 204800 $ (400x8x64)^2 $, with stride equal to 20. For the test, however only 
+7 images are used which obviously are not present in the training ones.
+
+\subsubsection{Model Initialization}
+The initialization of the weights takes place following the method in \cite{0799924140}, 
+while for the optimization of the gradient the method defined in \cite{0799924121} is used.
+The training of the ComCNN network takes place in 50 epochs with a batch 
+size of 128. The learning rate falls from 0.01 to 0.0001. The initial parameters 
+of the second RecCNN network are identical to those of the first network, 
+including the batch size.

### 2021-03-31 paper_3.tex
continuing 3.4.3

@@
 including the batch size.
+
+\subsubsection{Experimental Results}
+Various quality factors (\emph{QS}), useful for indicating the degree of loss in a 
+compressed image, are manually set in order to achieve the same bits per 
+pixel (\emph{bpp}) of the original image. In order to compare the other methods 
+existing at the state of the art with the proposed method, two compression 
+quality indices were used such as \emph{PSNR} and \emph{SSIM}. With a \emph{QF} set to 5, the ù
+comparison results obtained are shown in figure \ref{fig:QF5}, while the results 
+obtained whit \emph{QF} set to 10 are shown in figure \ref{fig:QF10}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper3/comparison.png}
+    \centering
+    \caption{JPEG: QF=5, PSNR(db) and SSIM results of alghoritms image deblocking and denoising.}
+    \label{fig:QF5}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper3/comparison2.png}
+    \centering
+    \caption{JPEG: QF=10, PSNR(db) and SSIM results of alghoritms image deblocking and denoising.}
+    \label{fig:QF10}
+\end{figure}

### 2021-04-01 slides.tex
start paper3
start slide paper3
finish slide 2 paper3

@@
     \begin{enumerate}
-        \item The number k of superpixels entered manually
+        \item The number K of superpixels entered manually
         \item New similarity techniques to improve performance
@@
 
+\section{Paper 3}
+\subsection{\emph{"An End-to-End Compression Framework Based on Convolutional Neural Networks"}}
+
+\begin{frame}{INTRODUCTION}
+    In recent years, within the field of computer vision, remarkable results 
+    have been achieved with regard to image compression. The purpose of 
+    compressionis to be able to transmit, or save, the entire image at low bit 
+    rates. The following article presents a compression method based on 
+    convolutional neural networks (CNNs) which, through the use of various 
+    state-of-the-art codecs, are able to achieve better performance in terms 
+    of compression and image quality.
+\end{frame}
+
+\begin{frame}{RELATED WORK}
+    At the state of the art there are post-processing methods that use 
+    {\bfseries{deblocking}} and {\bfseries{restoring}} techniques \footfullcite{0799924108}. These techniques have a strong 
+    computational impact on systems. These operations focus on eliminating 
+    artifacts and blocks that contain noise within the image. Other methods 
+    use CNNs for {\bfseries{super-resolution}} (SR) images \footfullcite{0799924123}. There are deep learning 
+    methods that are used for {\bfseries{lossy}} \footfullcite{0799924125} or {\bfseries{lossless}} \footfullcite{0799924130} compression of images, but 
+    these ignore the use of the various existing codecs.
+\end{frame}
+
 \end{document}

### 2021-04-01 slides.tex
start experiments slide paper3

@@
 \renewcommand\thesubfigure{\thefigure.\alph{subfigure}.}
+\DeclareMathOperator*{\argmax}{argmax}
+\DeclareMathOperator*{\argmin}{argmin}
 
@@
 
+\begin{frame}{THE PROPOSED COMPRESSION FRAMEWORK pt1}
+    The proposed system is composed of two convolutional neural networks:
+    \begin{enumerate}
+        \item \emph{ComCNN}: used for compact representation of images
+        \item \emph{RecCNN}: used for decoding and reconstruction of images
+    \end{enumerate}
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 0.8 \linewidth]{images/paper3/framework.png}
+        \centering
+        \caption{Up: the ComCNN. Down: the RecCNN. Right: the codec.}
+        \label{fig: framework}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{THE PROPOSED COMPRESSION FRAMEWORK pt2}
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[H]
+                \includegraphics[width = 1 \linewidth]{images/paper3/ComCNN.png}
+                \caption{ComCNN architecture.}
+            \end{figure}
+            \begin{block}{Parameter optimizations}
+                \small $$ \hat{\theta_1} = \argmin\limits_{\theta_1}||Re(\hat{\theta_2},Cr(\theta_1,x))-x||^2 $$
+            \end{block}
+            \begin{block}{Loss Function}
+               \tiny $$ L_1(\theta_1) = \frac{1}{2N}\sum_{k=1}^N||Re(\hat{\theta_2}, C_r(\theta1,x_k))-x_k||^2 $$
+            \end{block}
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[htbp]
+                \centering
+                \includegraphics[width = 1 \linewidth]{images/paper3/RecCNN.png}
+                \centering
+                \caption{RecCNN architecture.}
+            \end{figure}
+            \begin{block}{Parameter optimizations}
+                \small $$ \hat{\theta_2} = \argmin\limits_{\theta_2}||Re(\hat{\theta_2},\hat{x}_m)-x||^2 $$
+            \end{block}
+            \begin{block}{Loss Function}
+                \tiny $$ L_2(\theta_2) = \frac{1}{2N}\sum_{k=1}^N||res(Co(\hat{x}_{mk}), \theta_2) - (Co(\hat{x}_{mk})-x_k)||^2 $$
+             \end{block}
+        \end{minipage}
+    \end{minipage}
+\end{frame}
+
+\begin{frame}{EXPERIMENTS}
+
+\end{frame}
+
 \end{document}

### 2021-04-01 slides.tex
finish slides paper3

@@
 \begin{frame}{EXPERIMENTS}
+    The performance comparison is made by citing various techniques present 
+    at the state of the art. A compression quality index ({\bfseries\emph{PSNR}}) and ù
+    an image similarity index ({\bfseries\emph{SSIM}}) are used. What is really important to note 
+    is how the proposed method manages to have better performance than 
+    the already used codecs such as \emph{JPEG}, \emph{JPEG2000} and \emph{BPG}, at different 
+    bit rates (\emph{bpp}) and quality factors (\emph{QS}). As for the execution times, in 
+    terms of CPU / GPU, the proposed algorithm is faster than those already 
+    existing.
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 1 \linewidth]{images/paper3/time.png}
+        \centering
+        \caption{Running time(s) of compared methods in CPU (/GPU) }
+        \label{fig:time}
+    \end{figure}
+\end{frame}
 
+\begin{frame}{EXPERIMENTS: JPEG vs. The proposed system}
+    With a variable QF (first set to 5 and then to 10), the results obtained by 
+    the various methods, in terms of PSNR and SSIM, are shown in the following figures:
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[H]
+                \includegraphics[width = 1 \linewidth]{images/paper3/comparison.png}
+                \caption{QF = 5, PSNR(db) and SSIM results of alghoritms image deblocking and denoising}
+            \end{figure}
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[htbp]
+                \centering
+                \includegraphics[width = 1 \linewidth]{images/paper3/comparison2.png}
+                \caption{QF = 10, PSNR(db) and SSIM results of alghoritms image deblocking and denoising}
+                \centering
+            \end{figure}
+        \end{minipage}
+    \end{minipage}
+\end{frame}
+
+\begin{frame}{EXPERIMENTS: JPEG2000 vs. The proposed system}
+    As we can see from the comparison made in figure \ref{fig:parrot}, the difference in  
+    visual quality between the proposed method and the JPEG2000 codec is 
+    considerable. With the same amount of bit rates, the JPEG2000 codec 
+    produces worse results by losing several structural information. 
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[H]
+                \includegraphics[width = 1 \linewidth]{images/paper3/JPEG2000.png}                
+                \caption{Average PSNR(dB)/SSIM results of JPEG2000 and the proposed method on different datasets.}
+            \end{figure}
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[htbp]
+                \centering
+                \includegraphics[width = 1 \linewidth]{images/paper3/JPEG2000p.png}
+                \caption{Performance comparison of JPEG2000 at difference bit rates.}
+                \label{fig:parrot}
+                \centering
+            \end{figure}
+        \end{minipage}
+    \end{minipage}
+\end{frame}
+
+\begin{frame}{EXPERIMENTS: BPG vs. The proposed system}
+    As for the BPG codec, if used in combination with the \emph{ComCNN} and 
+    \emph{RecCNN} networks, it reaches higher \emph{PSNR} and \emph{SSIM} levels than when 
+    used individually or with only one of the two networks.   
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 1 \linewidth]{images/paper3/BPG.png}
+        \centering
+        \caption{BPG: PSNR (dB) and SSIM result of BPG, BPG + RecCNN and the proposed method.}
+        \label{fig:BPG}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{CONCLUSION}
+    The proposed method seems to have the best performance compared to other 
+    methods already existing in the state of the art. The proposed technique 
+    then validates the use of one or more convolutional neural networks to carry 
+    out the task of encoding and decoding images, even in some cases achieving 
+    better quality than existing codecs for image compression.
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 0.5 \linewidth]{images/paper3/final.png}
+        \centering
+        \caption{Visual quality comparison of image deblocking ad different QF.}
+        \label{fig:final comparison}
+    \end{figure}
 \end{frame}

### 2021-04-01 paper_4.tex
start introduction paper4

\section{A Data Set for Camera-Independent Color Constancy}

\begin{flushleft}
    \author{
    Ça$ \breve{g} $lar Aytekin, 
    Jarno Nikkanen, 
    Moncef Gabbouj
    \emph{Fellow, IEEE}
    }
\end{flushleft}

\begin{center}
    \emph{IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL. 27, NO. 2, FEBRUARY 2018}
\end{center}

\subsection{INTRODUCTION}

### 2021-04-01 paper_4.tex
finish 4.1

@@
 \subsection{INTRODUCTION}
+Color constancy is a characteristic of the human visual system (HVS) that 
+helps to perceive a constant color, for example of an object, at different levels 
+of illuminations. It is claimed that the achievement of constancy occurs by 
+approximating the composition of the lighting in order to obtain the true 
+color of the object. There are supervised and unsupervised methods 
+that calculate color consistency. Unsupervised methods are divided into two 
+categories, based on the techniques they use to estimate the color of 
+the illuminating source. The first category makes statistical assumptions 
+about reflectance in a scene. The second category instead uses the physical 
+properties of objects in scenes. Supervised methods also fall into two categories. 
+The first category tries to learn a combination of unsupervised methods to 
+estimate the illumination. The second category builds its own model for 
+learning about illumination. The major factor affecting all of these methods 
+is the sensitivity of the camera sensor. When the sets used for training, 
+validation and testing contain images taken by different cameras, the results 
+returned by the algorithms may be different, as well as their performance. 
+On the other hand, one method returns "fixed" results when operating on 
+images from the same camera. In the CC field, this problem is called camera-independence.
+This report provides a dataset, called Intel-TUT, which is useful for testing 
+camera-independence in the CC.
+Three different cameras capture real scenes both in the lab and elsewhere.
+Laboratory images have different lighting conditions.
+The dataset contains 1536 images and a test set consisting of 454 images taken by a single camera.

### 2021-04-01 paper_4.tex
finish 4.2

@@
 images from the same camera. In the CC field, this problem is called camera-independence.
-This report provides a dataset, called Intel-TUT, which is useful for testing 
-camera-independence in the CC.
-Three different cameras capture real scenes both in the lab and elsewhere.
-Laboratory images have different lighting conditions.
-The dataset contains 1536 images and a test set consisting of 454 images taken by a single camera.
+This report provides a dataset, called \emph{Intel-TUT}, which is 
+useful for testing camera-independence in the CC. Three different cameras 
+capture real scenes both in the lab and elsewhere. Laboratory images have 
+different lighting conditions. The dataset contains 1536 images and a test 
+set consisting of 454 images taken by a single camera.
+
+\subsection{COLOR CONSTANCY DATASETS}
+One of the first datasets for calculating the CC was the one proposed in 
+\cite{0807099130}. The single camera captured images showing a total of 1995 surfaces, 
+11 lab illuminations and 81 illuminations from the real world. The dataset 
+also contains a number of images that make up 50 scenes. After a correct 
+calibration, it removes the irrelevant images, the remainder was made up of 
+only 529 images which made up 30 scenes. Each of these images belongs to 
+the set captured in the lab. Another dataset is the one proposed in \cite{0807099132}, consisting 
+of 11,000 images of indoor / outdoor scenes. The scenes were captured in 
+different geographic locations and under different weather conditions. Unfortunately 
+this dataset contains low resolution images that require a correction 
+phase. Another dataset containing 246 indoor images and 322 outdoor images, 
+taken by two different cameras, is the one proposed in \cite{0807099120}. Another 
+dataset that uses the auto-bracketing technique to acquire the images is the 
+one proposed in \cite{0807099134}. In this dataset they are acquired up to 9 different 
+images, of the same scene, with different settings for each shot. A dataset that 
+aims to obtain multiple lighting in a scene is the one proposed in \cite{0807099135}. 
+This contains relatively few images, 9 acquired in an outdoor environment 
+and 59 lab images. The is also a dataset containing the videos mentioned 
+in \cite{0807099136}. There was only one study \cite{0807099129} that relies on color conversion in order 
+to achieve camera independence. However, this method requires a very 
+sensitive spectral camera to achieve good performance, so it is not applicable 
+to all images. Finally, a last dataset consisting of 1600 indoor and outdoor 
+images, taken by 9 different cameras, is the one proposed in \cite{0807099128} called NUS. 
+In this collection, each scene was captured by each camera with slight misalignments. 
+The database proposed in this paper is similar to the NUT only 
+for the different cameras used. However, the proposed database has some 
+features such as the following:
+\begin{itemize}
+    \item Provides the spectral sensitivities of the cameras;
+    \item Different illuminants illuminate the scene;
+    \item Among the different cameras used, one is mobile;
+    \item Provides a set of tests for good evaluation of CC methods.
+\end{itemize}
+
+\subsection{THE PROPOSED INTEL-TUT DATA SET}

### 2021-04-02 paper_4.tex
finish 4.3.2

@@
 \subsection{THE PROPOSED INTEL-TUT DATA SET}
+The purpose of the dataset is to help the algorithms to determine if the color 
+constancy value obtained is to be considered good or not. If an algorithm 
+does not find a change in this value on the same set of images taken by the 
+same camera, then this algorithm is able to have a uniform color constancy 
+and consequently would produce optimal outputs.
+
+\subsubsection{Light Sources}
+A variety of devices were used that were capable of producing a light source. 
+Each property such as luminance (Lux), color temperature (CCT) and CIE 
+xy chromaticity, have been appropriately set to have an equitable acquisition.
+
+\subsubsection{Cameras}
+Three types of camera are used for the construction of the dataset. Two 
+of these belong to the high-end, while a third belongs to the category of 
+mobile phones. To achieve correct color correction, several 3x3 size color 
+conversion matrices (\emph{CCMs}) were used. In other words, try to transform 
+the components of the image from RGB to sRGB in order to adapt them to 
+the lighting under which the image is viewed. For the outdoors, 10 CCMs 
+were used based on the type of illumination. Another factor that required 
+correction was the color shading (\emph{CS}). This only requires correction for the 
+images coming from the mobile phone.

### 2021-04-02 paper_4.tex
finish 4.3.5

@@
 of these belong to the high-end, while a third belongs to the category of 
-mobile phones. To achieve correct color correction, several 3x3 size color 
+mobile. To achieve correct color correction, several 3x3 size color 
 conversion matrices (\emph{CCMs}) were used. In other words, try to transform 
@@
 correction was the color shading (\emph{CS}). This only requires correction for the 
-images coming from the mobile phone.
+images coming from the mobile.
+
+\subsubsection{Scene Contents}
+The scenes that make up the dataset are divided into lab scenes and field 
+scenes. There are several types of different lab scenes, each having 5 different 
+illuminations (Fig. \ref{fig:Lab}). Both the lab scenes and those acquired in the field 
+are 64, for a total of 128 scenes. Each lab scene is captured with each camera 
+in almost the same shot. An attempt was made to preserve the same settings 
+in the field scenes even if the latter have different lighting. In order to have 
+good stabilization, a fixed tripod is used.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 0.6 \linewidth]{images/paper4/lab.png}
+    \centering
+    \caption{Lab real scenes}
+    \label{fig:Lab}
+\end{figure}
+
+\subsubsection{Ground Truths}
+The ground-truth is based on the chromaticity of the illumination, or white 
+points, assumed by the camera which can change for each image. This parameter 
+is calculated by averaging the achromatic colors present in the lighter 
+patches of the color-checker, that appear in the last line.
+
+\subsubsection{Recommendations for Evaluating CC Algorithm Performance}
+In order to evaluate the performance of the algorithm with this type of 
+dataset, it is recommended to use the following strategies:
+\begin{enumerate}
+    \item \emph{Camera independence}: the article proposes six-fold cross validation, 
+    where each fold, divided into training, validation and test, contains a 
+    grouping of images for each of the nine cameras. This technique aims 
+    to obtain a fair evaluation of camera-independence of an algorithm (the 
+    algorithm considers all images as if coming from the same camera).
+    \item \emph{Camera and Scene Independence}: in this case it is recommended to 
+    use the images acquired by Nikon and the mobile for training, while 
+    the Canon images must be used for validation. As for the test, it is 
+    recommended to use the Canon images belonging to the second group 
+    of images. In this way you can understand the influence of camera-
+    independence. If you get a low error, which means that the algorithm 
+    treats each scene (each made up of images captured by different cameras) 
+    as if it had been captured entirely by a single camera, then at 
+    this point you would get, in addition to independence of the camera, 
+    the independence of the scene. This is a good result if it is achieved in 
+    this type of dataset.
+    \item \emph{Camera and Scene Independence from Single Camera}: in this strategy 
+    it is suggested to use the images from the second group as training 
+    and validation while using the images acquired by Nikon and the 
+    mobile for testing. In this way we want to understand if the algorithm 
+    obtains the camera/scene independence effect with images produced 
+    by another different camera (Canon). If this technique were 
+    used with the 1 (where a low error implies the achievement of the 
+    camera-independence) then when new images of different origin would 
+    be inserted, the error would be higher than that obtained in 1, this is 
+    because the camera-independence it faces the old set of cameras and not 
+    the new one. It is being said that thanks to the combination of these, 
+    it is possible to have a targeted camera-independence and a targeted 
+    scene-independence for each new camera.
+    \item \emph{Testing the Effect of Color Shading}: if you were to use the images 
+    of your mobile, to test their color shading correction (CS), you could 
+    enclose them all in a test set. Images that cause a high error will be 
+    those that have not undergone the correction process.
+    \item \emph{Testing the Effect of Resolution}: color constancy can be easily calculated when the images are at high resolution.
+As you can guess, this result is not achievable with images from a mobile phone.
+For this reason, the dataset contains a portion of image downscaling (1080p) useful for observing how the resolution can affect the performance of the algorithm.
+\end{enumerate}

### 2021-04-03 paper_4.tex
finish 4.4.1

@@
     those that have not undergone the correction process.
-    \item \emph{Testing the Effect of Resolution}: color constancy can be easily calculated when the images are at high resolution.
-As you can guess, this result is not achievable with images from a mobile phone.
-For this reason, the dataset contains a portion of image downscaling (1080p) useful for observing how the resolution can affect the performance of the algorithm.
+    \item \emph{Testing the Effect of Resolution}: color constancy can be easily calculated 
+    when the images are at high resolution. As you can guess, this 
+    result is not achievable with images from a mobile phone. For this 
+    reason, the dataset contains a portion of image downscaling (1080p) 
+    useful for observing how the resolution can affect the performance of 
+    the algorithm.
 \end{enumerate}
+
+\subsection{EXPERIMENTAL RESULTS}
+\subsubsection{Evaluation of Unsupervised Baseline Methods}
+In summary, in order to have the effect of the camera-independecy on a 
+set of images from different cameras, it is enough to be able to calculate 
+the constancy of the color which, in other words, means having to detect the 
+chromaticity of the illuminate that precisely illuminates the scene. Given the 
+chromaticity estimated by the algorithm ($ p^{Est} $) and the effective chromaticity 
+(white point or ground truth) ($ p^E $), the performance of an algorithm can be 
+evaluated based on the result returned by the recovery angular error (RAE):
+\begin{equation}
+    RAE=\cos^{-1}\left(\frac{p^Ep^{Est}}{||p^E||~||p^{Est}||}\right)
+\end{equation}
+This error index is calculated both on the performances obtained in high 
+resolution images and in those obtained at low resolution. To make some 
+comparison, an algorithm that has a low RAE is the unsupervised algorithm 
+GW \cite{0807099104} which assumes that the average chromaticity in an image is gray. 
+Even the MaxRGB algorithm \cite{0807099103} manages to have good performance 
+in images where there are saturated areas where, thanks to these, the white 
+point can be easily recovered. MaxRGB is currently the only algorithm that 
+manages to have a low RAE even with low quality images (1080p). The 
+performances of these algorithms, together with two others (SoG and GE), 
+are compared in figure \ref{fig:RAE} where for each set of images (Lab 
+Printouts, Lab Real Scenes, $ 1^{st} $ Field Set and $ 2^{nd} $ Field set), taken from different cameras, 
+are calculated mean, median and maximum of RAE values reached for each 
+image. Subsequently, in figure \ref{fig:RAEstandard} the mean, median and maximum of the 
+standard deviation obtained from each image, from each algorithm, are calculated 
+again. As you can see, the GW algorithm is the only one to have the 
+camera-independence for all the rooms used.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper4/RAEHigh.png}
+    \centering
+    \caption{Recovery Angular Errors (Mean, Median and Maximum) of some algorithms.}
+    \label{fig:RAE}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 0.6 \linewidth]{images/paper4/standardHigh.png}
+    \centering
+    \caption{Mean, Median and Maximum RAE of some algorithms.}
+    \label{fig:RAEstandard}
+\end{figure}
+
+\subsubsection{Evaluation of a Direct Supervised Method}

### 2021-04-03 paper_4.tex
finish 4.4.1

@@
 
-\subsubsection{Recommendations for Evaluating CC Algorithm Performance}
+\subsubsection{Recommendations for Evaluating CC Algorithm Performance}\label{recommend}
 In order to evaluate the performance of the algorithm with this type of 
@@
 \subsubsection{Evaluation of a Direct Supervised Method}
+In order to be able to calculate color constancy, and thus be able to achieve 
+the camera-independence, various methods were used that included the use 
+of convolutional neural networks (CNNs). In method \cite{0807099122}, the network used 
+is composed of a convolutional layer with 240 filters of size 1x1, the usual 
+function of ReLU, a max-Pooling of blocks of size 8x8 with stride 8. Finally 
+there is a fully-connected layer with 40 layers hidden and a 3-dimensional 
+output in which there is the estimated chromaticity of the lighting.
+In order to demonstrate the validity of the proposed dataset, the use of CNN has been adapted to the techniques described in \ref{recommend}:
+\begin{enumerate}
+    \item Following technique 1, various CNNs are trained to provide the least 
+    possible error. The error reached by the model is less than when using 
+    the Canon for training and validation. This means that the networks 
+    assume the camera-independence only with the Nikon and mobile models. 
+    Therefore the networks would be able to recognize new cameras. As 
+    can be seen in the figure, the RAE values between the various cameras 
+    are very similar (Fig. \ref{fig:CNNtec1}).
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 1 \linewidth]{images/paper4/CNNtec1.png}
+        \centering
+        \caption{Camera Independence of \cite{0807099122} with CCM on $ 1^{rst} $ thecnique. Mean, Median and Maximum RAE of CNN.}
+        \label{fig:CNNtec1}
+    \end{figure}
+    \item Now a CNN is trained using technique 2. The training is carried out 
+    with images acquired from both Nikon and mobile. Canon's images are 
+    used for validation, while Canon's images belonging to the $ 2^{nd} $ field 
+    are used for the test. Low errors are obtained with the use of a color 
+    conversion matrix (CCM) \cite{0807099129} and therefore the model manages to have 
+    the camera/scene-independence (Fig. \ref{fig:CNNtec2}).
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 0.6 \linewidth]{images/paper4/CNNtec2.png}
+        \centering
+        \caption{Camera Independence of \cite{0807099122} with CCM on $ 2^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
+        \label{fig:CNNtec2}
+    \end{figure}
+    \item According to technique 3, a CNN can be trained to reach camera independence 
+    only on one camera, excluding the others. In this case, since 
+    the images of the $ 2^{nd} $ field, used for both training and validation, belong 
+    only to Canon, then CNN will get the camera/scene-independence 
+    only on this type of camera.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 0.6 \linewidth]{images/paper4/CNNtec3.png}
+        \centering
+        \caption{Camera Independence of \cite{0807099122} on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
+        \label{fig:CNNtec2}
+    \end{figure}
+\end{enumerate}

### 2021-04-03 paper_4.tex
finish 4.4.3

@@
 \end{enumerate}
+
+\subsubsection{A State of the Art Camera Independent Method}
+The following section presents a competitive method \cite{0807099125} that can beat the 
+performance of \cite{0807099122}. Also in this new method there is an even deeper CNN 
+that uses a set of images on which a CCM pre-processing phase has already 
+been applied. The comparisons of the results obtained by \cite{0807099122} and by \cite{0807099125} in 
+all the techniques proposed in \ref{recommend} where it can be seen that all the error 
+rates of \cite{0807099125} are smaller than those of \cite{0807099122} and therefore the model is able to 
+reach the camera/scene-independece more easily.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper4/25tech1.png}
+    \centering
+    \caption{Camera Independence of \cite{0807099122} with CCM on $ 1^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
+    \label{fig:25t1}
+    \begin{minipage}[t]{.45\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{images/paper4/25tech2.png}
+        \caption{\small Camera Independence of \cite{0807099122} on $ 2^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
+    \end{minipage}
+    \hfill
+    \begin{minipage}{.45\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{images/paper4/25tech3.png}
+        \caption{\small Camera Independence of \cite{0807099122} on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
+    \end{minipage}  
+    \label{fig:1-2}
+\end{figure}
+
+\subsection{CONCLUSION}

### 2021-04-05 paper_4.tex
finish paper4

@@
 same camera, then this algorithm is able to have a uniform color constancy 
-and consequently would produce optimal outputs.
+and consequently would produce optimal outputs. Each image in the 
+dataset has undergone several changes such as: black level correction (BLC), 
+color shading correction (CSC) (only for mobile camera), white balance (WB), 
+color conversion from RGB sensor to sRGB (CCM) , gamma correction of 
+0.45, sharpening effect correction (blur) and brightness normalization.
 
@@
     only to Canon, then CNN will get the camera/scene-independence 
-    only on this type of camera.
+    only on this type of camera (Fig. \ref{fig:CNNtec3}).
     \begin{figure}[h!]
@@
         \caption{Camera Independence of \cite{0807099122} on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
-        \label{fig:CNNtec2}
+        \label{fig:CNNtec3}
     \end{figure}
@@
 \subsection{CONCLUSION}
+The dataset proposed in this paper is useful for testing the behavior of an algorithm, or a model based on CNN, in the search of camera/scene-independece.
+If the algorithm manages to obtain this benefit, then it will be able to generalize a scene composed of several images acquired from different cameras, otherwise the results returned by this will be highly variable.
+Achieving this goal can also be done using a CNN if the CMM process is applied to its input set.
+It is necessary to specify that, in order to achieve the final result, it is essential to have the spectral sensitivities of each camera without which it would not be possible to achieve camera independence.

### 2021-04-05 slides.tex
Slide paper4 Evaluations

@@
 \usepackage{subcaption}
+\usepackage{hyperref}
 \captionsetup[figure]{labelsep=period}
@@
 
+\section{Paper 4}
+\subsection{\emph{"A Data Set for Camera-Independent Color Constancy"}}
+
+\begin{frame}{INTRODUCTION}
+    In computer vision, the output generated by an algorithm depends on the 
+    nature of the images set given as input. When the images come from 
+    different sources (e.g. different cameras), the behavior of the algorithm is 
+    not always the same. For this reason, we try to standardize the input in 
+    order to have a more uniform output.
+\end{frame}
+
+\begin{frame}{COLOR CONSTANCY DATASETS}
+    To produce uniform output, an algorithm must achieve "{\bfseries{color 
+    constancy}}" on all input images. In order to calculate this property, there 
+    are supervised and unsupervised algorithms. To test the performance of 
+    these algorithms, there are already state-of-the-art datasets \footfullcite{0807099130} \footfullcite{0807099132} \footfullcite{0807099120}
+    containing indoor and outdoor images, but these have few images inside 
+    them.
+\end{frame}
+
+\begin{frame}{THE PROPOSED INTEL-TUT DATA SET}
+    The purpose of the paper is to present a dataset containing images useful 
+    for researching the {\bfseries{camera/scene-independence}} effect of an algorithm.
+    To achive this, each scene was captured under five different illumination. 
+    In each scene there are images taken from three different cameras, 
+    including a mobile one.
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 0.6 \linewidth]{images/paper4/lab.png}
+        \centering
+        \caption{Lab real scenes}
+        \label{fig:Lab}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Chromaticity}
+    \begin{block}{Chromatic adaptation - \href{https://en.wikipedia.org/wiki/Color_vision}{\underline{Wikipedia}}}
+        \emph{"In color vision, chromatic adaptation refers to color constancy; the 
+        ability of the visual system to preserve the appearance of an object under 
+        a wide range of light sources."}
+    \end{block}
+    The only information available on the light source are: the "\emph{Spectral 
+    Power Distributions}" (SPD) and the "\emph{Spectral Reflectance}" (SR)
+    Thanks to this information, we can obtain the existing chromaticity in the image 
+    and compare it with that obtained from the "\emph{Camera Spectral Senstivities}" (CSS).
+    \begin{block}{Target}
+        The goal is to be able to bring the white point, calculated by each algorithm, closer to the white point of the ground truth, within the same color spectrum (sRGB).
+To do this, a "\emph{Color Conversion Matrix}" (CMM) is used.
+    \end{block}
+\end{frame}
+
+\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Evaluations}
+
+\end{frame}
+
 \end{document}

### 2021-04-05 slides.tex
unsupervised methods

@@
     \begin{block}{Target}
-        The goal is to be able to bring the white point, calculated by each algorithm, closer to the white point of the ground truth, within the same color spectrum (sRGB).
-To do this, a "\emph{Color Conversion Matrix}" (CMM) is used.
+        The goal is to be able to bring the white point, calculated by each 
+        algorithm, closer to the white point of the ground truth, within the same 
+        color spectrum (sRGB). To do this, a "\emph{Color Conversion Matrix}" (CMM) 
+        is used.
     \end{block}
@@
 \begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Evaluations}
+    The performance of supervised and unsupervised methods can be 
+    evaluated with 5 of the following strategies:
+    \begin{enumerate}
+        \item Camera Independence \label{CI}
+        \item Camera and Scene Independence
+        \item Camera and Scene Independence from Single Camera
+        \item Testing the Effect of Color Shading
+        \item Testing the Effect of Resolution
+    \end{enumerate}
+    In each of these strategies, the training set, validation set and testing 
+    set contain, in different positions, different images acquired from different 
+    cameras.
+\end{frame}
 
+\begin{frame}{EXPERIMENTAL RESULTS - Unsupervised methods}
+    \begin{block}{Recover Angluar Error}
+        Given the chromaticity estimated by the algorithm ($ p^{Est} $) and the 
+        effective chromaticity (white point or ground truth) ($ p^E $), the 
+        performance of an algorithm can be evaluated based on the result 
+        returned by the "\emph{Recovery Angular Error}" (RAE):
+        $$ RAE=\cos^{-1}\left(\frac{p^Ep^{Est}}{||p^E||~||p^{Est}||}\right) $$
+    \end{block}
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 0.8 \linewidth]{images/paper4/standardHigh.png}
+        \centering
+        \caption{Mean, Median and Maximum RAE of some algorithms. GW \footfullcite{0807099104} achieves the best performance}
+        \label{fig:RAEstandard}
+    \end{figure}
 \end{frame}

### 2021-04-05 slides.tex
finish slide paper4

@@
         algorithm, closer to the white point of the ground truth, within the same 
-        color spectrum (sRGB). To do this, a "\emph{Color Conversion Matrix}" (CMM) 
+        color spectrum (sRGB). To do this, a "\emph{Color Conversion Matrix}" (CCM) 
         is used.
@@
 
+\begin{frame}{EXPERIMENTAL RESULTS - Supervised methods}
+    Color constancy can also be calculated from convolutional neural networks (\emph{CCNs}) such as the one proposed in \footfullcite{0807099125}
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 1 \linewidth]{images/paper4/25tech1.png}
+        \centering
+        \caption{Camera Independence with CCM on $ 1^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
+        \label{fig:CNNtec1}
+    \end{figure}
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[H]
+                \includegraphics[width=\linewidth]{images/paper4/25tech2.png}
+                \caption{\small Camera Independence on $ 2^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
+            \end{figure}
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[htbp]
+                \centering
+                \includegraphics[width=0.8\linewidth]{images/paper4/25tech3.png}
+                \caption{\small Camera Independence on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
+                \centering
+            \end{figure}
+        \end{minipage}
+    \end{minipage}
+\end{frame}
+
+\begin{frame}{CONCLUSION}
+    The dataset proposed in this paper is useful for testing the behavior of 
+    an algorithm, or a model based on CNN, in the search of camera/scene-independece. 
+    Achieving this goal can also be done using a CNN if the CMM process is 
+    applied to its input set. It is necessary to specify that, in order to 
+    achieve the final result, it is essential to have the spectral sensitivities of each camera 
+    without which it would not be possible to achieve camera independence.
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 0.5 \linewidth]{images/paper4/CSS.png}
+        \centering
+        \caption{Camera Spectral Sensitivities (CSS) of the light sources.}
+        \label{fig:CNNtec1}
+    \end{figure}
+\end{frame}
+
 \end{document}

### 2021-04-05 paper_5.tex
start paper5

\section{An End-to-End Multi-Task and Fusion CNN for Inertial-Based Gait Recognition}

\begin{flushleft}
    \author{
    Rubén Delgrado-Esca$ \tilde{n} $o,
    Francisco M. Castro,
    Julián Ramos Cózar,
    Manuel J. Marín-Jiménez,
    and Nicolás Guil
    }
\end{flushleft}

\begin{center}
    \emph{IEEE DIGITAL OBJECT IDENTIFIER}
\end{center}

\subsection{INTRODUCTION}

### 2021-04-05 paper_5.tex
finish 5.1

@@
 \subsection{INTRODUCTION}
+An individual's gait appears as their own fingerprint. The study of this 
+topic doesn't not only concern the area of medicine, but also that of security 
+and identification. The gating study is based on a non-invasive system that 
+collects patterns without the direct intervention of the subject. The data, 
+which allow the recognition of the gait, are taken by inertial sensors present 
+in a multitude of devices such as smartphones or smartwatches. A system 
+is presented that uses a convolutional neural network (CNN) that uses the 
+data collected by these inertial sensors to be able to predict the subject. The 
+approach followed is the one in figure \ref{fig:preview}. Two extensions have been added 
+to the network. The first deals with merging sensory data, while the second 
+deals with improving the learning process and producing multiple outputs 
+from a single input, thanks to a multi-task scheme. The tasks considered 
+are: identification, gender recognition and age estimation. The dataset used 
+is OU-ISIR gait database \cite{0857651721}.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 0.6 \linewidth]{images/paper5/usecase.png}
+    \centering
+    \caption{A preview of how the model works.}
+    \label{fig:preview}
+\end{figure}
+
+\subsection{RELATED WORK}

### 2021-04-06 paper_5.tex
finish 5.2

@@
 \subsection{RELATED WORK}
+Some methods have placed inertial sensors in different parts of the body 
+such as legs \cite{0857651733}, hips \cite{0857651732}, ankles, or even in objects such as bags [35] and 
+pockets \cite{0857651720}. Other methods \cite{0857651736} directly use all the inertial sensors present 
+in the smartphone. With the advent of deep learning and CNNs, classifying 
+an activity has turned out to be an easier job. The input provided to these 
+networks is either the raw data of the inertial sensors, or the images that 
+represented such data. The entire sequence of data is divided into segments, 
+or windows, in order not to negatively affect the performance of the network. 
+In the following work, a union of all the data produced by inertial sensors is 
+carried out with the multi-task approach in order to provide a single model 
+that uses different inputs to produce different outputs.

### 2021-04-06 paper_5.tex
finish 5.3.1

@@
 are: identification, gender recognition and age estimation. The dataset used 
-is OU-ISIR gait database \cite{0857651721}.
+is OU-ISIR gait database \cite{0857651721}, containing information such as inertial sensors 
+such as accelerometers and gyroscopes.
 \begin{figure}[htbp]
@@
 that uses different inputs to produce different outputs.
+
+\subsection{PROPOSED APPROACH}
+\subsubsection{Problem definition}
+The proposed neural network is able to automatically extract the discriminat 
+features from a gait sequence. There is no data pre-processing phase. The 
+dataset used contains three labels for each fetature, indicating the age, years 
+and gender of the subject, but in addition to this, any type of dataset with 
+labels and sensory data would have been fine. In the following paper the 
+following nomenclature will be used:
+\begin{itemize}
+    \item {\bfseries{\emph{S}}}: input temporal sequence of \emph{D} channel measurements taken by a sensor.
+    \item {\bfseries{$ s_i $}}: sub-sequence of \emph{S} having length \emph{L}, given as input to CNN.
+    \item $ y_i^t $: label of the sub-sequence $ s_i $ and taskt \emph{t}.
+    \item $ g(s_i, \theta ) $: non-linear function applied to $ s_i $ with a set of parameters $ \theta $.
+    \item {\bfseries{$ \hat{y_i} $}}: output of the network for a given $ s_i $ input.
+\end{itemize}
+
+\subsubsection{Initial CNN Architecture}

### 2021-04-06 paper_5.tex
finish 5.3.2

@@
 \subsubsection{Initial CNN Architecture}
+The length of the input is normalized before it can end up on CNN. Each 
+sequence S is divided into U sub-sequences $ s_i $, where $ 1 \leq i \leq U $. However, 
+a sequence is divided into windows having length L, with an overlap of 0\%, 
+where each signal size defines a specific input channel. The number D of 
+channels is useful for defining the 1 x N x D dimension of the filter of the 
+first layer, where N indicates the dimension of the convolution. The proposed 
+convolutional network is composed of 4 convolutional layers and a gradually 
+increasing number of filters. After convolution there are elements such as 
+ReLU, batch normalization (useful for faster learning) and max pooling. After 
+the last convolutional layer, the average is chosen as a pooling operation. 
+Then dropout and fully-connected layers are added with a number of outputs 
+equal to the required classes. The last layer is composed of the Softmax 
+normalization function which returns the probability distribution of each class. 
+To train the model, a cross-entropy is used as a loss function.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper5/architecture.png}
+    \centering
+    \caption{Pipeline for multi-task and multi-sensor learning in a gait-based system}
+    \label{fig:pipeline}
+\end{figure}
+
+\subsubsection{Multi-task Approach}

### 2021-04-07 paper_5.tex
finish 5.3.3

@@
 normalization function which returns the probability distribution of each class. 
-To train the model, a cross-entropy is used as a loss function.
+To train the model, only for the identification task, a cross-entropy is used 
+as a loss function.
 \begin{figure}[htbp]
@@
 \subsubsection{Multi-task Approach}
+The aim is to training a deep multi-task model (DTM). In order to do this, 
+there must be a set of tuples $ I = (s_i, y_i^m, y_1^1, ..., y_i^T) $ where $ y_i^m $ is the label 
+of the main task, $ y_i^t $, with $ t \in [1,T] $, is the label for each auxilary task. 
+Each individual task has its own loss function \emph{L}. The loss function (\ref{loss-function}) is 
+calculated on each sub-sequence \emph{s} and is formed by the product of each single 
+loss function, of each task, with the weights ($ \lambda $)  associated at each task.
+\begin{eqnarray}\label{loss-function}
+    \emph{$ L_{DTM} (g(s,\theta), Y) $} & = & \lambda_{id}L_{id}(\hat{y}^{id}, y^{id}) \nonumber \\
+                                        &   & + \lambda_{age}L_{age}(\hat{y}^{age}, y^{age}) \nonumber \\
+                                        &   & + \lambda_{gender}L_{gender}(\hat{y}^{gender}, y^{gender}) 
+\end{eqnarray}
+Where $ Y = (y^{id}_i, y^{age}_i, y^{gender}_i) $ and $ L_{id}, L_{age}, L_{gender} $ are the loss functions of 
+each tasks. As for the identity and gender tasks, their loss function is the 
+cross-entropy and is calculated with the formula \ref{cross-entropy}.
+\begin{equation}\label{cross-entropy}
+    \emph{$ L_m(\hat{y}, c) $} = -\hat{y}_c+\log\sum^K_{k=1}e^{\hat{y}k} 
+\end{equation}
+Where $ \hat{y} $ is the ouput vector of the network, $ \hat{y}_c $ is the output for target class, 
+$ \hat{y}_k $ is the \emph{k}-th component of the output vector, \emph{c} is the ground-truth class 
+and \emph{K} is the total number of classes.

### 2021-04-07 paper_5.tex
finish 5.3.4

@@
 and \emph{K} is the total number of classes.
+
+\subsubsection{Modality Fusion}
+The merging of data that occurs at the input is useful for increasing the accuracy of the 
+network and allows understanding the relationships between 
+the different types of input data. Each data coming from a specific sensor 
+will be inserted in an individual branch, composed of a specific number of 
+convolutional layers that will calculate specific predictors for each sensor. 
+In the end, the data will be concatenated in a common branch which has the 
+task of extracting the combined features from all the sensors. Based on the accuracy metric, the 
+layer that will return the best result will be selected.
+
+\subsubsection{Identity Authentication}

### 2021-04-07 paper_5.tex
finish 5.4.1

@@
 \subsubsection{Identity Authentication}
+An authentication process begins by submitting a sample of input to CNN. 
+Within this, there may be a layer that will produce a vector of features. 
+To find out which layer it is, a cross-validation process is performed. Once 
+extracted, the features are normalized with the L2 standard. Subsequently 
+a vector is calculated containing the Euclidean distances between the values 
+given in input and those present in the training set. In order to calculate the 
+\emph{Area Under Curve} (AUC) or the \emph{Equal-Error-Rate} (EER), these distances 
+are transformed into probabilities.
+
+\subsection{EXPERIMENTS AND RESULTS}
+\subsubsection{Dataset}
+The OU-ISIR dataset is composed in two parts. Part A contains data on 744 
+individuals, each having two sub-sequence (s) recording at a rate of 100Hz 
+via an IMU sensor located at the waist of each. The first sequence is used for 
+training, the second for testing. The labels associated with each individual 
+are: identity, gender and age (split in ranges). Part B, on the other hand, 
+is composed of 495 individuals with 3 IMU sensors located on the body. For 
+each individual and sensor, there are two sequences of walking levels, an up-slope 
+walk sequence and the other down-slope walk. The data that will be 
+merged are those coming from sensors such as accelerometer and gyroscope.

### 2021-04-07 paper_5.tex
finish 5.4.3

@@
 merged are those coming from sensors such as accelerometer and gyroscope.
+
+\subsubsection{Input data}
+A data augumentation process is carried out to increase the amount of data 
+available for training. In this way, instead of giving a single sequence S 
+as input, three will be given, more precisely:
+\begin{itemize}
+    \item A Gaussian noise is added to the input signal;
+    \item The sequence S is resized with a random value between 0.7 and 1.1;
+    \item A sequence of 10 numbers is first interpolated to S and then the resulting sequence is sampled.
+\end{itemize}
+Each sequence (S) is divided into 100 sub-sequences ($ s_i $) (100Hz = 1 per 
+second), a number enough to contain a walk, with overlap equal to 75\%.
+
+\subsubsection{Implementation details}
+First 100 epochs are performed in order to train the model, with the training 
+set divided into training and validation. At the end of the training, in order to 
+be able to fine-tune the parameters, a further 50 epochs are performed with 
+the training set only. The optimization is carried out with the stochastic 
+gradient descent (SGD) standard with a mini-batch of 128 samples, weigth 
+decay of 0.0005 and a moment of 0.9. The total accuracy is obtained by 
+combining the accuracies derived from the output of each sub-sequence ($ s_i $) 
+of the input S. To obtain this, simply multiply each probability obtained 
+from each of the sub-sequences with the following equation:
+\begin{equation}
+    P(S=c) = \prod_{i=1}^UP_i(s_i=c)
+\end{equation}
+Where U is the number of subsequences $ s_i $, P(s=c) is the probability of assign the identity \emph{c} to the person in sequence S and $ P_i(s_i=c) $ is the probability of assign the identity \emph{c} to teh person in subsequence $ s_i $.
+
+\subsubsection{Gait Recognition experiments}
+\begin{enumerate}
+    \item \emph{Sensor position}: 
+\end{enumerate}

### 2021-04-08 paper_5.tex
working on 5.4.4

@@
 \subsubsection{Gait Recognition experiments}
+Different types of experiments and their respective performances, in terms of accuracy and F1-measure, are presented below.
 \begin{enumerate}
-    \item \emph{Sensor position}: 
+    \item \emph{Sensor position}: the following experiment show that using 3 different 
+    sensors, the model has greater accuracy and a high value of F1-measure, 
+    when using data from the sensor positioned on the left side of the body.
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{*{3}{|c}|}%%{|c|c|c|}
+            \hline
+            IMU Position & Acc & F1-score \\
+            \hline
+            center & 92.3 & 90.8\\
+            left & \bfseries{95.2} & \bfseries{94.0}\\
+            right & 91.5 & 90.0\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Accuracy and F1-score of three different sensors.}
+        \label{table accuracy and F1}
+    \end{table}
+
+    \item \emph{Single task with individuals sensors} (1 Task - 1 Sensor): being a multi-task 
+    network, a CNN network is created for each sensor in combination 
+    with each label. As there are three types of labels and two sensors, a 
+    total of 6 CNN networks are trained. From the results obtained from 
+    the experiment, it can be seen that both sensors affect the model in an 
+    almost similar way, in terms of accuracy and F1-Measure. These values 
+    indicate that both sensors can be used in order to achive the purpose 
+    of identifying the walk.
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{|c||ccc|c||ccc|c|}
+            \hline
+                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
+            \hline
+                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
+            \hline
+                SingleTask Accelerometer & 89.7 & 91.0 & 94.8 & 91.8 & 87.6 & 91.3 & 94.5 & 91.2\\
+                SingleTask Gyroscope& 89.1 & 89.1 & 94.4 & 90.9 & 87.5 & 89.7 & 94.4 & 90.5\\
+            \hline 
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Accuracy and F1-score (1 Task - 1 Sensor).}
+        \label{table accuracy and F1 (1 Task - 1 Sensor)}
+    \end{table}
+
+    \item \emph{Multi-task with individual sensors} (+ Task - 1 Sensor): in this experiment 
+    more tasks are assigned to each of the sensors (3 tasks for 1 
+    sensor) implying the creation of two CNN networks. This experiment 
+    is useful to see if there are any performance improvements with respect 
+    to the single assignment (defined in the previous point). The loss function 
+    is that described in equation \ref{loss-function}. Comparing the results obtained 
+    in table \ref{table accuracy and F1 (1 Task - 1 Sensor)} with table \ref{table accuracy and F1 (more Task - 1 Sensor)}, it can be seen that the following experiment led 
+    to a slight improvement in performance.
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{|c||ccc|c||ccc|c|}
+            \hline
+                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
+            \hline
+                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
+            \hline
+                MultiTask Accelerometer & 90.9 & 93.3 & 95.9 & 93.4 & 89.1 & 93.3 & 95.9 & 92.8\\
+                MultiTask Gyroscope & 90.1 & 90.1 & 94.8 & 91.7 & 88.3 & 90.5 & 94.9 & 91.2\\
+            \hline 
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Accuracy and F1-score (+ Task - 1 Sensor).}
+        \label{table accuracy and F1 (more Task - 1 Sensor)}
+    \end{table}
+
+    \item \emph{Selection of the fusion position}: The fusion can take place in any convolutional 
+    layer, called the common branch, of the network. For each 
+    layer, a number of filters are applied which increases as the 
+    depth of the network increases. As can be seen from table \ref{table accuracy and F1 fusion}, the best performances 
+    are obtained in the fusion obtained in the first convolutional layer of 
+    the network. Subsequent convolutional layers score lower because the 
+    amount of information used for training is low.
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{*{3}{|c}|}%%{|c|c|c|}
+            \hline
+            Position & Acc & F1-score\\
+            \hline
+            Conv1 & \bfseries{94.2} & \bfseries{92.9}\\
+            Conv2 & 94.0 & 92.7\\
+            Conv3 & 93.4 & 92.0\\
+            Conv4 & 89.0 & 86.7\\
+            Conv5 & 89.0 & 86.7\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Accuracy and F1-score of fusion level experiment.}
+        \label{table accuracy and F1 fusion}
+    \end{table}
+
 \end{enumerate}

### 2021-04-08 paper_5.tex
working on 5.4.4

@@
 
-    \item \emph{Single task with individuals sensors} (1 Task - 1 Sensor): being a multi-task 
+    \item \emph{Single task with individuals sensors} (1 Task, 1 Sensor): being a multi-task 
     network, a CNN network is created for each sensor in combination 
@@
         \end{adjustbox}
-        \caption{Accuracy and F1-score (1 Task - 1 Sensor).}
+        \caption{Accuracy and F1-score (1 Task, 1 Sensor).}
         \label{table accuracy and F1 (1 Task - 1 Sensor)}
@@
 
-    \item \emph{Multi-task with individual sensors} (+ Task - 1 Sensor): in this experiment 
+    \item \emph{Multi-task with individual sensors} (+ Task, 1 Sensor): in this experiment 
     more tasks are assigned to each of the sensors (3 tasks for 1 
@@
         \end{adjustbox}
-        \caption{Accuracy and F1-score (+ Task - 1 Sensor).}
+        \caption{Accuracy and F1-score (+ Task, 1 Sensor).}
         \label{table accuracy and F1 (more Task - 1 Sensor)}
@@
 
+    \item \emph{Single Task with Fusion} (1 Task, + Sensor): in this experiment 3 CNNs 
+    are used, one for each task, each making up a branch. In this case, the 
+    combination of data from different sensors will be useful to be able to 
+    determine only 1 task and therefore only one class. The results obtained 
+    are better than the previous points, except for the gender class where 
+    the MultiTask approach achieves a better score.
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{|c||ccc|c||ccc|c|}
+            \hline
+                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
+            \hline
+                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
+            \hline
+                SingleTask Fusion & 94.2 & 95.0 & 95.6 & 94.9 & 93.5 & 95.0 & 95.6 & 94.7\\
+            \hline 
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Accuracy and F1-score (1 Task, + Sensor).}
+        \label{table accuracy and F1 (1 Task, + Sensor)}
+    \end{table}
 \end{enumerate}

### 2021-04-08 paper_5.tex
working on 5.4.4

@@
     \end{table}
+
+    \item \emph{Multi-task with Fusion} (+ Task, + Sensor): the last experiment consists in applying the fusion in a multitasking context within the network.
+In this case it will be necessary to train a CNN for all three existing tasks.
+From the results shown in table \ref{table accuracy and F1 (+ Task, + Sensor)}, this architecture manages to achieve better performance than the others mentioned above, this is because the model has much more information (labels and inputs) to describe people.
+The strength of this architecture is that it manages to return a result for each task.
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{|c||ccc|c||ccc|c|}
+            \hline
+                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
+            \hline
+                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
+            \hline
+                MultiTask Fusion & \bfseries{94.8} & \bfseries{96.1} & \bfseries{97.7} & \bfseries{96.2} & \bfseries{93.8} & \bfseries{96.3} & \bfseries{97.7} & \bfseries{95.9}\\
+            \hline 
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Accuracy and F1-score (1 Task, + Sensor).}
+        \label{table accuracy and F1 (+ Task, + Sensor)}
+    \end{table}
+
 \end{enumerate}

### 2021-04-08 paper_5.tex
finish  5.4.4

@@
 
-\subsubsection{Identity Authentication}
+\subsubsection{Identity Authentication}\label{IA}
 An authentication process begins by submitting a sample of input to CNN. 
@@
     \end{table}
+\end{enumerate}
 
-\end{enumerate}
+\subsubsection{Authentication Experiments}
+In paragraph \ref{IA} we said that to see if two different samples belong to the 
+same subject, an identity authentication process must be carried out. In 
+other words, it is necessary to evaluate the goodness of a model by calculating 
+the AUC and EER index. To do this, one had to first calculate the 
+Euclidean distances between the sample vector present in the test set with 
+the sample vectors present in the training set. Subsequently, it was necessary 
+to transform these distances into probabilities that will be represented 
+on a ROC curve. Once this is done, for each model previously described, 
+the values for AUC (the higher the better) and EER (the lower the better), 
+calculated on the ROC curve, are shown in table \ref{Authentication}. 
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{|c|cc|}
+        \hline
+        Architecture & EER & AUC\\
+        \hline
+        SingleTask Accelerometer & 1.47 & 99.91\\
+        SingleTask Gyroscope & 2.50 & 99.80\\
+        \hline
+        MultiTask Accelerometer & 1.61 & 99.90\\
+        MultiTask Gyroscope & 2.85 & 99.72\\
+        \hline
+        SingleTask Fusion & \bfseries{1.14} & \bfseries{99.93}\\
+        \hline
+        MultiTask Fusion & 1.34 & 99.92\\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Authentication accuracy.}
+    \label{Authentication}
+\end{table}

### 2021-04-08 paper_5.tex
finish paper5

@@
 is OU-ISIR gait database \cite{0857651721}, containing information such as inertial sensors 
-such as accelerometers and gyroscopes.
+such as accelerometers and gyroscopes. Gait recognition can be used in two contexts:
+\begin{enumerate}
+    \item {\bfseries{Identification}}: gait is used to obtain the identity of a known subject.
+    \item {\bfseries{Authentication}}: gait is used to validate the identity of a known subject.
+\end{enumerate}
 \begin{figure}[htbp]
@@
 \subsubsection{Gait Recognition experiments}
-Different types of experiments and their respective performances, in terms of accuracy and F1-measure, are presented below.
+Different types of experiments on recognition, and their respective performances, in terms of accuracy and F1-measure, are presented below.
 \begin{enumerate}
@@
 the values for AUC (the higher the better) and EER (the lower the better), 
-calculated on the ROC curve, are shown in table \ref{Authentication}. 
+calculated on the ROC curve, are shown in table \ref{Authentication}. From the results shown 
+in the table, the multitask model obtains worse performance than the singletask 
+model, this is caused by the fact that in the multitask model the labels 
+to be managed are many more than the single label (id) to be managed in 
+the singletask model.
 \begin{table}[h!]
@@
 \end{table}
+
+\subsubsection{State of art comparison}
+Comparing the proposed system with those already existing in the state of 
+art, both for gait recognition (Tab.\ref{Gait comparison}) and authentication (Tab.\ref{Authentication comparison}), the 
+performances outperforms those of the competitors.
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{|c|ccc|c|}
+        \hline
+        CNN & Id & Age & Gender & Avg\\
+        \hline
+        AE-GDI-CC & 61.0 & - & - & -\\
+        Muaaz et al. & 63.5 & - & - & -\\
+        Ngo et al. & 70.2 & - & - & -\\
+        Wei et al. & 83.8 & - & - & - \\
+        \hline
+        MultiTask Fusion & \bfseries{94.8} & \bfseries{96.1} & \bfseries{97.7} & \bfseries{96.2}\\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Gait recognition comparison with some methods.}
+    \label{Gait comparison}
+\end{table}
+
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{|c|c|}
+        \hline
+        Approach & EER\\
+        \hline
+        Gafurov et al. & 15.8 \\
+        Derawi et al. & 14.3 \\
+        Rong et al. & 14.3 \\
+        Ngo et al. & 13.5 \\
+        Imp GDI + i-vector & 7.1 \\
+        NC GDI + i-vector & 5.6 \\
+        \hline
+        SingleTask Fusion & \bfseries{1.1}\\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Authentication comparison with some methods.}
+    \label{Authentication comparison}
+\end{table}
+
+\subsubsection{Execution time during test}
+MultiTask models are the most time-consuming, but it is also true that they 
+produce three outputs simultaneously (Fig. \ref{fig:time}).
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 0.6 \linewidth]{images/paper5/time.png}
+    \centering
+    \caption{Execution time of the proposed models}
+    \label{fig:time}
+\end{figure}
+
+\subsection{CONCLUSIONS}
+As a final consideration, the model to be used, in the case of gait recognition, 
+is the one that merges the input information and adopts a multitask 
+approach. On the other hand, as regards the authentication problem, it has 
+been seen that it is better to use a singletask model.

### 2021-04-10 slides.tex
start slide paper5

@@
 
+\section{Paper 5}
+\subsection{\emph{"An End-to-End Multi-Task and Fusion CNN for Inertial-Based Gait Recognition"}}
+
+\begin{frame}{INTRODUCTION}
+    The gait recognition is an activity used in the medical, security and 
+    authentication fields. The following paper shows a convolutional neural 
+    network (CNN) which takes as input a series of inertial data, coming 
+    from different sensors, and produces as output a prediction useful for 
+    recognizing a subject.
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 0.6 \linewidth]{images/paper5/usecase.png}
+        \centering
+        \caption{A preview of how the model works.}
+        \label{fig:preview}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{RELATED WORK}
+
+\end{frame}
+
 \end{document}

### 2021-04-10 slides.tex
experiments slide paper 5

@@
 \begin{frame}{RELATED WORK}
+    Some methods have placed inertial sensors in different parts of the body 
+    such as legs \footfullcite{0857651733}, hips \footfullcite{0857651732}, ankles, or even in objects such as bags and 
+    pockets. Other methods \footfullcite{0857651736} directly use all the inertial sensors present in 
+    the smartphone. In the proposed method, the data coming from the 
+    different sensors are merged and sent to the network which will have the 
+    task of predicting some tasks such as: {\bfseries{Identification}}, {\bfseries{age}} and {\bfseries{gender}} of 
+    the subject.
+\end{frame}
 
+\begin{frame}{PROPOSED APPROACH - CNN Architecture}
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 0.8 \linewidth]{images/paper5/architecture.png}
+        \centering
+        \caption{Pipeline for multi-task and multi-sensor learning in a gait-based system}
+        \label{fig:pipeline}
+    \end{figure}
+    The network consists of two branches, one for each sensor (accelerometer 
+    and gyroscope). The Input is split into 3 channels, 1 for each physical 
+    size of the signal (axis x, y and z). After merging the data into a single 
+    branch, the feature vector is extracted and then the three classes are 
+    predicted. The data used are those present in the OU-ISIR dataset \small\footfullcite{0857651721}.
+\end{frame}
+
+\begin{frame}{PROPOSED APPROACH - Multi-Task}
+    A network that manages different labels falls into the category of deep 
+    multitask (\emph{DMT}) networks. To train this network, the sequence S of data 
+    coming in input is splitted into $ s_i $ sub-sequences each of which will be 
+    inserted in a tuple $ I = (s_i, y_i^m, y_1^1, ..., y_i^T) $ where $ y_i^m $ is the label of the 
+    main task, $ y_i^t $, with $ t \in [1,T] $, is the label for each auxilary task. Both 
+    the subsequences $ s_i $ and the tasks have their own loss function. The  total  
+    accuracy  is  obtained  by combining the accuracies derived from the output 
+    of each sub-sequence $ s_i $  of  the  input  S.
+\end{frame}
+
+\begin{frame}{PROPOSED APPROACH - Identity Authentication}
+    Unlike the acknowledgment, the authentication problem aims to see if 
+    two different inputs belong to the same subject. To do this, it is necessary 
+    to calculate the Euclidean distances between the input data and the data 
+    vectors present in the training set. Once this is done, the resulting vector 
+    must be translated into probabilities that will be useful in order to 
+    calculate two indices (Area Under Curve (AUC), Equal-Error-Rate 
+    (EER)) that will be useful for evaluating the CNN network.
+\end{frame}
+
+\begin{frame}{EXPERIMENTS AND RESULTS}
+    For recognition, different types of experiments on different models and 
+    their respective performances in terms of accuracy and F1-measure are 
+    presented below.
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{table}[h!]
+            \centering
+                \begin{adjustbox}{max width=\textwidth}
+                \begin{tabular}{|c||ccc|c||ccc|c|}
+                    \hline
+                        & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
+                    \hline
+                        Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
+                    \hline
+                        SingleTask Accelerometer & 89.7 & 91.0 & 94.8 & 91.8 & 87.6 & 91.3 & 94.5 & 91.2\\
+                        SingleTask Gyroscope& 89.1 & 89.1 & 94.4 & 90.9 & 87.5 & 89.7 & 94.4 & 90.5\\
+                    \hline 
+                \end{tabular}
+                \end{adjustbox}
+                \caption{Accuracy and F1-score (1 Task, 1 Sensor).}
+                \label{table accuracy and F1 (1 Task - 1 Sensor)}
+            \end{table}
+            \centering
+            \begin{table}[h!]
+                \centering
+                \begin{adjustbox}{max width=\textwidth}
+                \begin{tabular}{|c||ccc|c||ccc|c|}
+                    \hline
+                        & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
+                    \hline
+                        Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
+                    \hline
+                        SingleTask Fusion & 94.2 & 95.0 & 95.6 & 94.9 & 93.5 & 95.0 & 95.6 & 94.7\\
+                    \hline 
+                \end{tabular}
+                \end{adjustbox}
+                \caption{Accuracy and F1-score (1 Task, + Sensor).}
+                \label{table accuracy and F1 (1 Task, + Sensor)}
+            \end{table}
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[htbp]
+                \centering
+                \begin{table}[h!]
+                    \centering
+                    \begin{adjustbox}{max width=\textwidth}
+                    \begin{tabular}{|c||ccc|c||ccc|c|}
+                        \hline
+                            & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
+                        \hline
+                            Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
+                        \hline
+                            MultiTask Accelerometer & 90.9 & 93.3 & 95.9 & 93.4 & 89.1 & 93.3 & 95.9 & 92.8\\
+                            MultiTask Gyroscope & 90.1 & 90.1 & 94.8 & 91.7 & 88.3 & 90.5 & 94.9 & 91.2\\
+                        \hline 
+                    \end{tabular}
+                    \end{adjustbox}
+                    \caption{Accuracy and F1-score (+ Task, 1 Sensor).}
+                    \label{table accuracy and F1 (more Task - 1 Sensor)}
+                \end{table}
+                \centering
+                \begin{table}[h!]
+                    \centering
+                    \begin{adjustbox}{max width=\textwidth}
+                    \begin{tabular}{|c||ccc|c||ccc|c|}
+                        \hline
+                            & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
+                        \hline
+                            Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
+                        \hline
+                            MultiTask Fusion & \bfseries{94.8} & \bfseries{96.1} & \bfseries{97.7} & \bfseries{96.2} & \bfseries{93.8} & \bfseries{96.3} & \bfseries{97.7} & \bfseries{95.9}\\
+                        \hline 
+                    \end{tabular}
+                    \end{adjustbox}
+                    \caption{Accuracy and F1-score (1 Task, + Sensor).}
+                    \label{table accuracy and F1 (+ Task, + Sensor)}
+                \end{table}
+            \end{figure}
+        \end{minipage}
+    \end{minipage}
 \end{frame}

### 2021-04-10 slides.tex
finish slide paper5

@@
 
-\begin{frame}{EXPERIMENTS AND RESULTS}
+\begin{frame}{EXPERIMENTS AND RESULTS - Gait recognition}
     For recognition, different types of experiments on different models and 
@@
 
+\begin{frame}{EXPERIMENTS AND RESULTS - Authentication}
+    For identity authentication, on the other hand, the results shown in the table show that for this type of problem the single task model is better than the multi-task model.
+This happens because in this problem a single label (id) is required and not others.
+The introduction of other labels leads the multitask model to have worse accuracy than the single task model.
+The indices AUC (higher is better) and EER (lower is better) are calculated thanks to the probabilities obtained from the Euclidean distance vector.
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{|c|cc|}
+            \hline
+            Architecture & EER & AUC\\
+            \hline
+            SingleTask Accelerometer & 1.47 & 99.91\\
+            SingleTask Gyroscope & 2.50 & 99.80\\
+            \hline
+            MultiTask Accelerometer & 1.61 & 99.90\\
+            MultiTask Gyroscope & 2.85 & 99.72\\
+            \hline
+            SingleTask Fusion & \bfseries{1.14} & \bfseries{99.93}\\
+            \hline
+            MultiTask Fusion & 1.34 & 99.92\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Authentication accuracy.}
+        \label{Authentication}
+    \end{table}
+\end{frame}
+
+\begin{frame}{EXPERIMENTS AND RESULTS - State of the art Comparison}
+    Comparing the proposed system with those already existing in the state 
+    of the art, both for recognition and authentication, the performance, in 
+    terms of accuracy, achieved outperforms those competitors.
+        \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{table}[h!]
+                \centering
+                \begin{adjustbox}{max width=\textwidth}
+                \begin{tabular}{|c|ccc|c|}
+                    \hline
+                    CNN & Id & Age & Gender & Avg\\
+                    \hline
+                    AE-GDI-CC & 61.0 & - & - & -\\
+                    Muaaz et al. & 63.5 & - & - & -\\
+                    Ngo et al. & 70.2 & - & - & -\\
+                    Wei et al. & 83.8 & - & - & - \\
+                    \hline
+                    MultiTask Fusion & \bfseries{94.8} & \bfseries{96.1} & \bfseries{97.7} & \bfseries{96.2}\\
+                    \hline
+                \end{tabular}
+                \end{adjustbox}
+                \caption{Gait recognition comparison with some methods.}
+                \label{Gait comparison}
+            \end{table}
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
+            \begin{table}[h!]
+                \centering
+                \begin{adjustbox}{max width=\textwidth}
+                \begin{tabular}{|c|c|}
+                    \hline
+                    Approach & EER\\
+                    \hline
+                    Gafurov et al. & 15.8 \\
+                    Derawi et al. & 14.3 \\
+                    Rong et al. & 14.3 \\
+                    Ngo et al. & 13.5 \\
+                    Imp GDI + i-vector & 7.1 \\
+                    NC GDI + i-vector & 5.6 \\
+                    \hline
+                    SingleTask Fusion & \bfseries{1.1}\\
+                    \hline
+                \end{tabular}
+                \end{adjustbox}
+                \caption{Authentication comparison with some methods.}
+                \label{Authentication comparison}
+            \end{table}
+        \end{minipage}
+    \end{minipage}
+\end{frame}
+
+\begin{frame}{CONCLUSIONS}
+    As a final consideration, the model to be used, in the case of gait recognition, 
+    is the one that merges the input information and adopts a multitask 
+    approach. On the other hand, as regards the authentication problem, it has 
+    been seen that it is better to use a singletask model.
+\end{frame}
 \end{document}

### 2021-04-10 paper_6.tex
start paper6

\section{Coarse-to-Fine Semantic Segmentation From Image-Level Labels}

\begin{flushleft}
    \author{
    Longlong Jing,
    Yucheng Chen,
    Yingli Tan,
    \emph{Fellow, IEEE}
    }
\end{flushleft}

\begin{center}
    \emph{IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL.29, 2020}
\end{center}

\subsection{INTRODUCTION}

### 2021-04-10 paper_6.tex
finish 6.1 paper6

@@
 \subsection{INTRODUCTION}
+To obtain a semantic segmentation it is necessary to have an annotated 
+training set. Semantic segmentation generally requires pixel-wise semantic 
+annotation techniques which are time-consuming. To solve the annotation 
+problem, weakly supervised and semi-supervised semantic segmentation 
+methods have been proposed. Methods such as object-level labels and image-level 
+labels are used to extract annotations. These annotations are useful for 
+producing datasets useful for training a weakly supervised model, such as 
+the one proposed. By training a weakly supervised semantic segmentation 
+model, with the labels produced, the performances match those of the supervised 
+methods. Unfortunately, methods such as object-level labels produce 
+bounding boxes that are still not precise, so the use of the image-level labels 
+method prevails. The dataset used is that of ImageNet where a category is 
+associated with each image. The proposed model is able to generate as many 
+segmentation masks as there are different objects belonging to different 
+categories in each image. Network training takes place using information such as 
+masks, images and labels of each category. An example of the coarse-to-fine 
+mask produced by the model is the one shown in figure \ref{fig:semanticWork}.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper6/work.png}
+    \centering
+    \caption{Example of semantic segmentation generated by the proposed method.}
+    \label{fig:semanticWork}
+\end{figure}

### 2021-04-10 paper_6.tex
finish 6.2

@@
 mask produced by the model is the one shown in figure \ref{fig:semanticWork}.
-\begin{figure}[htbp]
+\begin{figure}[h!]
     \centering
@@
 \end{figure}
+
+\subsection{RELATED WORK}
+\subsubsection{Semantic Segmentation}
+There are three different types of semantic segmentation methods that differ 
+based on the level of annotation used:
+\begin{enumerate}
+    \item \emph{Fully Supervised Pixel-Wise Annotation-Based Methods}: trained with 
+    pixel-wise labels annotated by people:
+    \item \emph{Weakly Supervised Object-level Annotation-Based-Methods}: trained with 
+    methods such as object-level annotations based on the use of bounding 
+    boxes;
+    \item \emph{Weakly Supervised Image-Level Annotation-Based Methods}: trained 
+    with image category labels.
+\end{enumerate}
+The methods in the first point, if trained with precise labels, are able to 
+obtain the best performances.
+
+\subsubsection{Foreground Segmentation}
+The labels assigned to pixels can be useful to separate a foreground object from a background object.
+Also for this task there are three strategies to perform a segmentation of the objects in the foreground:
+\begin{enumerate}
+    \item \emph{Joint segmentation-based Methods}: used prior knowledge as supervision.
+    \item \emph{Saliency prediction-based Methods}: identify regions present in the human visual scene.
+    \item \emph{Object proposal-based Methods}: locate all objects in images.
+\end{enumerate}
+The proposed framework can also be used for this purpose.

### 2021-04-10 paper_6.tex
finish 6.3.3

@@
 \subsubsection{Foreground Segmentation}
-The labels assigned to pixels can be useful to separate a foreground object from a background object.
-Also for this task there are three strategies to perform a segmentation of the objects in the foreground:
+The labels assigned to pixels can be useful to separate a foreground object 
+from a background object. Also for this task there are three strategies to 
+perform a segmentation of the objects in the foreground:
 \begin{enumerate}
     \item \emph{Joint segmentation-based Methods}: used prior knowledge as supervision.
-    \item \emph{Saliency prediction-based Methods}: identify regions present in the human visual scene.
+    \item \emph{Saliency prediction-based Methods}: identify regions present in the human 
+    visual scene.
     \item \emph{Object proposal-based Methods}: locate all objects in images.
@@
 The proposed framework can also be used for this purpose.
+
+\subsection{THE PROPOSED APPROACH}
+\subsubsection{Overview}
+The work performed by the model is divided into three steps: \emph{coarse mask 
+generation}, \emph{coarse mask enhancement}, and \emph{Recursive mask refinement} (Fig. \ref{fig:step}). In 
+order to generate the initial masks, a CNN is trained and subsequently these 
+are improved with a graph-based model. Images, enhanced masks and lables 
+are used to train the model.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper6/step.png}
+    \centering
+    \caption{Steps of the proposed method.}
+    \label{fig:step}
+\end{figure}
+
+\subsubsection{Coarse Mask Generation}
+The generation of a mask must occur without any information on the labels.
+The CNN present in \cite{0876055520} is used for this purpose. This network is trained 
+with millions of unlabeled images and is also the fastest of other methods 
+existing in the state of the art. Unfortunately, as seen in image \ref{fig:semanticWork}, the 
+generated coarse masks appear to be inaccurate and do not correspond with 
+the position of the underlying object.
+
+\subsubsection{Coarse Mask Enhancement}
+The enhancement of the mask is done before the net training process takes 
+place. To carry out the improvement, the unsupervised GrubCut model \cite{0876055542} 
+is used. This method performs segmentations that divide the background 
+from the foreground using a Gaussian Mixture model to estimate the color 
+distribution of objects. These distributions are used to construct a Markov 
+Random Field on the labels of each pixel. A graph cut optimization has the 
+task of maximizing the search for connected regions having the same label. 
+There are two steps to apply the GrabCut:
+\begin{enumerate}
+    \item search for the smallest bounding box inside the mask.
+    \item enhance the mask based on the previously created bounding box and on the RGB image.
+\end{enumerate}
+The enhanced mask will be used to recursively train the network.

### 2021-04-10 paper_6.tex
finish 6.3.4

@@
 The enhanced mask will be used to recursively train the network.
+
+\subsubsection{Recursive Mask Refinement}
+By combining the labels with the enhanced masks, a semantic segmentation is obtained.
+The purpose is to assign the category label that describes the content to the pixels belonging to the foreground.
+As a semantic segmentation network it was decided to use the one called \emph{DeepLab} \cite{0876055502}.
+This network is trained with the improved masks and has the purpose of generating more and more precise masks, without noise, which will be used as a new training set.
+Enhancing the mask is a recursive process that will end when the system converges to the best representation of the mask.
+The masks are then used as semantic labels to continue training the network.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper6/DeepLab.png}
+    \centering
+    \caption{The process of semantic mask generation.}
+    \label{fig:semanticWork}
+\end{figure}

### 2021-04-10 paper_6.tex
start 6.4

@@
 \subsubsection{Recursive Mask Refinement}
-By combining the labels with the enhanced masks, a semantic segmentation is obtained.
-The purpose is to assign the category label that describes the content to the pixels belonging to the foreground.
-As a semantic segmentation network it was decided to use the one called \emph{DeepLab} \cite{0876055502}.
-This network is trained with the improved masks and has the purpose of generating more and more precise masks, without noise, which will be used as a new training set.
-Enhancing the mask is a recursive process that will end when the system converges to the best representation of the mask.
-The masks are then used as semantic labels to continue training the network.
+By combining the labels with the enhanced masks, a semantic segmentation 
+is obtained. The purpose is to assign the category label that describes the 
+content to the pixels belonging to the foreground. As a semantic segmentation 
+network it was decided to use the one called \emph{DeepLab} \cite{0876055502}. This network 
+is trained with the improved masks and has the purpose of generating more and more 
+precise masks, without noise, which will be used as a new training 
+set. Enhancing the mask is a recursive process that will end when the system 
+converges to the best representation of the mask. The masks are then used 
+as semantic labels to continue training the network.
 \begin{figure}[h!]
@@
 \end{figure}
+
+\subsubsection{Model Parameterization}
+In summary, to generate high-quality semantic segmentation masks, it is 
+required to take an image from the ImgNet dataset and submit it to the 
+following steps:
+\begin{enumerate}
+    \item Create a first mask ($ mask_c $) with a non-superivisoned network \cite{0876055520};
+    \item Improve maskc with the GrabCut model \cite{0876055542} to generate a new mask ($ mask_e $);
+    \item Train DeepLab network \cite{0876055502} with $ mask_e $;
+    \item Generate a better mask ($ mask_r $) using the original ImgNet image;
+    \item Enhance the generated mask ($ mask_e $) by applying the GrubCut method;
+    \item Repeat from step 3 until the best mask will be obtained.
+\end{enumerate}
+
+\subsubsection{Extended the Proposed Framework to Foreground Segmentation}
+In order to use the proposed framework in a foreground object recognition 
+problem, only the part concerning the enhanced of the mask must be replaced 
+with a code that allows to perform the required task. With an architecture 
+similar to \emph{FPN} \cite{0876055543}, the new network is called the \emph{Dilated Feature Pyramid 
+Network} (DFPN). This network has several dilated layers, in three branches, 
+added to enlarge the receptive field of the network (Fig \ref{fig:DFPN}). The features generated 
+by these layers are aggregated to make a prediction.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.8 \linewidth]{images/paper6/DFPN.png}
+    \centering
+    \caption{DFPN architecture.}
+    \label{fig:DFPN}
+\end{figure}
+
+\subsection{EXPERIMENTS}

### 2021-04-11 paper_6.tex
finish 6.4.3

@@
 \subsection{EXPERIMENTS}
+The network is trained with the images and labels present in ImageNet, while 
+the evaluation of the model is carried out on the PASCAL VOC dataset.
+\subsubsection{Datasets}
+\begin{enumerate}
+    \item \emph{ImageNet}: contains about 100,000 labels (synset) annotated by the 
+    human, and each label has at least 1000 related images. Two datasets 
+    useful for training are formed by ImageNet, these are ImageNet-Sub1 
+    and ImageNet-Sub2. The first has a collection of images collected based 
+    on the selected category while the second contains images with categories 
+    that are not present in the VOC dataset that are present in 
+    ImageNet-Sub1.
+    \item \emph{VOC}: dataset containing 21 object categories including background. 
+    The collection is divided into 3 parts: training, validation and test. In 
+    order to be able to evaluate the mask, the results must be sent to the 
+    PASCAL VOC evaluation server. 20 image categories are chosen that 
+    approximate those of ImageNet as the training dataset.
+    \item \emph{MIT Object Discovery Dataset}: this dataset is useful for comparing the 
+    results obtained from segmenting objects in the foreground. There are 
+    at least three categories of objects in the collection.
+\end{enumerate}
+
+\subsubsection{Training Details for Recursive Mask Refinement}
+The Stochastic Gradient Descent mini-batch with a batch size of 12 images 
+is chosen among the parameters. Parameters such as learning rate, momentum 
+and Weight decay are set ad hoc. The training process consists of 5 
+rounds where for each of them the mask is continuously improved. The data 
+augumentation process is present in every training session.
+
+\subsubsection{Evaluation Metrics}
+The \emph{Intersection over Union} (IoU) averaged over 21 categories is used as an evaluation index of the semantic segmentation and foreground segmentation.
+This metric is particularly useful for evaluating the accuracy of the identification of an object.
+Both the predicted mask and the ground truth mask are required for its calculation.
+The IoU index is therefore calculated from the ratio between the area of overlap and the area of union of the two masks.
+Obviously, the higher this index is, the better the predicted mask will be.

### 2021-04-11 paper_6.tex
finish 6.4.4

@@
 \subsubsection{Evaluation Metrics}
-The \emph{Intersection over Union} (IoU) averaged over 21 categories is used as an evaluation index of the semantic segmentation and foreground segmentation.
-This metric is particularly useful for evaluating the accuracy of the identification of an object.
-Both the predicted mask and the ground truth mask are required for its calculation.
-The IoU index is therefore calculated from the ratio between the area of overlap and the area of union of the two masks.
+The \emph{Intersection over Union} (IoU) averaged over 21 categories is used as an 
+evaluation index of the semantic segmentation and foreground segmentation. 
+This metric is particularly useful for evaluating the accuracy of the identification 
+of an object. Both the predicted mask and the ground truth mask 
+are required for its calculation. The IoU index is therefore calculated from 
+the ratio between the area of overlap and the area of union of the two masks. 
 Obviously, the higher this index is, the better the predicted mask will be.
+
+\subsubsection{Semantic Segmentation Results}
+\begin{enumerate}
+    \item \emph{Impact of the mask quality}: as shown in Table \ref{IoU}, the various processing 
+    steps lead to a constant increase in the IoU index. In particular, 
+    the value reached by the index is that relating to the first round of 
+    network training, therefore we proceed recursively with the training of 
+    the network so that it can produce a better mask.
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{|c|c|}
+            \hline
+            Training Mask Type & IoU(\%)\\
+            \hline
+            Coarse Masks & 32.5 \\
+            Bounding Boxes & 35.2 \\
+            Enhanced Masks & 47.7 \\
+            Refined Masks & 50.4 \\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+        \caption{THe performance of semantic segmentation networks evalueted in the validation split of PASCAL VOC dataset in the mean IoU.}
+        \label{IoU}
+    \end{table}
+
+    \item \emph{Effectiveness of recursive refinement}: the evaluation of each refined 
+    mask takes place using two types of masks, with or without application 
+    of the GrabCut. Between two rounds the masks are improved 
+    with a post-processing process by three strategies: a) If the pixels in 
+    the foreground are less than 1\% and greater than 80\%, then this image 
+    will be discarded by the next training round. b) All the pixels 
+    of the original image, labeled with a category must correspond to the 
+    predicted pixels with the same category, otherwise these will be considered 
+    as background pixels. c) In recursive training, the GrubCut 
+    method is applied to the masks that the DeepLab model predicted to 
+    have improved masks. In figure \ref{fig:GrubCutApp} it can be seen that the application 
+    of GrubCut increases the IoU value and also the system saturates after 
+    5 training rounds.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 0.8 \linewidth]{images/paper6/GrabCut.png}
+        \centering
+        \caption{Enhancement with GrubCut application}
+        \label{fig:GrubCutApp}
+    \end{figure}
+
+    \item \emph{Comparison with others}: The performance comparison is carried out on both the validation and test sets of the PASCAL VOC dataset (Fig.
+\ref{fig:IoU score comparison}).
+In the state of the art, models trained with methods based on object-level labels annotation obtain a better score (greater than 60\%) than models trained with methods that have an annotation of the type image-level labels.
+The proposed model, on the other hand, while using the image-level labels annotation method, achieves an average IoU score greater than 60\% on both the evaluation and test sets.
+However, there are several classes in which the model obtains a low IoU value (Fig.
+\ref{fig:classes}).
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 0.6 \linewidth]{images/paper6/comparison.png}
+        \centering
+        \caption{Comparison, in terms of IoU score, between different models.}
+        \label{fig:IoU score comparison}
+    \end{figure}
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 1 \linewidth]{images/paper6/classes.png}
+        \centering
+        \caption{Score of IoU in some classes.}
+        \label{fig:classes}
+    \end{figure}
+\end{enumerate}
+
+\subsubsection{Qualitative Results}

### 2021-04-11 paper_6.tex
finish 6.4.5

@@
 \subsubsection{Qualitative Results}
+Another purpose of the model was to carry out a semantic segmentation also on the different objects, belonging to different categories, present in a single image, in order to be able to distinguish them.
+A small example of multiple segmentation on different objects is shown in figure \ref{fig:segmentationCategories}.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper6/multiple segmentation.png}
+    \centering
+    \caption{Example of semantic segmentation on different categories.}
+    \label{fig:segmentationCategories}
+\end{figure}
+
+\subsubsection{Foreground Segmentations Results}

### 2021-04-11 papers/paper_3.tex
new folders structures

--- 2021-03-31 paper_3.tex
@@
 existing at the state of the art with the proposed method, two compression 
-quality indices were used such as \emph{PSNR} and \emph{SSIM}. With a \emph{QF} set to 5, the ù
-comparison results obtained are shown in figure \ref{fig:QF5}, while the results 
-obtained whit \emph{QF} set to 10 are shown in figure \ref{fig:QF10}
-\begin{figure}[h!]
+quality indices were used such as \emph{PSNR} and \emph{SSIM}. With a \emph{QF} set to 5 and 10, the 
+comparison results obtained are shown in figure \ref{fig:QF5}.
+\begin{figure}[htbp]
     \centering
     \includegraphics[width = 1 \linewidth]{images/paper3/comparison.png}
+    \includegraphics[width = 1 \linewidth]{images/paper3/comparison2.png}
     \centering
-    \caption{JPEG: QF=5, PSNR(db) and SSIM results of alghoritms image deblocking and denoising.}
+    \caption{JPEG: QF=5 and QF=10, PSNR(db) and SSIM results of alghoritms image deblocking and denoising.}
     \label{fig:QF5}
 \end{figure}
+As we can see from figure \ref{fig:QF5}, 
+the most used method in the state of the art \cite{0799924108} blurs the image a lot by 
+losing some detail on the corners, the proposed method has a gain of 1.20db 
+in PSNR, producing compressed images with better quality, and a gain of 
+0.0227 in SSIM indicating a high similarity with the original image. The 
+proposed framework also manages to exceed the performance of the ARCNN 
+\cite{0799924109} method which represents a milestone in this area. The strength of the 
+proposed method is based on obtaining better compression than commonly 
+used codecs, such as \emph{JPEG}, \emph{JPEG2000} and \emph{BPG}, in a variable bit rate 
+range. As we can see from the comparison made in figure \ref{fig:JPEG2000p}, the difference 
+in visual quality between the proposed method and the JPEG2000 codec 
+is considerable. With the same amount of bit rates, the JPEG2000 codec 
+produces worse results by losing several structural information.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper3/JPEG2000p.png}
+    \centering
+    \caption{Performance comparison of JPEG2000 at difference bit rates.}
+    \label{fig:JPEG2000p}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 0.6 \linewidth]{images/paper3/JPEG2000.png}
+    \centering
+    \caption{Average PSNR(dB)/SSIM results of JPEG2000 and the proposed method.}
+    \label{fig:JPEG2000}
+\end{figure}
+As for the BPG codec, 
+if used in combination with the ComCNN and RecCNN networks, it reaches 
+higher PSNR and SSIM levels than when used individually or with only one 
+of the two networks, moreover, on average, it has a saving of about 5.22\% of 
+the amount of bit rate.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = 1 \linewidth]{images/paper3/BPG.png}
+    \centering
+    \caption{BPG: PSNR (dB) and SSIM result of BPG, BPG + RecCNN and the proposed method.}
+    \label{fig:BPG}
+\end{figure}
 
-\begin{figure}[h!]
+\subsubsection{Running Time}
+The execution time of all algorithms, CPU and GPU, are shown in figure \ref{fig:time}. 
+It should be noted that the time reached by the GPU was calculated only 
+for the proposed method. The processed images, in grayscale, are in a size 
+of 256x256. The proposed algorithm appears to be the fastest compared to 
+the others.
+\begin{figure}[htbp]
     \centering
-    \includegraphics[width = 1 \linewidth]{images/paper3/comparison2.png}
+    \includegraphics[width = 1 \linewidth]{images/paper3/time.png}
     \centering
-    \caption{JPEG: QF=10, PSNR(db) and SSIM results of alghoritms image deblocking and denoising.}
-    \label{fig:QF10}
+    \caption{Running time(s) of compared methods in CPU (/GPU) }
+    \label{fig:time}
 \end{figure}
+
+\subsection{CONCLUSION}
+The proposed method seems to have the best performance compared to other 
+methods already existing in the state of the art. The proposed technique 
+then validates the use of one or more convolutional neural networks to carry 
+out the task of encoding and decoding images, even in some cases achieving 
+better quality than existing codecs for image compression.

### 2021-04-11 papers/paper_5.tex
new folders structures

--- 2021-04-08 paper_5.tex
@@
 Some methods have placed inertial sensors in different parts of the body 
-such as legs \cite{0857651733}, hips \cite{0857651732}, ankles, or even in objects such as bags [35] and 
+such as legs \cite{0857651733}, hips \cite{0857651732}, ankles, or even in objects such as bags \cite{0857651735} and 
 pockets \cite{0857651720}. Other methods \cite{0857651736} directly use all the inertial sensors present 

### 2021-04-11 papers/paper_6.tex
new folders structures

--- 2021-04-11 paper_6.tex
@@
         \end{adjustbox}
-        \caption{THe performance of semantic segmentation networks evalueted in the validation split of PASCAL VOC dataset in the mean IoU.}
+        \caption{The performance of semantic segmentation networks evalueted in the validation split of PASCAL VOC dataset in the mean IoU.}
         \label{IoU}
@@
 
-    \item \emph{Comparison with others}: The performance comparison is carried out on both the validation and test sets of the PASCAL VOC dataset (Fig.
-\ref{fig:IoU score comparison}).
+    \item \emph{Comparison with others}: The performance comparison is carried out on both the validation and test sets of the PASCAL VOC dataset (Tab.
+\ref{IoU score comparison}).
 In the state of the art, models trained with methods based on object-level labels annotation obtain a better score (greater than 60\%) than models trained with methods that have an annotation of the type image-level labels.
@@
 \ref{fig:classes}).
-    \begin{figure}[h!]
+    \begin{table}[h!]
         \centering
-        \includegraphics[width = 0.6 \linewidth]{images/paper6/comparison.png}
-        \centering
+        \begin{adjustbox}{max width=0.8\textwidth}
+        \begin{tabular}{|c|c|c|}
+            \hline
+            Methods & mIoU(val) & mIoU(test)\\
+            \hline
+            Supervision: Object-level Labels & &\\
+            SDI \cite{0876055513} & 65.7 & 67.5\\
+            \hline
+            Supervision: Image-level Labels & &\\
+            Bootstrap \cite{0876055555} & 63.0 & 63.9\\
+            \bfseries{The proposed weakly supervised method} & \bfseries{61.9} & \bfseries{62.8}\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
         \caption{Comparison, in terms of IoU score, between different models.}
-        \label{fig:IoU score comparison}
-    \end{figure}
+        \label{IoU score comparison}
+    \end{table}
     \begin{figure}[h!]
@@
 \subsubsection{Qualitative Results}
-Another purpose of the model was to carry out a semantic segmentation also on the different objects, belonging to different categories, present in a single image, in order to be able to distinguish them.
-A small example of multiple segmentation on different objects is shown in figure \ref{fig:segmentationCategories}.
+Another purpose of the model was to carry out a semantic segmentation also 
+on the different objects, belonging to different categories, present in a single 
+image, in order to be able to distinguish them. A small example of multiple 
+segmentation on different objects is shown in figure \ref{fig:segmentationCategories}.
 \begin{figure}[h!]
@@
 \subsubsection{Foreground Segmentations Results}
+Also for the segmentation of objects in the foreground, comparisons were 
+made with existing models of the state of the art. The dataset used this 
+time is that of the MIT Object Discovery unlike the PASCAL VOC used 
+in the previous comparisons. From the performance obtained, the proposed 
+model, which is remembered to be weakly supervised, manages to achieve the 
+performance of the supervised models, with a difference of 2.06\% compared 
+to the supervised \emph{PixelObjectness} model \cite{0876055538}.
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{|c||c|c|c|c||c|c|c|c|}
+        \hline
+        \multirow{2}{*}{\bfseries{Methods}} & \multicolumn{4}{c||}{\bfseries{MIT dataset (subset)}} & \multicolumn{4}{c|}{\bfseries{MIT dataset (full)}} \\            & \bfseries{Ariplane} & \bfseries{Car} & \bfseries{Horse}  & \bfseries{Average} & \bfseries{Ariplane} & \bfseries{Car} & \bfseries{Horse}  & \bfseries{Average} \\
+        \hline
+        \bfseries{\#Images} & 82 & 89 & 93 & N/A & 470 & 1208 & 810 & N/A\\
+        \hline
+        UnsupervisedSeg \cite{0876055520} & 61.37 & 70.52 & 55.09 &62.32 & N/A & N/A & N/A & N/A\\
+        \hline
+        PixelObjectness \cite{0876055538} & 66.43 & 85.07 & 60.85 &70.78 & 66.18 & 84.80 & 64.90 & 71.96\\
+        \hline 
+        \bfseries{FPN-Baseline} & 61.09 & 76.22 & 57.89 & \bfseries{65.08} & 61.93 & 75.94 & 64.03 & \bfseries{67.3}\\
+        \hline
+        \bfseries{Proposed Method} & 64.92 & 77.60 & 60.36 & \bfseries{67.63(+2.57)} & 65.88 & 77.07 & 65.82 & \bfseries{69.59(+2.29)}\\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Quantitative Results of Foreground Segmentation on MIT object Discovery Dataset.}
+    \label{}
+\end{table}
+
+\subsection{CONCLUSION}
+The proposed framework is therefore useful for carrying out a semantic segmentation 
+starting with the mask, identified by an unsupervised network for 
+the identification of objects in the foreground \cite{0876055520}, and then improving it 
+with a fully convolution neural network. The final mask is obtained simply 
+by training the model with the annotated labels for each category. The 
+method also manages to detect multiple masks for each type of category 
+present in each image. It is also possible to identify a foreground object, 
+achieving performance equivalent to that of supervised methods.

### 2021-04-11 slides.tex
new folders structures

--- 2021-04-10 slides.tex
@@
 \logo{\includegraphics[width=0.1\linewidth]{logoUnimi2.png}}
-\section{Paper 1}
-\subsection{\emph{"A Unified Framework for Salient StructureDetection by Contour-Guided Visual Search"}}
-\begin{frame}{INTRODUCTION}
-    The purpose of the paper is to introduce a new method, called CGVS in the 
-    state of the art, which is able to identify regions and salient objects 
-    within a scene simultaneously. The proposed system attempts to 
-    bridge the gap between the two highly related tasks of \emph{"human 
-    fixation"} prediction and \emph{"salient object detection"}, with a general 
-    framework.
-\end{frame}
 
-\begin{frame}{RELATED WORK}
-    To obtain the final result, two pathways are crossed (Fig.\ref{fid: flowchart}):
-    \begin{enumerate}
-        \item Selective
-        \item Non-Selective
-    \end{enumerate}
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 0.8\linewidth]{images/paper1/selective and non-selective pathways.png}
-        \centering
-        \caption{The flowchart of the porposed system.}
-        \label{fid: flowchart}
-    \end{figure}
-\end{frame}
-
-\begin{frame}[t]{CONTOUR-GUIDED VISUAL SEARCH MODEL pt1}
-    In \emph{Non-Selective} pathway are computed:
-    \begin{enumerate}
-        \item \emph{Boundary} \footfullcite{0747815570}
-        \item \emph{Contour-Based Spatial Prior (CBSP)} $ \rightarrow S_w = S_e + S_c $
-    \end{enumerate}
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 0.5\linewidth]{images/paper1/CBSP.png}
-        \centering
-        \caption{CBSP reconstruction.}\vspace{0mm}
-        \label{fid: CBSP}
-    \end{figure}
-    In \emph{Selective} pathway are computed the basic low-level features:
-    \begin{enumerate}
-        \item \emph{Luminance} $ \rightarrow f_{lum} = (r+g+b)/3 $
-        \item \emph{Color-Opponent} $ \rightarrow f_{rg} = r-g , f_{by} = b-(r+g)/2 $
-        \item \emph{Texture Channel} ($ f_{ed} $)
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}[t]{CONTOUR-GUIDED VISUAL SEARCH MODEL pt2}
-    \begin{block}{Bayesian inference}
-        All the previous informations are used to compute the Bayesian inference:
-        $$ p(s|x) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
-    \end{block}
-    Where:
-    \begin{enumerate}
-        \item $ p(x|s) \rightarrow $ likelihood of a pixel at \emph{x} belonging to a salient structure \emph{s}
-        \item $ p(x|b) \rightarrow $ likelihood of a pixel at \emph{x} belonging to the background \emph{b}
-        \item $ p(s) \mbox{ and } p(b)=1-p(s) \rightarrow $ prior probabilities of a pixel at x belonging to a salient structure and the background, respectively.
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}{CONTOUR-GUIDED VISUAL SEARCH MODEL pt3}
-    To compute the prior probabilities, we need:
-    \begin{enumerate}
-        \item \emph{Predict the Size of Potential Structure}: using a optimal threshold ($ T_{opt} $) 
-        useful for separating the background from the foreground (salient structures).
-        \item \emph{Evaluate the Importance of Each Feature}: weighing every salient structure.
-        \item \emph{Calculate the Observation Likelihood:} both $ p(x|s) \mbox{ and } p(x|b) $
-        \item \emph{Enhance the Salient Structure by Iterating}: we re-initialize the prior 
-        function with the smoothed version of $ p(s|x) $ (by median filtering 
-        with a size of 21 × 21 pixels)
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}[t]{EXPERIMENTS}
-    The results obtained on different datasets \footfullcite{PASCAL-S, ECSSD, ASD}, were compared with those 
-    btained by the systems already existing at the state of the art.
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 0.8 \linewidth]{/paper1/metrics.png}
-        \centering
-        \caption{Metrics comparison.}
-        \label{fig: metrics}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{DISCUSSION}
-    It is necessary to say that the results obtained by the proposed method 
-    are obtained using the center bias, which if removed places the system 
-    performance under those of systems such as \emph{RF} \footfullcite{0747815518} and \emph{HS}\footfullcite{0747815508} (which do not 
-    use the central bias). This method offers a dual use. In 
-    a cluttered scene with no dominant objects, the system will function as a 
-    fixation prediction model. Finally, on the other hand, with simple scenes, 
-    the system detects existing relevant objects.
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 0.7 \linewidth]{paper1/SystemsComp.png}
-        \centering
-        \label{fig: metrics}
-    \end{figure}
-\end{frame}
-
-\section{Paper 2}
-\subsection{\emph{"Linear Spectral Clustering Superpixel"}}
-\begin{frame}{INTRODUCTION}
-    The introduced technique is called SUPERPIXEL. Widely used in image 
-    processing for particular tasks such as image segmentation, image analysis, 
-    image classification, target tracking, 3D reconstruction, surface retrieval and 
-    object proposal. The purpose of the elaborate story is to reduce the 
-    computational complexity through a superpixel system called LSC (Linear Spectral
-    Clustering).
-\end{frame}
-
-\begin{frame}{LSC SUPERPIXEL pt1}
-    Goal: optimization (max/min) of two objective functions to create clusters of pixels called superpixels:
-    \begin{block}{Objective Function 1: Weighted K-Means}
-        $$ F_{km} = \sum_{k=1}^K\sum_{p\in\pi_k}\omega(p)= || \phi(p)-m_k ||^2 $$
-    \end{block}
-    \begin{block}{Objective Function 2: Normalized cuts}
-        $$ F_{N_{cuts}} = \frac{1}{K}\sum_{k=1}^K\frac{\sum_{p\in\pi_k}\sum_{q\in\pi_k}W(p,q)}{\sum_{p\in\pi_k}\sum_{q\in{V}}W(p,q)} $$
-    \end{block}
-    Problem: extremely high computational!
-\end{frame}
-
-\begin{frame}{LSC SUPERPIXEL pt2}
-    If corollary 1 is satisfied, then  \emph{weghted K-means clustering} can be used 
-    for segmentation and for creation of superpixel regions, instead of the 
-    eigen-vector based method.
-    \begin{block}{\bfseries{Corollary 1}}
-        Optimizations of the objective functions of the weighted K-means
-        and the normalized cuts are mathematically equivalent if (1) and (2) 
-        hold simultaneously. The symbol $ \cdot $ stands for inner product.
-    \end{block}
-
-    \begin{block}{Equation (1)}
-           $$ \omega(p)\phi(p) \cdot \omega(q)\phi(q) = W(p,q), \forall p,q \in V $$
-    \end{block}
-
-    \begin{block}{Equation (2)}
-        $$ \omega(p) = \sum_{q \in V} W(p,q), \forall p \in V $$
-    \end{block}
-\end{frame}
-
-\begin{frame}{LSC Algorithm pt1}
-    Problem? $ \rightarrow $ Find the correct positive similarity function $ W (p,q) $, 
-    between two data points \emph{p} and \emph{q} to solve equation 1.
-    \begin{block}{Similarity Function}
-        \begin{equation}\small
-            \begin{split}
-                W(p,q) = C_s^2(\cos \frac{\pi}{2}(x_p-x_q)+\cos\frac{\pi}{2}(y_p-y_q)) \\
-                + C_c^2(\cos \frac{\pi}{2}(l_p-l_q)+\cos\frac{\pi}{2}(\alpha_p-\alpha_q) \\
-                + \cos\frac{\pi}{2}(\beta_p-\beta_q)x2.55^2)
-            \end{split}
-        \end{equation}
-    \end{block}
-
-    \begin{block}{Mapping Function}
-        \begin{equation}\small
-            \begin{split}
-                \phi(p) = \frac{1}{\omega(p)}[C_c\cos\frac{\pi}{2}l_p, C_c\sin\frac{\pi}{2}l_p, 2.55C_c\cos\frac{\pi}{2}\alpha_p \\
-                x 2.55C_c\sin\frac{\pi}{2}\alpha_p, 2.55C_c\cos\frac{\pi}{2}\beta_p, 2.55C_c\sin\frac{\pi}{2}\alpha_p, \\
-                x C_s\cos\frac{\pi}{2}x_p, C_s\sin\frac{\pi}{2}x_p, C_s\cos\frac{\pi}{2}y_p, C_s\sin\frac{\pi}{2}x_p]
-            \end{split}
-        \end{equation} 
-    \end{block}
-
-\end{frame}
-
-\begin{frame}{LSC Algorithm pt2}
-    Assuming that equation 1 exists, LSC method takes two parameters as 
-    input; The image to be segmented and the preferred K number of 
-    superpixels that the algorithm will have to produce. The number K 
-    corresponds to the number of centroids and each of these will be useful 
-    for grouping the neighbors pixels, in a range of $ \tau v_x \ x \ \tau v_y $, with $ \tau>0.5 $, 
-    using a distance comparison.
-    \begin{figure}[h!]
-        \centering
-        \includegraphics[width = 0.7 \linewidth]{paper2/slide1.png}
-        \centering
-        \caption{Sample images segmented with K = 1000/500/200 superpixels using LSC.}
-        \label{fig: metrics}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{COMPARATIVE EXPERIMENTS}
-    \begin{table}[htbp!]
-        \centering
-        \begin{adjustbox}{max width=\textwidth}
-        \begin{tabular}{*{9}{|c}|}%%{|c|c|c|c|c|c|c|c|c|}
-            \hline
-            & EneOpt0 & SEEDS\footfullcite{0781426509} & ERS\footfullcite{0781426508} & Lattices & NCuts & SLIC\footfullcite{0781426514} & Turbo & LSC \\
-            \hline
-            \bfseries{ADERENCE TO BOUNDARY} & & & & & & & & \\
-            \emph{Under segmentation error} & 0.230 & 0.197 & 0.198 & 0.303 & 0.220 & 0.213 & 0.277 & \bfseries{0.190}\\
-            \emph{Boundary recall} & 0.765 & 0.918 & 0.920 & 0.811 & 0.789 & 0.837 & 0.739 & \bfseries{0.926}\\
-            \emph{Achievable segmentation accuracy} & 0.950 & 0.960 & 0.959 & 0.933 & 0.956 & 0.956 & 0.943 & \bfseries{0.962}\\
-            \hline
-            \bfseries{SEGMENTATION SPEED} & & & & & & & & \\
-            \emph{Computational complexity} & $ O(N^3/K^2) $ & $ O(N) $ & $ O(N^2 \lg{N}) $ & $ O(N^{\frac{3}{2}} \lg{N}) $ & $ O(N^{\frac{3}{2}}) $ & $ O(N) $ & $ O(N) $ & $ O(N) $\\
-            \emph{Average time per image} & 3.35s & \bfseries{0.0935}s & 0.969s & 0.284s & 93.4s & 0.125s & 6.61s & 0.334s\\
-            \hline
-        \end{tabular}
-        \end{adjustbox}
-        \caption{Performance metrics superpixel segmentation algorithms at K=400}
-        \label{table superpixels}
-    \end{table}
-    Best performance: low "Under segmentation Error" (\emph{UE}), high 
-    "Boundary Recall" (\emph{BR}) and high "Achievable segmentation accuracy 
-    (\emph{ASA}).
-\end{frame}
-
-\begin{frame}{APPLICATIONS: Class segmentation}
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 1 \linewidth]{images/paper2/superpixelAlgo.png}
-        \centering
-        \caption{Segmentation using different superpixels algorithms. (a) Original Image. (b) QS. (c) ERS. (d) SLIC. (e) LSC. (f)Ground Truth.}
-        \label{fig: superpixelSegmentation}
-    \end{figure}
-
-    \begin{table}[h!]
-        \centering
-        \begin{adjustbox}{max width=4cm}
-        \begin{tabular}{*{5}{|c}|}%%{|c|c|c|c|c|}
-            \hline
-            & QS & ERS & SLIC & LSC\\
-            \hline
-            bike & 72.2 & 74.2 & 76.3 & \bfseries{76.9}\\
-            cars & 72.2 & 74.7 & 72.5 & \bfseries{76.8}\\
-            person & 66.3 & 66.5 & 66.7 & \bfseries{67.0}\\
-            \hline
-        \end{tabular}
-        \end{adjustbox}
-        \caption{Accuracy using different superpixels algorithms.}
-        \label{table accuracy}
-    \end{table}
-\end{frame}
-
-\begin{frame}{APPLICATIONS: Weakly Supervised Semantic Segmentation}
-    \begin{minipage}{\linewidth}
-        \centering
-        \begin{minipage}{0.45\linewidth}
-            \begin{figure}[H]
-                \includegraphics[width = 0.7 \linewidth]{images/paper2/semanticSegmentation.png}
-                \caption{Weakly supervised semantic segmentation.
-(a) A training image with bounding boxes.
-(b) Output of soft-max layer of $ FCN_c $.
-(c) Coarse semantic segmentation result.
-(d) Superpixels with higher probability of foreground.
-(e) Fore-/Background segmentation result after iterative optimization.
-(f) Refined semantic segmentation result.}
-            \end{figure}
-        \end{minipage}
-        \hspace{0.05\linewidth}
-        \begin{minipage}{0.45\linewidth}
-            \begin{figure}[htbp]
-                \centering
-                \includegraphics[width = 1 \linewidth]{images/paper2/segmentationAlgo.png}
-                \centering
-                \caption{Semantic segmentation. (a) Input image. (b) Strong. (c) Bbox-seg. (d) $ Joint_{sp} $ (LSC) }
-            \end{figure}
-            \begin{table}[H]
-                \begin{adjustbox}{max width=4cm}
-                    \begin{tabular}{*{3}{|c}|}%%{|c|c|c|}
-                        \hline
-                        Strong\footnotemark[1]& Bbox-seg\footnotemark[1] & $ Joint_{sp} $ \\
-                        \hline
-                        62.5 & 60.6 & \bfseries{64.0} \\
-                        \hline
-                    \end{tabular}
-                \end{adjustbox}
-                \caption{Semantic segmentation accuracy in terms of Mean IOU (\%)}
-            \end{table}
-        \end{minipage}
-    \end{minipage}
-    \footnotetext[1]{\tiny G. Papandreou, L. Chen, K. Murphy, and A. Yuille, “Weakly-and semi-
-    supervised learning of a deep convolutional network for semantic image segmentation,” in Proc. ICCV, pp. 1742–1750, Dec. 2015}
-\end{frame}
-
-\begin{frame}{CONCLUSIONS}
-    The LSC algorithm seems to be the best in terms of adherence to the 
-    boundary and in the creation of superpixels with increasingly regular 
-    shape, but there are still two problems to solve:
-    \begin{enumerate}
-        \item The number K of superpixels entered manually
-        \item New similarity techniques to improve performance
-    \end{enumerate}
-\end{frame}
-
-\section{Paper 3}
-\subsection{\emph{"An End-to-End Compression Framework Based on Convolutional Neural Networks"}}
-
-\begin{frame}{INTRODUCTION}
-    In recent years, within the field of computer vision, remarkable results 
-    have been achieved with regard to image compression. The purpose of 
-    compressionis to be able to transmit, or save, the entire image at low bit 
-    rates. The following article presents a compression method based on 
-    convolutional neural networks (CNNs) which, through the use of various 
-    state-of-the-art codecs, are able to achieve better performance in terms 
-    of compression and image quality.
-\end{frame}
-
-\begin{frame}{RELATED WORK}
-    At the state of the art there are post-processing methods that use 
-    {\bfseries{deblocking}} and {\bfseries{restoring}} techniques \footfullcite{0799924108}. These techniques have a strong 
-    computational impact on systems. These operations focus on eliminating 
-    artifacts and blocks that contain noise within the image. Other methods 
-    use CNNs for {\bfseries{super-resolution}} (SR) images \footfullcite{0799924123}. There are deep learning 
-    methods that are used for {\bfseries{lossy}} \footfullcite{0799924125} or {\bfseries{lossless}} \footfullcite{0799924130} compression of images, but 
-    these ignore the use of the various existing codecs.
-\end{frame}
-
-\begin{frame}{THE PROPOSED COMPRESSION FRAMEWORK pt1}
-    The proposed system is composed of two convolutional neural networks:
-    \begin{enumerate}
-        \item \emph{ComCNN}: used for compact representation of images
-        \item \emph{RecCNN}: used for decoding and reconstruction of images
-    \end{enumerate}
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 0.8 \linewidth]{images/paper3/framework.png}
-        \centering
-        \caption{Up: the ComCNN. Down: the RecCNN. Right: the codec.}
-        \label{fig: framework}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{THE PROPOSED COMPRESSION FRAMEWORK pt2}
-    \begin{minipage}{\linewidth}
-        \centering
-        \begin{minipage}{0.45\linewidth}
-            \begin{figure}[H]
-                \includegraphics[width = 1 \linewidth]{images/paper3/ComCNN.png}
-                \caption{ComCNN architecture.}
-            \end{figure}
-            \begin{block}{Parameter optimizations}
-                \small $$ \hat{\theta_1} = \argmin\limits_{\theta_1}||Re(\hat{\theta_2},Cr(\theta_1,x))-x||^2 $$
-            \end{block}
-            \begin{block}{Loss Function}
-               \tiny $$ L_1(\theta_1) = \frac{1}{2N}\sum_{k=1}^N||Re(\hat{\theta_2}, C_r(\theta1,x_k))-x_k||^2 $$
-            \end{block}
-        \end{minipage}
-        \hspace{0.05\linewidth}
-        \begin{minipage}{0.45\linewidth}
-            \begin{figure}[htbp]
-                \centering
-                \includegraphics[width = 1 \linewidth]{images/paper3/RecCNN.png}
-                \centering
-                \caption{RecCNN architecture.}
-            \end{figure}
-            \begin{block}{Parameter optimizations}
-                \small $$ \hat{\theta_2} = \argmin\limits_{\theta_2}||Re(\hat{\theta_2},\hat{x}_m)-x||^2 $$
-            \end{block}
-            \begin{block}{Loss Function}
-                \tiny $$ L_2(\theta_2) = \frac{1}{2N}\sum_{k=1}^N||res(Co(\hat{x}_{mk}), \theta_2) - (Co(\hat{x}_{mk})-x_k)||^2 $$
-             \end{block}
-        \end{minipage}
-    \end{minipage}
-\end{frame}
-
-\begin{frame}{EXPERIMENTS}
-    The performance comparison is made by citing various techniques present 
-    at the state of the art. A compression quality index ({\bfseries\emph{PSNR}}) and ù
-    an image similarity index ({\bfseries\emph{SSIM}}) are used. What is really important to note 
-    is how the proposed method manages to have better performance than 
-    the already used codecs such as \emph{JPEG}, \emph{JPEG2000} and \emph{BPG}, at different 
-    bit rates (\emph{bpp}) and quality factors (\emph{QS}). As for the execution times, in 
-    terms of CPU / GPU, the proposed algorithm is faster than those already 
-    existing.
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 1 \linewidth]{images/paper3/time.png}
-        \centering
-        \caption{Running time(s) of compared methods in CPU (/GPU) }
-        \label{fig:time}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{EXPERIMENTS: JPEG vs. The proposed system}
-    With a variable QF (first set to 5 and then to 10), the results obtained by 
-    the various methods, in terms of PSNR and SSIM, are shown in the following figures:
-    \begin{minipage}{\linewidth}
-        \centering
-        \begin{minipage}{0.45\linewidth}
-            \begin{figure}[H]
-                \includegraphics[width = 1 \linewidth]{images/paper3/comparison.png}
-                \caption{QF = 5, PSNR(db) and SSIM results of alghoritms image deblocking and denoising}
-            \end{figure}
-        \end{minipage}
-        \hspace{0.05\linewidth}
-        \begin{minipage}{0.45\linewidth}
-            \begin{figure}[htbp]
-                \centering
-                \includegraphics[width = 1 \linewidth]{images/paper3/comparison2.png}
-                \caption{QF = 10, PSNR(db) and SSIM results of alghoritms image deblocking and denoising}
-                \centering
-            \end{figure}
-        \end{minipage}
-    \end{minipage}
-\end{frame}
-
-\begin{frame}{EXPERIMENTS: JPEG2000 vs. The proposed system}
-    As we can see from the comparison made in figure \ref{fig:parrot}, the difference in  
-    visual quality between the proposed method and the JPEG2000 codec is 
-    considerable. With the same amount of bit rates, the JPEG2000 codec 
-    produces worse results by losing several structural information. 
-    \begin{minipage}{\linewidth}
-        \centering
-        \begin{minipage}{0.45\linewidth}
-            \begin{figure}[H]
-                \includegraphics[width = 1 \linewidth]{images/paper3/JPEG2000.png}                
-                \caption{Average PSNR(dB)/SSIM results of JPEG2000 and the proposed method on different datasets.}
-            \end{figure}
-        \end{minipage}
-        \hspace{0.05\linewidth}
-        \begin{minipage}{0.45\linewidth}
-            \begin{figure}[htbp]
-                \centering
-                \includegraphics[width = 1 \linewidth]{images/paper3/JPEG2000p.png}
-                \caption{Performance comparison of JPEG2000 at difference bit rates.}
-                \label{fig:parrot}
-                \centering
-            \end{figure}
-        \end{minipage}
-    \end{minipage}
-\end{frame}
-
-\begin{frame}{EXPERIMENTS: BPG vs. The proposed system}
-    As for the BPG codec, if used in combination with the \emph{ComCNN} and 
-    \emph{RecCNN} networks, it reaches higher \emph{PSNR} and \emph{SSIM} levels than when 
-    used individually or with only one of the two networks.   
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 1 \linewidth]{images/paper3/BPG.png}
-        \centering
-        \caption{BPG: PSNR (dB) and SSIM result of BPG, BPG + RecCNN and the proposed method.}
-        \label{fig:BPG}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{CONCLUSION}
-    The proposed method seems to have the best performance compared to other 
-    methods already existing in the state of the art. The proposed technique 
-    then validates the use of one or more convolutional neural networks to carry 
-    out the task of encoding and decoding images, even in some cases achieving 
-    better quality than existing codecs for image compression.
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 0.5 \linewidth]{images/paper3/final.png}
-        \centering
-        \caption{Visual quality comparison of image deblocking ad different QF.}
-        \label{fig:final comparison}
-    \end{figure}
-\end{frame}
-
-\section{Paper 4}
-\subsection{\emph{"A Data Set for Camera-Independent Color Constancy"}}
-
-\begin{frame}{INTRODUCTION}
-    In computer vision, the output generated by an algorithm depends on the 
-    nature of the images set given as input. When the images come from 
-    different sources (e.g. different cameras), the behavior of the algorithm is 
-    not always the same. For this reason, we try to standardize the input in 
-    order to have a more uniform output.
-\end{frame}
-
-\begin{frame}{COLOR CONSTANCY DATASETS}
-    To produce uniform output, an algorithm must achieve "{\bfseries{color 
-    constancy}}" on all input images. In order to calculate this property, there 
-    are supervised and unsupervised algorithms. To test the performance of 
-    these algorithms, there are already state-of-the-art datasets \footfullcite{0807099130} \footfullcite{0807099132} \footfullcite{0807099120}
-    containing indoor and outdoor images, but these have few images inside 
-    them.
-\end{frame}
-
-\begin{frame}{THE PROPOSED INTEL-TUT DATA SET}
-    The purpose of the paper is to present a dataset containing images useful 
-    for researching the {\bfseries{camera/scene-independence}} effect of an algorithm.
-    To achive this, each scene was captured under five different illumination. 
-    In each scene there are images taken from three different cameras, 
-    including a mobile one.
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 0.6 \linewidth]{images/paper4/lab.png}
-        \centering
-        \caption{Lab real scenes}
-        \label{fig:Lab}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Chromaticity}
-    \begin{block}{Chromatic adaptation - \href{https://en.wikipedia.org/wiki/Color_vision}{\underline{Wikipedia}}}
-        \emph{"In color vision, chromatic adaptation refers to color constancy; the 
-        ability of the visual system to preserve the appearance of an object under 
-        a wide range of light sources."}
-    \end{block}
-    The only information available on the light source are: the "\emph{Spectral 
-    Power Distributions}" (SPD) and the "\emph{Spectral Reflectance}" (SR)
-    Thanks to this information, we can obtain the existing chromaticity in the image 
-    and compare it with that obtained from the "\emph{Camera Spectral Senstivities}" (CSS).
-    \begin{block}{Target}
-        The goal is to be able to bring the white point, calculated by each 
-        algorithm, closer to the white point of the ground truth, within the same 
-        color spectrum (sRGB). To do this, a "\emph{Color Conversion Matrix}" (CCM) 
-        is used.
-    \end{block}
-\end{frame}
-
-\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Evaluations}
-    The performance of supervised and unsupervised methods can be 
-    evaluated with 5 of the following strategies:
-    \begin{enumerate}
-        \item Camera Independence \label{CI}
-        \item Camera and Scene Independence
-        \item Camera and Scene Independence from Single Camera
-        \item Testing the Effect of Color Shading
-        \item Testing the Effect of Resolution
-    \end{enumerate}
-    In each of these strategies, the training set, validation set and testing 
-    set contain, in different positions, different images acquired from different 
-    cameras.
-\end{frame}
-
-\begin{frame}{EXPERIMENTAL RESULTS - Unsupervised methods}
-    \begin{block}{Recover Angluar Error}
-        Given the chromaticity estimated by the algorithm ($ p^{Est} $) and the 
-        effective chromaticity (white point or ground truth) ($ p^E $), the 
-        performance of an algorithm can be evaluated based on the result 
-        returned by the "\emph{Recovery Angular Error}" (RAE):
-        $$ RAE=\cos^{-1}\left(\frac{p^Ep^{Est}}{||p^E||~||p^{Est}||}\right) $$
-    \end{block}
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 0.8 \linewidth]{images/paper4/standardHigh.png}
-        \centering
-        \caption{Mean, Median and Maximum RAE of some algorithms. GW \footfullcite{0807099104} achieves the best performance}
-        \label{fig:RAEstandard}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{EXPERIMENTAL RESULTS - Supervised methods}
-    Color constancy can also be calculated from convolutional neural networks (\emph{CCNs}) such as the one proposed in \footfullcite{0807099125}
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 1 \linewidth]{images/paper4/25tech1.png}
-        \centering
-        \caption{Camera Independence with CCM on $ 1^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
-        \label{fig:CNNtec1}
-    \end{figure}
-    \begin{minipage}{\linewidth}
-        \centering
-        \begin{minipage}{0.45\linewidth}
-            \begin{figure}[H]
-                \includegraphics[width=\linewidth]{images/paper4/25tech2.png}
-                \caption{\small Camera Independence on $ 2^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
-            \end{figure}
-        \end{minipage}
-        \hspace{0.05\linewidth}
-        \begin{minipage}{0.45\linewidth}
-            \begin{figure}[htbp]
-                \centering
-                \includegraphics[width=0.8\linewidth]{images/paper4/25tech3.png}
-                \caption{\small Camera Independence on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
-                \centering
-            \end{figure}
-        \end{minipage}
-    \end{minipage}
-\end{frame}
-
-\begin{frame}{CONCLUSION}
-    The dataset proposed in this paper is useful for testing the behavior of 
-    an algorithm, or a model based on CNN, in the search of camera/scene-independece. 
-    Achieving this goal can also be done using a CNN if the CMM process is 
-    applied to its input set. It is necessary to specify that, in order to 
-    achieve the final result, it is essential to have the spectral sensitivities of each camera 
-    without which it would not be possible to achieve camera independence.
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 0.5 \linewidth]{images/paper4/CSS.png}
-        \centering
-        \caption{Camera Spectral Sensitivities (CSS) of the light sources.}
-        \label{fig:CNNtec1}
-    \end{figure}
-\end{frame}
-
-\section{Paper 5}
-\subsection{\emph{"An End-to-End Multi-Task and Fusion CNN for Inertial-Based Gait Recognition"}}
-
-\begin{frame}{INTRODUCTION}
-    The gait recognition is an activity used in the medical, security and 
-    authentication fields. The following paper shows a convolutional neural 
-    network (CNN) which takes as input a series of inertial data, coming 
-    from different sensors, and produces as output a prediction useful for 
-    recognizing a subject.
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width = 0.6 \linewidth]{images/paper5/usecase.png}
-        \centering
-        \caption{A preview of how the model works.}
-        \label{fig:preview}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{RELATED WORK}
-
-\end{frame}
+\input{slides/slides_paper1.tex}
+\input{slides/slides_paper2.tex}
+\input{slides/slides_paper3.tex}
+\input{slides/slides_paper4.tex}
+\input{slides/slides_paper5.tex}
+\input{slides/slides_paper6.tex}
 

### 2021-04-11 slides/slides_paper1.tex
new folders structures

\section{Paper 1}
\subsection{\emph{"A Unified Framework for Salient StructureDetection by Contour-Guided Visual Search"}}
\begin{frame}{INTRODUCTION}
    The purpose of the paper is to introduce a new method, called CGVS in the 
    state of the art, which is able to identify regions and salient objects 
    within a scene simultaneously. The proposed system attempts to 
    bridge the gap between the two highly related tasks of \emph{"human 
    fixation"} prediction and \emph{"salient object detection"}, with a general 
    framework.
\end{frame}

\begin{frame}{RELATED WORK}
    To obtain the final result, two pathways are crossed (Fig.\ref{fid: flowchart}):
    \begin{enumerate}
        \item Selective
        \item Non-Selective
    \end{enumerate}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8\linewidth]{images/paper1/selective and non-selective pathways.png}
        \centering
        \caption{The flowchart of the porposed system.}
        \label{fid: flowchart}
    \end{figure}
\end{frame}

\begin{frame}[t]{CONTOUR-GUIDED VISUAL SEARCH MODEL pt1}
    In \emph{Non-Selective} pathway are computed:
    \begin{enumerate}
        \item \emph{Boundary} \footfullcite{0747815570}
        \item \emph{Contour-Based Spatial Prior (CBSP)} $ \rightarrow S_w = S_e + S_c $
    \end{enumerate}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.5\linewidth]{images/paper1/CBSP.png}
        \centering
        \caption{CBSP reconstruction.}\vspace{0mm}
        \label{fid: CBSP}
    \end{figure}
    In \emph{Selective} pathway are computed the basic low-level features:
    \begin{enumerate}
        \item \emph{Luminance} $ \rightarrow f_{lum} = (r+g+b)/3 $
        \item \emph{Color-Opponent} $ \rightarrow f_{rg} = r-g , f_{by} = b-(r+g)/2 $
        \item \emph{Texture Channel} ($ f_{ed} $)
    \end{enumerate}
\end{frame}

\begin{frame}[t]{CONTOUR-GUIDED VISUAL SEARCH MODEL pt2}
    \begin{block}{Bayesian inference}
        All the previous informations are used to compute the Bayesian inference:
        $$ p(s|x) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
    \end{block}
    Where:
    \begin{enumerate}
        \item $ p(x|s) \rightarrow $ likelihood of a pixel at \emph{x} belonging to a salient structure \emph{s}
        \item $ p(x|b) \rightarrow $ likelihood of a pixel at \emph{x} belonging to the background \emph{b}
        \item $ p(s) \mbox{ and } p(b)=1-p(s) \rightarrow $ prior probabilities of a pixel at x belonging to a salient structure and the background, respectively.
    \end{enumerate}
\end{frame}

\begin{frame}{CONTOUR-GUIDED VISUAL SEARCH MODEL pt3}
    To compute the prior probabilities, we need:
    \begin{enumerate}
        \item \emph{Predict the Size of Potential Structure}: using a optimal threshold ($ T_{opt} $) 
        useful for separating the background from the foreground (salient structures).
        \item \emph{Evaluate the Importance of Each Feature}: weighing every salient structure.
        \item \emph{Calculate the Observation Likelihood:} both $ p(x|s) \mbox{ and } p(x|b) $
        \item \emph{Enhance the Salient Structure by Iterating}: we re-initialize the prior 
        function with the smoothed version of $ p(s|x) $ (by median filtering 
        with a size of 21 × 21 pixels)
    \end{enumerate}
\end{frame}

\begin{frame}[t]{EXPERIMENTS}
    The results obtained on different datasets \footfullcite{PASCAL-S, ECSSD, ASD}, were compared with those 
    btained by the systems already existing at the state of the art.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8 \linewidth]{/paper1/metrics.png}
        \centering
        \caption{Metrics comparison.}
        \label{fig: metrics}
    \end{figure}
\end{frame}

\begin{frame}{DISCUSSION}
    It is necessary to say that the results obtained by the proposed method 
    are obtained using the center bias, which if removed places the system 
    performance under those of systems such as \emph{RF} \footfullcite{0747815518} and \emph{HS}\footfullcite{0747815508} (which do not 
    use the central bias). This method offers a dual use. In 
    a cluttered scene with no dominant objects, the system will function as a 
    fixation prediction model. Finally, on the other hand, with simple scenes, 
    the system detects existing relevant objects.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.7 \linewidth]{paper1/SystemsComp.png}
        \centering
        \label{fig: metrics}
    \end{figure}
\end{frame}

### 2021-04-11 slides/slides_paper2.tex
new folders structures

--- 2021-03-28 paper_2.tex
@@
-\section{Linear Spectral Clustering Superpixel}
-
-\begin{flushleft}
-    \author{
-    Jiansheng Chen, 
-    \emph{Member, IEEE}, 
-    Zhengqin Li,
-    \emph{Student Member, IEEE}, 
-    Bo Huang 
-}
-\end{flushleft}
-
-\begin{center}
-    \emph{IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL. 26, NO. 7, JULY 2017}
-\end{center}
-
-\subsection{INTRODUCTION}
+\section{Paper 2}
+\subsection{\emph{"Linear Spectral Clustering Superpixel"}}
+\begin{frame}{INTRODUCTION}
     The introduced technique is called SUPERPIXEL. Widely used in image 
@@
     image classification, target tracking, 3D reconstruction, surface retrieval and 
-object proposal. The purpose of this technique is to be able to group the 
-pixels into groups that delimit the edges of an object in order to be able 
-to extract its content. Compared to other methods already existing in the 
-state of the art, characteristics such as size, number of superpixels and shape 
-are not considered. The purpose of the elaborate story is to reduce the 
-computational complexity. The three targets that must be satisfied by each 
-superpixel algorithm are:
-\begin{enumerate}
-    \item Adhere well to the edges without forming overlaps on objects;
-    \item Have a pre-processing technique useful to improve efficiency;
-    \item Consider global information.
-\end{enumerate}
-The proposed system, called Linear Spectral Clustering (LSC), manages to 
-satisfy all the previous points with a high memory efficiency. In LSC, each 
-pixel is mapped to a point within a ten-dimensional space of characteristics 
-in which the weighted K-means is applied for segmentation.
+    object proposal. The purpose of the elaborate story is to reduce the 
+    computational complexity through a superpixel system called LSC (Linear Spectral
+    Clustering).
+\end{frame}
 
-\subsection{LSC SUPERPIXEL}
-The study focuses on the relationships between the results returned by the 
-optimization functions, and those returned by two other equations. If the results 
-are equivalent, then weighted k-means clustering can replace the highly 
-complex eigen based method.
+\begin{frame}{LSC SUPERPIXEL pt1}
+    Goal: optimization (max/min) of two objective functions to create clusters of pixels called superpixels:
+    \begin{block}{Objective Function 1: Weighted K-Means}
+        $$ F_{km} = \sum_{k=1}^K\sum_{p\in\pi_k}\omega(p)= || \phi(p)-m_k ||^2 $$
+    \end{block}
+    \begin{block}{Objective Function 2: Normalized cuts}
+        $$ F_{N_{cuts}} = \frac{1}{K}\sum_{k=1}^K\frac{\sum_{p\in\pi_k}\sum_{q\in\pi_k}W(p,q)}{\sum_{p\in\pi_k}\sum_{q\in{V}}W(p,q)} $$
+    \end{block}
+    Problem: extremely high computational!
+\end{frame}
 
-\subsubsection{Mathematical Backgrounds}
-The task of LSC is to discover the relationships that exist between the objective 
-functions ($ F_{N_{cuts}} $) (\ref{FNcuts}), of the normalized cuts, and the objective functions 
-of the weighted K-means ($ F_{km}$) (\ref{Fkm}). 
-\begin{equation} \label{Fkm}
-    F_{km} = \sum_{k=1}^K\sum_{p\in\pi_k}\omega(p)= || \phi(p)-m_k ||^2 
-\end{equation}
-\begin{equation} \label{Centroid}
-    m_k = \frac{\sum_{q\in\pi_k}\omega(q)\phi(q)}{\sum_{q\in\pi_k}\omega(q)}
-\end{equation}
-\begin{equation} \label{FNcuts}
-    F_{N_{cuts}} = \frac{1}{K}\sum_{k=1}^K\frac{\sum_{p\in\pi_k}\sum_{q\in\pi_k}W(p,q)}{\sum_{p\in\pi_k}\sum_{q\in{V}}W(p,q)}
-\end{equation}
-Where $ m_k $ (\ref{Centroid}) represent the average point, or centroid, of each cluster. Within 
-the formulation of normalized cuts, each data Point corresponds to a node 
-within a graph \emph{G = (V, E, W)} where \emph{V} is the set of all nodes, \emph{E} represents 
-the set of all edges connected and \emph{W} represents the result returned by a 
-similarity function between nodes. The criterion of normalized cuts is based 
-on maximizing the $ F_{N_{cuts}} $ function. The minimization or maximization problems 
-are called \emph{optimization problems} which can be solved by using a positive kernel of 
-a matrix. To see the relationship between the two functions, the Dhillon's concept \cite{0781426526} is extended, to obtain {\bfseries Corollary \ref{Corollary1}}:
+\begin{frame}{LSC SUPERPIXEL pt2}
+    If corollary 1 is satisfied, then  \emph{weghted K-means clustering} can be used 
+    for segmentation and for creation of superpixel regions, instead of the 
+    eigen-vector based method.
+    \begin{block}{\bfseries{Corollary 1}}
+        Optimizations of the objective functions of the weighted K-means
+        and the normalized cuts are mathematically equivalent if (1) and (2) 
+        hold simultaneously. The symbol $ \cdot $ stands for inner product.
+    \end{block}
 
-\begin{corollary} \label{Corollary1}
-    Optimizations of the objective functions of the weighted K-means
-    and the normalized cuts are mathematically equivalent if (\ref{eq4}) and (\ref{eq5}) 
-    hold simultaneously. The symbol $ \cdot $ stands for inner product.
-\end{corollary}
+    \begin{block}{Equation (1)}
+           $$ \omega(p)\phi(p) \cdot \omega(q)\phi(q) = W(p,q), \forall p,q \in V $$
+    \end{block}
 
-\begin{equation} \label{eq4}
-    \omega(p)\pi(p) \cdot \omega(q)\pi(q) = W(p,q), \forall p,q \in V
-\end{equation}
+    \begin{block}{Equation (2)}
+        $$ \omega(p) = \sum_{q \in V} W(p,q), \forall p \in V $$
+    \end{block}
+\end{frame}
 
-\begin{equation} \label{eq5}
-    w(p) = \sum_{q \in V} W(p,q), \forall p \in V
-\end{equation}
-
-After making various derivative calculations, $ F_{km} $ can be seen as: 
-\begin{equation}
-    F_{km} = C - K * F_{N_{cuts}} 
-\end{equation}
-
-From the above definition it is possible to note that the minimization of 
-$ F_{km} $ is equivalent to the maximization of $ F_{N_{cuts}} $. Specifically, both $ F_{km} $ and 
-$ F_{km} $ perform an identical partitioning of the n-dimensional space defined by 
-the function $ \phi $.
-
-\subsubsection{LSC Algorithm}
-The purpose of LSC is to find the correct positive function W (p, q) in order 
-to satisfy {\emph{Corollary \ref{Corollary1}}}. To achieve this, the Euclidean distance calculation 
-was used as an index of similarity between two pixels. Each pixel \emph{p} is represented 
-by five dimensional vectors \emph{(l, a, b, x, y)} in the CIELAB color space, where \emph{l} 
-epresents brightness, \emph{a} and \emph{b} represent opposite colors and \emph{x} and \emph{y} represent
-the coordinates of the plane. The similarity function, in order to satisfy 
-the positivity condition required by (\ref{eq4}), is extended as a convergent Fourier series: 
-\begin{equation}
+\begin{frame}{LSC Algorithm pt1}
+    Problem? $ \rightarrow $ Find the correct positive similarity function $ W (p,q) $, 
+    between two data points \emph{p} and \emph{q} to solve equation 1.
+    \begin{block}{Similarity Function}
+        \begin{equation}\small
             \begin{split}
@@
         \end{equation}
-Where $ C_s $ and $ C_c $ are used to control the relative significance of
-color and spatial information. The mapping function that maps a point in a ten-dimensional
-space is as follows:
-\begin{equation}
+    \end{block}
+
+    \begin{block}{Mapping Function}
+        \begin{equation}\small
             \begin{split}
@@
         \end{equation} 
-In the defined space, the weighted K-mean clustering as well as being 
-equivalent to the Fncuts optimization function, creates the optimal context to 
-optimize it. The LCS algorithm takes two parameters as input; The image 
-to be segmented and the preferred K number of superpixels that the 
-algorithm will have to produce. Each \emph{K} pixel represents the central search point 
-and its vector will be used as the weighted initial vector of the corresponding 
-cluster. Each pixel is assigned to te cluster for which the weightedd mean 
-is closet to the picel's vector in the ten-dimensional feature space. At each 
-assignment, the weighted average and the central point will be updated until 
-the system convergence. Each cluster will form a superpixel and each of 
-these, if considered spatially small, can be joined to other clusters to form 
-a larger cluster. The total complexity achieved by LSC is \emph{O(kN + nZ)}, where 
-\emph{k} represents the number of iterations, \emph{N} the number of pixels, \emph{n} the average 
-number of adjacent neighbors and \emph{z} represents the number of small 
-isolated superpixels to be joined. This complexity, when compared with that 
-achieved by other superpixel systems, is the lowest.
+    \end{block}
 
-\subsection{COMPARATIVE EXPERIMENTS}
-In order to evaluate the quantitative goodness of the proposed algorithm, 
-three comparison metrics are used: under segmentation error (\emph{UE}) \cite{0781426514}, boundary 
-recall (\emph{BR}) and achievable segmentation accuracy (\emph{ASA}). The 
-goal is to have a low UE value, while it is preferable to have high values in BR 
-and ASA. A low percentage of UE indicates that the detected boundary is made 
-up of a small amount of pixels not belonging to the object to be delimited. 
-A segmentation is correct when at least two boundary pixel fall from at least 
-one superpixel boundary point. A high BR index indicates that the better 
-segmentation is obtained. On the other hand, the ASA metric indicates the 
-level of accurancy achieved in the segmentation pashe of contour, obtained 
-thanks to the various labels (ground-truth) placed on each superpixel. A 
-high ASA value indicates that superpixel adapt well to objects. The experiments 
-were conducted on a set of 300 images belonging to the Barkeley 
-Segmentation Database \cite{0781426515}.
+\end{frame}
 
-\subsubsection{Parameter Selection}
-When the ratio $ r = C_s / C_c $ is high, then the neighboring pixels tend to be 
-aggregated into a single cluster, forming superpixels with a regular shape 
-and therefore potentially incorrect. On the other hand, when \emph{r} is small, 
-then it means that the pixels tend to have similar colors, therefore both 
-will be grouped into a single cluster, forming irregular superpixels. In order to 
-choose an optimal r value, it is necessary to introduce a metric that calculates 
-the average  values of shape regularity. The average value of shape regularity 
-is measured with a metric called superpixel compactness \emph{(CP)} \cite{0781426533} which is 
-inversely proportional to the BR index. So as CP increases, the likelihood 
-of regular shapes being created is greater and at the same time worse segmentation 
-will be generated as BR decreases. The r value will be chosen 
-when the value resulting from $ (1-BR / CP) $ is the lowest. Therefore \emph{r} can be 
-used as a correction parameter. In order to control the search range of the 
-K-means cluster algorithm, a $ \tau $ parameter is used which is equal to at least 
-0.5. This value will be multiplied by the spatial components, vertical ($ v_x $) 
-and horizontal ($ v_y $), of the vector belonging to each point in space. Clearly, 
-as this parameter increases, the size of each superpixel generated and the 
-general $ O(N) $ complexity will increase. In the experiments conducted, $ \tau $ is 
-set to 1.
+\begin{frame}{LSC Algorithm pt2}
+    Assuming that equation 1 exists, LSC method takes two parameters as 
+    input; The image to be segmented and the preferred K number of 
+    superpixels that the algorithm will have to produce. The number K 
+    corresponds to the number of centroids and each of these will be useful 
+    for grouping the neighbors pixels, in a range of $ \tau v_x \ x \ \tau v_y $, with $ \tau>0.5 $, 
+    using a distance comparison.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 0.7 \linewidth]{paper2/slide1.png}
+        \centering
+        \caption{Sample images segmented with K = 1000/500/200 superpixels using LSC.}
+        \label{fig: metrics}
+    \end{figure}
+\end{frame}
 
-\subsubsection{Comparison With State-of-the-Art}
-The proposed system is compared with other existing superpixels algorithms 
-in the state of the art. A comparison, in terms of boundary adherence and 
-speed in segmentation (Table \ref{table superpixels}), when the number of superpixels \emph{K} generated 
-is 400. With a relatively high \emph{K} number, LSC achieves the best 
-performance.
-
-\begin{table}[h!]
+\begin{frame}{COMPARATIVE EXPERIMENTS}
+    \begin{table}[htbp!]
         \centering
@@
             \hline
-        & EneOpt0 & SEEDS & ERS & Lattices & NCuts & SLIC & Turbo & LSC \\
+            & EneOpt0 & SEEDS\footfullcite{0781426509} & ERS\footfullcite{0781426508} & Lattices & NCuts & SLIC\footfullcite{0781426514} & Turbo & LSC \\
             \hline
@@
     \end{table}
-As we can see from the results, the worst algorithm, in terms of time, 
-is \emph{NCuts}, while a good algorithm, which ranks second before \emph{LSC}, is \emph{SLIC}. 
-Unlike the algorithm studied, SLIC uses an iterative K-means clustering 
-performed inside different feature spaces, based only on local characteristics. 
-On the other hand, LSC is able to use local and global features thanks to the 
-$ \phi $  mapping function, all to have a better segmentation. However, when 
-K = 400, the CP value of the \emph{ERS} \cite{0781426508} and \emph{SEEDS} \cite{0781426509} algorithms are 0.151 
-and 0.280 respectively, while the CP value of LSC is 0.366. Looking at the data 
-in the table, this makes us understand how LSC is able to have a better BR 
-value despite having a higher CP value than the previous algorithms, this 
-represents the strength of this algorithm.
+    Best performance: low "Under segmentation Error" (\emph{UE}), high 
+    "Boundary Recall" (\emph{BR}) and high "Achievable segmentation accuracy 
+    (\emph{ASA}).
+\end{frame}
 
+\begin{frame}{APPLICATIONS: Class segmentation}
     \begin{figure}[htbp]
         \centering
-    \includegraphics[width = 1 \linewidth]{images/paper2/superpixelsComparison.png}
+        \includegraphics[width = 1 \linewidth]{images/paper2/superpixelAlgo.png}
         \centering
-    \caption{Superpixel results from different algorithms. (a) SEEDS. (b) NCuts. (c) SLIC. (d) ERS. (e) LSC.}
-    \label{fig: superpixelsComparison}
+        \caption{Segmentation using different superpixels algorithms. (a) Original Image. (b) QS. (c) ERS. (d) SLIC. (e) LSC. (f)Ground Truth.}
+        \label{fig: superpixelSegmentation}
     \end{figure}
 
-\subsection{APPLICATIONS}
-\subsubsection{Class Segmentation}
-An SVM-based multi-class object classifier trained on the histograms of the generated 
-superpixels was used. In order for similar superpixels to have the same 
-label, a conditional random field (CRF) is used to refine the segmentation. 
-Thanks to this model, the prediction made by the classifier will also 
-take into account the neighbors superpixels to the one to be labeled. The 
-method used is that proposed in \cite{0781426534} where the main unit of measurement is 
-that of the superpixel. In \cite{0781426534} the quick shift (\emph{QS}) algorithm is used for the 
-generation of superpixels. The experiments were conducted on the \emph{Graz-02} 
-database \cite{0781426535} containing already labeled objects. The accuracy achieved by 
-the QS, ERS, SLIC and LSC algorithms is that shown in the Table \ref{table accuracy}, while 
-the various segmentations, obtained from each of these, are visible in the 
-figure \ref{fig: superpixelSegmentation}. As you can see, LSC performs a better segmentation than the other 
-methods, this happens because the information obtained from the histograms 
-belonging to the SIFT of different superpixel generated are used. In this way 
-there is a better adherence to the boundary of each object in addition the 
-superpixels take on a highly irregular shape for objects in the foreground and 
-more regular for the background.
     \begin{table}[h!]
         \centering
-    \begin{adjustbox}{max width=\textwidth}
+        \begin{adjustbox}{max width=4cm}
         \begin{tabular}{*{5}{|c}|}%%{|c|c|c|c|c|}
@@
     \end{table}
+\end{frame}
 
+\begin{frame}{APPLICATIONS: Weakly Supervised Semantic Segmentation}
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[H]
+                \includegraphics[width = 0.7 \linewidth]{images/paper2/semanticSegmentation.png}
+                \caption{Weakly supervised semantic segmentation.
+(a) A training image with bounding boxes.
+(b) Output of soft-max layer of $ FCN_c $.
+(c) Coarse semantic segmentation result.
+(d) Superpixels with higher probability of foreground.
+(e) Fore-/Background segmentation result after iterative optimization.
+(f) Refined semantic segmentation result.}
+            \end{figure}
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
             \begin{figure}[htbp]
                 \centering
-    \includegraphics[width = 1 \linewidth]{images/paper2/superpixelAlgo.png}
+                \includegraphics[width = 1 \linewidth]{images/paper2/segmentationAlgo.png}
                 \centering
-    \caption{Segmentation using different superpixels algorithms. (a) Original Image. (b) QS. (c) ERS. (d) SLIC. (e) LSC. (f)Ground Truth.}
-    \label{fig: superpixelSegmentation}
+                \caption{Semantic segmentation. (a) Input image. (b) Strong. (c) Bbox-seg. (d) $ Joint_{sp} $ (LSC) }
             \end{figure}
+            \begin{table}[H]
+                \begin{adjustbox}{max width=4cm}
+                    \begin{tabular}{*{3}{|c}|}%%{|c|c|c|}
+                        \hline
+                        Strong\footnotemark[1]& Bbox-seg\footnotemark[1] & $ Joint_{sp} $ \\
+                        \hline
+                        62.5 & 60.6 & \bfseries{64.0} \\
+                        \hline
+                    \end{tabular}
+                \end{adjustbox}
+                \caption{Semantic segmentation accuracy in terms of Mean IOU (\%)}
+            \end{table}
+        \end{minipage}
+    \end{minipage}
+    \footnotetext[1]{\tiny G. Papandreou, L. Chen, K. Murphy, and A. Yuille, “Weakly-and semi-
+    supervised learning of a deep convolutional network for semantic image segmentation,” in Proc. ICCV, pp. 1742–1750, Dec. 2015}
+\end{frame}
+
+\begin{frame}{CONCLUSIONS}
+    The LSC algorithm seems to be the best in terms of adherence to the 
+    boundary and in the creation of superpixels with increasingly regular 
+    shape, but there are still two problems to solve:
+    \begin{enumerate}
+        \item The number K of superpixels entered manually
+        \item New similarity techniques to improve performance
+    \end{enumerate}
+\end{frame}

### 2021-04-11 slides/slides_paper3.tex
new folders structures

\section{Paper 3}
\subsection{\emph{"An End-to-End Compression Framework Based on Convolutional Neural Networks"}}

\begin{frame}{INTRODUCTION}
    In recent years, within the field of computer vision, remarkable results 
    have been achieved with regard to image compression. The purpose of 
    compressionis to be able to transmit, or save, the entire image at low bit 
    rates. The following article presents a compression method based on 
    convolutional neural networks (CNNs) which, through the use of various 
    state-of-the-art codecs, are able to achieve better performance in terms 
    of compression and image quality.
\end{frame}

\begin{frame}{RELATED WORK}
    At the state of the art there are post-processing methods that use 
    {\bfseries{deblocking}} and {\bfseries{restoring}} techniques \footfullcite{0799924108}. These techniques have a strong 
    computational impact on systems. These operations focus on eliminating 
    artifacts and blocks that contain noise within the image. Other methods 
    use CNNs for {\bfseries{super-resolution}} (SR) images \footfullcite{0799924123}. There are deep learning 
    methods that are used for {\bfseries{lossy}} \footfullcite{0799924125} or {\bfseries{lossless}} \footfullcite{0799924130} compression of images, but 
    these ignore the use of the various existing codecs.
\end{frame}

\begin{frame}{THE PROPOSED COMPRESSION FRAMEWORK pt1}
    The proposed system is composed of two convolutional neural networks:
    \begin{enumerate}
        \item \emph{ComCNN}: used for compact representation of images
        \item \emph{RecCNN}: used for decoding and reconstruction of images
    \end{enumerate}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8 \linewidth]{images/paper3/framework.png}
        \centering
        \caption{Up: the ComCNN. Down: the RecCNN. Right: the codec.}
        \label{fig: framework}
    \end{figure}
\end{frame}

\begin{frame}{THE PROPOSED COMPRESSION FRAMEWORK pt2}
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[H]
                \includegraphics[width = 1 \linewidth]{images/paper3/ComCNN.png}
                \caption{ComCNN architecture.}
            \end{figure}
            \begin{block}{Parameter optimizations}
                \small $$ \hat{\theta_1} = \argmin\limits_{\theta_1}||Re(\hat{\theta_2},Cr(\theta_1,x))-x||^2 $$
            \end{block}
            \begin{block}{Loss Function}
               \tiny $$ L_1(\theta_1) = \frac{1}{2N}\sum_{k=1}^N||Re(\hat{\theta_2}, C_r(\theta1,x_k))-x_k||^2 $$
            \end{block}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[htbp]
                \centering
                \includegraphics[width = 1 \linewidth]{images/paper3/RecCNN.png}
                \centering
                \caption{RecCNN architecture.}
            \end{figure}
            \begin{block}{Parameter optimizations}
                \small $$ \hat{\theta_2} = \argmin\limits_{\theta_2}||Re(\hat{\theta_2},\hat{x}_m)-x||^2 $$
            \end{block}
            \begin{block}{Loss Function}
                \tiny $$ L_2(\theta_2) = \frac{1}{2N}\sum_{k=1}^N||res(Co(\hat{x}_{mk}), \theta_2) - (Co(\hat{x}_{mk})-x_k)||^2 $$
             \end{block}
        \end{minipage}
    \end{minipage}
\end{frame}

\begin{frame}{EXPERIMENTS}
    The performance comparison is made by citing various techniques present 
    at the state of the art. A compression quality index ({\bfseries\emph{PSNR}}) and ù
    an image similarity index ({\bfseries\emph{SSIM}}) are used. What is really important to note 
    is how the proposed method manages to have better performance than 
    the already used codecs such as \emph{JPEG}, \emph{JPEG2000} and \emph{BPG}, at different 
    bit rates (\emph{bpp}) and quality factors (\emph{QS}). As for the execution times, in 
    terms of CPU / GPU, the proposed algorithm is faster than those already 
    existing.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper3/time.png}
        \centering
        \caption{Running time(s) of compared methods in CPU (/GPU) }
        \label{fig:time}
    \end{figure}
\end{frame}

\begin{frame}{EXPERIMENTS: JPEG vs. The proposed system}
    With a variable QF (first set to 5 and then to 10), the results obtained by 
    the various methods, in terms of PSNR and SSIM, are shown in the following figures:
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[H]
                \includegraphics[width = 1 \linewidth]{images/paper3/comparison.png}
                \caption{QF = 5, PSNR(db) and SSIM results of alghoritms image deblocking and denoising}
            \end{figure}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[htbp]
                \centering
                \includegraphics[width = 1 \linewidth]{images/paper3/comparison2.png}
                \caption{QF = 10, PSNR(db) and SSIM results of alghoritms image deblocking and denoising}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}
\end{frame}

\begin{frame}{EXPERIMENTS: JPEG2000 vs. The proposed system}
    As we can see from the comparison made in figure \ref{fig:parrot}, the difference in  
    visual quality between the proposed method and the JPEG2000 codec is 
    considerable. With the same amount of bit rates, the JPEG2000 codec 
    produces worse results by losing several structural information. 
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[H]
                \includegraphics[width = 1 \linewidth]{images/paper3/JPEG2000.png}                
                \caption{Average PSNR(dB)/SSIM results of JPEG2000 and the proposed method on different datasets.}
            \end{figure}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[htbp]
                \centering
                \includegraphics[width = 1 \linewidth]{images/paper3/JPEG2000p.png}
                \caption{Performance comparison of JPEG2000 at difference bit rates.}
                \label{fig:parrot}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}
\end{frame}

\begin{frame}{EXPERIMENTS: BPG vs. The proposed system}
    As for the BPG codec, if used in combination with the \emph{ComCNN} and 
    \emph{RecCNN} networks, it reaches higher \emph{PSNR} and \emph{SSIM} levels than when 
    used individually or with only one of the two networks.   
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper3/BPG.png}
        \centering
        \caption{BPG: PSNR (dB) and SSIM result of BPG, BPG + RecCNN and the proposed method.}
        \label{fig:BPG}
    \end{figure}
\end{frame}

\begin{frame}{CONCLUSION}
    The proposed method seems to have the best performance compared to other 
    methods already existing in the state of the art. The proposed technique 
    then validates the use of one or more convolutional neural networks to carry 
    out the task of encoding and decoding images, even in some cases achieving 
    better quality than existing codecs for image compression.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.5 \linewidth]{images/paper3/final.png}
        \centering
        \caption{Visual quality comparison of image deblocking ad different QF.}
        \label{fig:final comparison}
    \end{figure}
\end{frame}

### 2021-04-11 slides/slides_paper4.tex
new folders structures

\section{Paper 4}
\subsection{\emph{"A Data Set for Camera-Independent Color Constancy"}}

\begin{frame}{INTRODUCTION}
    In computer vision, the output generated by an algorithm depends on the 
    nature of the images set given as input. When the images come from 
    different sources (e.g. different cameras), the behavior of the algorithm is 
    not always the same. For this reason, we try to standardize the input in 
    order to have a more uniform output.
\end{frame}

\begin{frame}{COLOR CONSTANCY DATASETS}
    To produce uniform output, an algorithm must achieve "{\bfseries{color 
    constancy}}" on all input images. In order to calculate this property, there 
    are supervised and unsupervised algorithms. To test the performance of 
    these algorithms, there are already state-of-the-art datasets \footfullcite{0807099130} \footfullcite{0807099132} \footfullcite{0807099120}
    containing indoor and outdoor images, but these have few images inside 
    them.
\end{frame}

\begin{frame}{THE PROPOSED INTEL-TUT DATA SET}
    The purpose of the paper is to present a dataset containing images useful 
    for researching the {\bfseries{camera/scene-independence}} effect of an algorithm.
    To achive this, each scene was captured under five different illumination. 
    In each scene there are images taken from three different cameras, 
    including a mobile one.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper4/lab.png}
        \centering
        \caption{Lab real scenes}
        \label{fig:Lab}
    \end{figure}
\end{frame}

\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Chromaticity}
    \begin{block}{Chromatic adaptation - \href{https://en.wikipedia.org/wiki/Color_vision}{\underline{Wikipedia}}}
        \emph{"In color vision, chromatic adaptation refers to color constancy; the 
        ability of the visual system to preserve the appearance of an object under 
        a wide range of light sources."}
    \end{block}
    The only information available on the light source are: the "\emph{Spectral 
    Power Distributions}" (SPD) and the "\emph{Spectral Reflectance}" (SR)
    Thanks to this information, we can obtain the existing chromaticity in the image 
    and compare it with that obtained from the "\emph{Camera Spectral Senstivities}" (CSS).
    \begin{block}{Target}
        The goal is to be able to bring the white point, calculated by each 
        algorithm, closer to the white point of the ground truth, within the same 
        color spectrum (sRGB). To do this, a "\emph{Color Conversion Matrix}" (CCM) 
        is used.
    \end{block}
\end{frame}

\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Evaluations}
    The performance of supervised and unsupervised methods can be 
    evaluated with 5 of the following strategies:
    \begin{enumerate}
        \item Camera Independence \label{CI}
        \item Camera and Scene Independence
        \item Camera and Scene Independence from Single Camera
        \item Testing the Effect of Color Shading
        \item Testing the Effect of Resolution
    \end{enumerate}
    In each of these strategies, the training set, validation set and testing 
    set contain, in different positions, different images acquired from different 
    cameras.
\end{frame}

\begin{frame}{EXPERIMENTAL RESULTS - Unsupervised methods}
    \begin{block}{Recover Angluar Error}
        Given the chromaticity estimated by the algorithm ($ p^{Est} $) and the 
        effective chromaticity (white point or ground truth) ($ p^E $), the 
        performance of an algorithm can be evaluated based on the result 
        returned by the "\emph{Recovery Angular Error}" (RAE):
        $$ RAE=\cos^{-1}\left(\frac{p^Ep^{Est}}{||p^E||~||p^{Est}||}\right) $$
    \end{block}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8 \linewidth]{images/paper4/standardHigh.png}
        \centering
        \caption{Mean, Median and Maximum RAE of some algorithms. GW \footfullcite{0807099104} achieves the best performance}
        \label{fig:RAEstandard}
    \end{figure}
\end{frame}

\begin{frame}{EXPERIMENTAL RESULTS - Supervised methods}
    Color constancy can also be calculated from convolutional neural networks (\emph{CCNs}) such as the one proposed in \footfullcite{0807099125}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper4/25tech1.png}
        \centering
        \caption{Camera Independence with CCM on $ 1^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
        \label{fig:CNNtec1}
    \end{figure}
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[H]
                \includegraphics[width=\linewidth]{images/paper4/25tech2.png}
                \caption{\small Camera Independence on $ 2^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
            \end{figure}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[htbp]
                \centering
                \includegraphics[width=0.8\linewidth]{images/paper4/25tech3.png}
                \caption{\small Camera Independence on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}
\end{frame}

\begin{frame}{CONCLUSION}
    The dataset proposed in this paper is useful for testing the behavior of 
    an algorithm, or a model based on CNN, in the search of camera/scene-independece. 
    Achieving this goal can also be done using a CNN if the CMM process is 
    applied to its input set. It is necessary to specify that, in order to 
    achieve the final result, it is essential to have the spectral sensitivities of each camera 
    without which it would not be possible to achieve camera independence.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.5 \linewidth]{images/paper4/CSS.png}
        \centering
        \caption{Camera Spectral Sensitivities (CSS) of the light sources.}
        \label{fig:CNNtec1}
    \end{figure}
\end{frame}

### 2021-04-11 slides/slides_paper5.tex
new folders structures

\section{Paper 5}
\subsection{\emph{"An End-to-End Multi-Task and Fusion CNN for Inertial-Based Gait Recognition"}}

\begin{frame}{INTRODUCTION}
    The gait recognition is an activity used in the medical, security and 
    authentication fields. The following paper shows a convolutional neural 
    network (CNN) which takes as input a series of inertial data, coming 
    from different sensors, and produces as output a prediction useful for 
    recognizing a subject.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper5/usecase.png}
        \centering
        \caption{A preview of how the model works.}
        \label{fig:preview}
    \end{figure}
\end{frame}

\begin{frame}{RELATED WORK}
    Some methods have placed inertial sensors in different parts of the body 
    such as legs \footfullcite{0857651733}, hips \footfullcite{0857651732}, ankles, or even in objects such as bags and 
    pockets. Other methods \footfullcite{0857651736} directly use all the inertial sensors present in 
    the smartphone. In the proposed method, the data coming from the 
    different sensors are merged and sent to the network which will have the 
    task of predicting some tasks such as: {\bfseries{Identification}}, {\bfseries{age}} and {\bfseries{gender}} of 
    the subject.
\end{frame}

\begin{frame}{PROPOSED APPROACH - CNN Architecture}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8 \linewidth]{images/paper5/architecture.png}
        \centering
        \caption{Pipeline for multi-task and multi-sensor learning in a gait-based system}
        \label{fig:pipeline}
    \end{figure}
    The network consists of two branches, one for each sensor (accelerometer 
    and gyroscope). The Input is split into 3 channels, 1 for each physical 
    size of the signal (axis x, y and z). After merging the data into a single 
    branch, the feature vector is extracted and then the three classes are 
    predicted. The data used are those present in the OU-ISIR dataset \small\footfullcite{0857651721}.
\end{frame}

\begin{frame}{PROPOSED APPROACH - Multi-Task}
    A network that manages different labels falls into the category of deep 
    multitask (\emph{DMT}) networks. To train this network, the sequence S of data 
    coming in input is splitted into $ s_i $ sub-sequences each of which will be 
    inserted in a tuple $ I = (s_i, y_i^m, y_1^1, ..., y_i^T) $ where $ y_i^m $ is the label of the 
    main task, $ y_i^t $, with $ t \in [1,T] $, is the label for each auxilary task. Both 
    the subsequences $ s_i $ and the tasks have their own loss function. The  total  
    accuracy  is  obtained  by combining the accuracies derived from the output 
    of each sub-sequence $ s_i $  of  the  input  S.
\end{frame}

\begin{frame}{PROPOSED APPROACH - Identity Authentication}
    Unlike the acknowledgment, the authentication problem aims to see if 
    two different inputs belong to the same subject. To do this, it is necessary 
    to calculate the Euclidean distances between the input data and the data 
    vectors present in the training set. Once this is done, the resulting vector 
    must be translated into probabilities that will be useful in order to 
    calculate two indices (Area Under Curve (AUC), Equal-Error-Rate 
    (EER)) that will be useful for evaluating the CNN network.
\end{frame}

\begin{frame}{EXPERIMENTS AND RESULTS - Gait recognition}
    For recognition, different types of experiments on different models and 
    their respective performances in terms of accuracy and F1-measure are 
    presented below.
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{table}[h!]
            \centering
                \begin{adjustbox}{max width=\textwidth}
                \begin{tabular}{|c||ccc|c||ccc|c|}
                    \hline
                        & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
                    \hline
                        Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
                    \hline
                        SingleTask Accelerometer & 89.7 & 91.0 & 94.8 & 91.8 & 87.6 & 91.3 & 94.5 & 91.2\\
                        SingleTask Gyroscope& 89.1 & 89.1 & 94.4 & 90.9 & 87.5 & 89.7 & 94.4 & 90.5\\
                    \hline 
                \end{tabular}
                \end{adjustbox}
                \caption{Accuracy and F1-score (1 Task, 1 Sensor).}
                \label{table accuracy and F1 (1 Task - 1 Sensor)}
            \end{table}
            \centering
            \begin{table}[h!]
                \centering
                \begin{adjustbox}{max width=\textwidth}
                \begin{tabular}{|c||ccc|c||ccc|c|}
                    \hline
                        & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
                    \hline
                        Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
                    \hline
                        SingleTask Fusion & 94.2 & 95.0 & 95.6 & 94.9 & 93.5 & 95.0 & 95.6 & 94.7\\
                    \hline 
                \end{tabular}
                \end{adjustbox}
                \caption{Accuracy and F1-score (1 Task, + Sensor).}
                \label{table accuracy and F1 (1 Task, + Sensor)}
            \end{table}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[htbp]
                \centering
                \begin{table}[h!]
                    \centering
                    \begin{adjustbox}{max width=\textwidth}
                    \begin{tabular}{|c||ccc|c||ccc|c|}
                        \hline
                            & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
                        \hline
                            Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
                        \hline
                            MultiTask Accelerometer & 90.9 & 93.3 & 95.9 & 93.4 & 89.1 & 93.3 & 95.9 & 92.8\\
                            MultiTask Gyroscope & 90.1 & 90.1 & 94.8 & 91.7 & 88.3 & 90.5 & 94.9 & 91.2\\
                        \hline 
                    \end{tabular}
                    \end{adjustbox}
                    \caption{Accuracy and F1-score (+ Task, 1 Sensor).}
                    \label{table accuracy and F1 (more Task - 1 Sensor)}
                \end{table}
                \centering
                \begin{table}[h!]
                    \centering
                    \begin{adjustbox}{max width=\textwidth}
                    \begin{tabular}{|c||ccc|c||ccc|c|}
                        \hline
                            & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
                        \hline
                            Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
                        \hline
                            MultiTask Fusion & \bfseries{94.8} & \bfseries{96.1} & \bfseries{97.7} & \bfseries{96.2} & \bfseries{93.8} & \bfseries{96.3} & \bfseries{97.7} & \bfseries{95.9}\\
                        \hline 
                    \end{tabular}
                    \end{adjustbox}
                    \caption{Accuracy and F1-score (1 Task, + Sensor).}
                    \label{table accuracy and F1 (+ Task, + Sensor)}
                \end{table}
            \end{figure}
        \end{minipage}
    \end{minipage}
\end{frame}

\begin{frame}{EXPERIMENTS AND RESULTS - Authentication}
    For identity authentication, on the other hand, the results shown in the table show that for this type of problem the single task model is better than the multi-task model. This happens because in this problem a single label (id) is required and not others. The introduction of other labels leads the multitask model to have worse accuracy than the single task model. The indices AUC (higher is better) and EER (lower is better) are calculated thanks to the probabilities obtained from the Euclidean distance vector.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c|cc|}
            \hline
            Architecture & EER & AUC\\
            \hline
            SingleTask Accelerometer & 1.47 & 99.91\\
            SingleTask Gyroscope & 2.50 & 99.80\\
            \hline
            MultiTask Accelerometer & 1.61 & 99.90\\
            MultiTask Gyroscope & 2.85 & 99.72\\
            \hline
            SingleTask Fusion & \bfseries{1.14} & \bfseries{99.93}\\
            \hline
            MultiTask Fusion & 1.34 & 99.92\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Authentication accuracy.}
        \label{Authentication}
    \end{table}
\end{frame}

\begin{frame}{EXPERIMENTS AND RESULTS - State of the art Comparison}
    Comparing the proposed system with those already existing in the state 
    of the art, both for recognition and authentication, the performance, in 
    terms of accuracy, achieved outperforms those competitors.
        \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{table}[h!]
                \centering
                \begin{adjustbox}{max width=\textwidth}
                \begin{tabular}{|c|ccc|c|}
                    \hline
                    CNN & Id & Age & Gender & Avg\\
                    \hline
                    AE-GDI-CC & 61.0 & - & - & -\\
                    Muaaz et al. & 63.5 & - & - & -\\
                    Ngo et al. & 70.2 & - & - & -\\
                    Wei et al. & 83.8 & - & - & - \\
                    \hline
                    MultiTask Fusion & \bfseries{94.8} & \bfseries{96.1} & \bfseries{97.7} & \bfseries{96.2}\\
                    \hline
                \end{tabular}
                \end{adjustbox}
                \caption{Gait recognition comparison with some methods.}
                \label{Gait comparison}
            \end{table}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{table}[h!]
                \centering
                \begin{adjustbox}{max width=\textwidth}
                \begin{tabular}{|c|c|}
                    \hline
                    Approach & EER\\
                    \hline
                    Gafurov et al. & 15.8 \\
                    Derawi et al. & 14.3 \\
                    Rong et al. & 14.3 \\
                    Ngo et al. & 13.5 \\
                    Imp GDI + i-vector & 7.1 \\
                    NC GDI + i-vector & 5.6 \\
                    \hline
                    SingleTask Fusion & \bfseries{1.1}\\
                    \hline
                \end{tabular}
                \end{adjustbox}
                \caption{Authentication comparison with some methods.}
                \label{Authentication comparison}
            \end{table}
        \end{minipage}
    \end{minipage}
\end{frame}

\begin{frame}{CONCLUSIONS}
    As a final consideration, the model to be used, in the case of gait recognition, 
    is the one that merges the input information and adopts a multitask 
    approach. On the other hand, as regards the authentication problem, it has 
    been seen that it is better to use a singletask model.
\end{frame}

### 2021-04-11 slides/slides_paper6.tex
new folders structures

\section{Paper 6}
\subsection{\emph{"Coarse-to-Fine Semantic Segmentation From Image-Level Labels"}}

\begin{frame}{INTRODUCTION}
    ciao mondo
\end{frame}

### 2021-04-11 papers/paper_6.tex
finish related work paper6

@@
     \item \emph{Fully Supervised Pixel-Wise Annotation-Based Methods}: trained with 
-    pixel-wise labels annotated by people:
+    pixel-wise labels annotated by people.
     \item \emph{Weakly Supervised Object-level Annotation-Based-Methods}: trained with 
     methods such as object-level annotations based on the use of bounding 
-    boxes;
+    boxes.
     \item \emph{Weakly Supervised Image-Level Annotation-Based Methods}: trained 

### 2021-04-11 slides/slides_paper6.tex
finish related work paper6

@@
 \begin{frame}{INTRODUCTION}
-    ciao mondo
+    Weakly supervised and semi-supervised methods are used to achieve 
+    semantic segmentation. These methods need techniques that are capable 
+    of producing useful labels in order to train the models. Two types of 
+    techniques that produce labels are: \emph{Image-level labels} (categories) and 
+    \emph{Object-level labels} (bounding boxes). In the following paper, the use of 
+    the first technique prevails over the second because it is more accurate. 
+    The proposed framework has the task of training a model that only 
+    depends on image category level annotations. The final goal is to be able 
+    to recognize different objects, in the foreground, belonging to different 
+    categories.
 \end{frame}
+
+\begin{frame}{RELATED WORK}
+    The following framework can be used both to perform semantic 
+    segmentation and to extract foreground objects. There are various 
+    models proposed at the state of the art that carry out a different 
+    semantic segmentation and a different foreground segmentation.
+    \begin{table}[h!]
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{|p{6cm}|p{6cm}|}
+            \hline
+            \centering
+            \bfseries{Semantic Segmentation Methods} &  ~~~~~~~~~~\bfseries{Foreground Methods} \\
+            \hline
+            \begin{enumerate}
+                \item \emph{Fully Supervised Pixel-Wise Annotation-Based Methods}: trained with 
+                pixel-wise labels annotated by people.
+                \item \emph{Weakly Supervised Object-level Annotation-Based-Methods}: trained with 
+                methods such as object-level annotations based on the use of bounding 
+                boxes.
+                \item \emph{Weakly Supervised Image-Level Annotation-Based Methods}: trained 
+                with image category labels.
+            \end{enumerate}
+            & 
+            \begin{enumerate}
+                \item \emph{Joint segmentation-based Methods}: used prior knowledge as supervision.
+                \item \emph{Saliency prediction-based Methods}: identify regions present in the human 
+                visual scene.
+                \item \emph{Object proposal-based Methods}: locate all objects in images.
+            \end{enumerate}\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+    \end{table}
+\end{frame}

### 2021-04-11 slides/slides_paper6.tex
CMG

@@
 \begin{frame}{RELATED WORK}
-    The following framework can be used both to perform semantic 
-    segmentation and to extract foreground objects. There are various 
-    models proposed at the state of the art that carry out a different 
-    semantic segmentation and a different foreground segmentation.
+    The following framework can be used for both semantic segmentation 
+    and foreground object segmentation. There are various models proposed 
+    at the state of the art that carry out a different semantic segmentation 
+    and a different foreground segmentation.
     \begin{table}[h!]
@@
             \centering
-            \bfseries{Semantic Segmentation Methods} &  ~~~~~~~~~~\bfseries{Foreground Methods} \\
+            \bfseries{Semantic Segmentation Methods} &  ~\bfseries{Foreground Segmentation Methods} \\
             \hline
@@
 \end{frame}
+
+\begin{frame}{THE PROPOSED APPROACH - 3 Steps}
+    The work performed by the model is divided into three steps: \emph{coarse mask generation}, \emph{coarse mask enhancement}, and \emph{recursive mask refinement}.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 1 \linewidth]{images/paper6/step.png}
+        \centering
+        \caption{Steps of the proposed method.}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{THE PROPOSED APPROACH - \emph{Coarse Mask Generation}}
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            A CNN network\footnotemark is used to be able 
+            to extract a first coarse mask. 
+            Unfortunately, as can be seen in 
+            the image, the generated masks 
+            appear to be inaccurate and do 
+            not comply with the position of 
+            the underlying object.
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[h!]
+                \centering
+                \includegraphics[width = 1 \linewidth]{images/paper6/coarse mask.png}
+                \centering
+            \end{figure}
+        \end{minipage}
+    \end{minipage}
+    \footnotetext{I.
+Croitoru, S.-V.
+Bogolin, and M.
+Leordeanu, “Unsupervised learning from video to detect foreground objects in single images,” in Proc.
+IEEE Int.
+Conf.
+Comput.
+Vis.
+(ICCV), Oct.
+2017, pp.
+4335–4343.}
+\end{frame}

### 2021-04-11 slides/slides_paper6.tex
start foreground

@@
         \begin{minipage}{0.45\linewidth}
-            A CNN network\footnotemark is used to be able 
+            A CNN network\footnotemark ~is used to be able 
             to extract a first coarse mask. 
@@
 \end{frame}
+
+\begin{frame}{THE PROPOSED APPROACH - \emph{Coarse Mask Enhancement}}
+    To carry out the enhanced coarse mask, the unsupervised GrubCut 
+    model\footnotemark ~is used. To achieve mask optimization, the 
+    method performs the following two steps:
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{enumerate}
+                \item search for the smallest bounding box inside the mask.
+                \item enhance the mask based on the previously created bounding box and on the RGB image.
+            \end{enumerate}
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[h!]
+                \centering
+                \includegraphics[width = 1.2 \linewidth]{images/paper6/enhancement.png}
+                \centering
+            \end{figure}
+        \end{minipage}
+    \end{minipage}
+    \footnotetext{C. Rother, V. Kolmogorov, and A. Blake, “GrabCut: Interactive foreground extraction using iterated graph cuts,” ACM Trans. Graph., vol. 23, no. 3, pp. 309–314, 2004.}
+\end{frame}
+
+\begin{frame}{THE PROPOSED APPROACH - \emph{Recursive Mask Refinement}}
+    A network called DeepLab \footfullcite{0876055502} is used for semantic segmentation. This 
+    network uses the mask generated by the GrubCut method and, through a 
+    comparison on the original image, produces a new better mask that will 
+    be used as a new training set. The best mask will be obtained after a 
+    maximum of 5 training rounds.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 1 \linewidth]{images/paper6/DeepLab.png}
+        \centering
+    \end{figure}
+\end{frame}

### 2021-04-12 slides/slides_paper6.tex
start foreground
finish slide paper6

@@
 \end{frame}
+
+\begin{frame}{EXPERIMENTS - Semantic Segmentation Results}
+    The \emph{Intersection over Union} (IoU), averaged over 21, categories is used as an 
+    evaluation index of the semantic segmentation and foreground segmentation. 
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{table}[h!]
+                \centering
+                \begin{adjustbox}{max width=0.7\textwidth}
+                \begin{tabular}{|c|c|}
+                    \hline
+                    Training Mask Type & IoU(\%)\\
+                    \hline
+                    Coarse Masks & 32.5 \\
+                    Bounding Boxes & 35.2 \\
+                    Enhanced Masks & 47.7 \\
+                    Refined Masks & 50.4 \\
+                    \hline
+                \end{tabular}
+                \end{adjustbox}
+                \caption{The performance of semantic segmentation networks evalueted in the validation split of PASCAL VOC dataset in the mean IoU (higher is better).}
+            \end{table}
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[h!]
+                \centering
+                \includegraphics[width = 1 \linewidth]{images/paper6/GrabCut.png}
+                \centering
+                \caption{Enhancement with GrubCut application}
+            \end{figure}
+        \end{minipage}
+    \end{minipage}
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=0.7\textwidth}
+        \begin{tabular}{|c|c|c|}
+            \hline
+            Methods & mIoU(val) & mIoU(test)\\
+            \hline
+            Supervision: Object-level Labels & &\\
+            SDI \cite{0876055513} & 65.7 & 67.5\\
+            \hline
+            Supervision: Image-level Labels & &\\
+            Bootstrap \cite{0876055555} & 63.0 & 63.9\\
+            \bfseries{The proposed weakly supervised method} & \bfseries{61.9} & \bfseries{62.8}\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Comparison, in terms of IoU score, between different models.}
+        \label{IoU score comparison}
+    \end{table}
+\end{frame}
+
+\begin{frame}{EXPERIMENTS - Foreground Segmentation Results}
+    With an architecture similar to \emph{FPN} \footfullcite{0876055543}, the new network is called the \emph{Dilated Feature Pyramid 
+    Network} (DFPN). This network has several dilated layers, in three branches, 
+    added to enlarge the receptive field of the network. The features generated 
+    by these layers are aggregated to make a prediction. From the performance obtained, the proposed 
+    model, which is remembered to be weakly supervised, manages to achieve the 
+    performance of the supervised models, with a difference of 2.06\% compared 
+    to the supervised \emph{PixelObjectness}.
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{|c||c|c|c|c||c|c|c|c|}
+            \hline
+            \multirow{2}{*}{\bfseries{Methods}} & \multicolumn{4}{c||}{\bfseries{MIT dataset (subset)}} & \multicolumn{4}{c|}{\bfseries{MIT dataset (full)}} \\            & \bfseries{Ariplane} & \bfseries{Car} & \bfseries{Horse}  & \bfseries{Average} & \bfseries{Ariplane} & \bfseries{Car} & \bfseries{Horse}  & \bfseries{Average} \\
+            \hline
+            \bfseries{\#Images} & 82 & 89 & 93 & N/A & 470 & 1208 & 810 & N/A\\
+            \hline
+            UnsupervisedSeg \cite{0876055520} & 61.37 & 70.52 & 55.09 &62.32 & N/A & N/A & N/A & N/A\\
+            \hline
+            PixelObjectness \cite{0876055538} & 66.43 & 85.07 & 60.85 &70.78 & 66.18 & 84.80 & 64.90 & 71.96\\
+            \hline 
+            \bfseries{FPN-Baseline} & 61.09 & 76.22 & 57.89 & \bfseries{65.08} & 61.93 & 75.94 & 64.03 & \bfseries{67.3}\\
+            \hline
+            \bfseries{Proposed Method} & 64.92 & 77.60 & 60.36 & \bfseries{67.63(+2.57)} & 65.88 & 77.07 & 65.82 & \bfseries{69.59(+2.29)}\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Quantitative Results of Foreground Segmentation on MIT object Discovery Dataset.}
+    \end{table}
+\end{frame}
+
+\begin{frame}{CONCLUSION}
+    The proposed framework, based on a weakly supervide model, is able to 
+    achieve the performance of the full supervised models that obtain better 
+    results at the state of the art. it is also capable of recognizing multiple categories of objects in an image (Fig. \ref{fig:segmentationCategories}). Despite the efforts made to arrive at such 
+    results, there are several classes in which the model fails to generate 
+    good masks (Fig. \ref{fig:classes}).
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 0.6 \linewidth]{images/paper6/multiple segmentation.png}
+        \centering
+        \caption{Example of semantic segmentation on different categories.}
+        \label{fig:segmentationCategories}
+    \end{figure}
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 1 \linewidth]{images/paper6/classes.png}
+        \centering
+        \caption{Score of IoU in some classes.}
+        \label{fig:classes}
+    \end{figure}
+\end{frame}

### 2021-04-12 papers/paper_7.tex
start paper7

--- 2021-04-11 paper_6.tex
@@
-\section{Coarse-to-Fine Semantic Segmentation From Image-Level Labels}
+\section{Variational-Based Mixed Noise Removal With CNN Deep Learning Regularization}
 
@@
     \author{
-    Longlong Jing,
-    Yucheng Chen,
-    Yingli Tan,
-    \emph{Fellow, IEEE}
+    Faqiang Wang,
+    Haiyang Huang,
+    Jun Liu
     }
@@
 \subsection{INTRODUCTION}
-To obtain a semantic segmentation it is necessary to have an annotated 
-training set. Semantic segmentation generally requires pixel-wise semantic 
-annotation techniques which are time-consuming. To solve the annotation 
-problem, weakly supervised and semi-supervised semantic segmentation 
-methods have been proposed. Methods such as object-level labels and image-level 
-labels are used to extract annotations. These annotations are useful for 
-producing datasets useful for training a weakly supervised model, such as 
-the one proposed. By training a weakly supervised semantic segmentation 
-model, with the labels produced, the performances match those of the supervised 
-methods. Unfortunately, methods such as object-level labels produce 
-bounding boxes that are still not precise, so the use of the image-level labels 
-method prevails. The dataset used is that of ImageNet where a category is 
-associated with each image. The proposed model is able to generate as many 
-segmentation masks as there are different objects belonging to different 
-categories in each image. Network training takes place using information such as 
-masks, images and labels of each category. An example of the coarse-to-fine 
-mask produced by the model is the one shown in figure \ref{fig:semanticWork}.
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width = 1 \linewidth]{images/paper6/work.png}
-    \centering
-    \caption{Example of semantic segmentation generated by the proposed method.}
-    \label{fig:semanticWork}
-\end{figure}
-
-\subsection{RELATED WORK}
-\subsubsection{Semantic Segmentation}
-There are three different types of semantic segmentation methods that differ 
-based on the level of annotation used:
-\begin{enumerate}
-    \item \emph{Fully Supervised Pixel-Wise Annotation-Based Methods}: trained with 
-    pixel-wise labels annotated by people:
-    \item \emph{Weakly Supervised Object-level Annotation-Based-Methods}: trained with 
-    methods such as object-level annotations based on the use of bounding 
-    boxes;
-    \item \emph{Weakly Supervised Image-Level Annotation-Based Methods}: trained 
-    with image category labels.
-\end{enumerate}
-The methods in the first point, if trained with precise labels, are able to 
-obtain the best performances.
-
-\subsubsection{Foreground Segmentation}
-The labels assigned to pixels can be useful to separate a foreground object 
-from a background object. Also for this task there are three strategies to 
-perform a segmentation of the objects in the foreground:
-\begin{enumerate}
-    \item \emph{Joint segmentation-based Methods}: used prior knowledge as supervision.
-    \item \emph{Saliency prediction-based Methods}: identify regions present in the human 
-    visual scene.
-    \item \emph{Object proposal-based Methods}: locate all objects in images.
-\end{enumerate}
-The proposed framework can also be used for this purpose.
-
-\subsection{THE PROPOSED APPROACH}
-\subsubsection{Overview}
-The work performed by the model is divided into three steps: \emph{coarse mask 
-generation}, \emph{coarse mask enhancement}, and \emph{Recursive mask refinement} (Fig. \ref{fig:step}). In 
-order to generate the initial masks, a CNN is trained and subsequently these 
-are improved with a graph-based model. Images, enhanced masks and lables 
-are used to train the model.
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width = 1 \linewidth]{images/paper6/step.png}
-    \centering
-    \caption{Steps of the proposed method.}
-    \label{fig:step}
-\end{figure}
-
-\subsubsection{Coarse Mask Generation}
-The generation of a mask must occur without any information on the labels.
-The CNN present in \cite{0876055520} is used for this purpose. This network is trained 
-with millions of unlabeled images and is also the fastest of other methods 
-existing in the state of the art. Unfortunately, as seen in image \ref{fig:semanticWork}, the 
-generated coarse masks appear to be inaccurate and do not correspond with 
-the position of the underlying object.
-
-\subsubsection{Coarse Mask Enhancement}
-The enhancement of the mask is done before the net training process takes 
-place. To carry out the improvement, the unsupervised GrubCut model \cite{0876055542} 
-is used. This method performs segmentations that divide the background 
-from the foreground using a Gaussian Mixture model to estimate the color 
-distribution of objects. These distributions are used to construct a Markov 
-Random Field on the labels of each pixel. A graph cut optimization has the 
-task of maximizing the search for connected regions having the same label. 
-There are two steps to apply the GrabCut:
-\begin{enumerate}
-    \item search for the smallest bounding box inside the mask.
-    \item enhance the mask based on the previously created bounding box and on the RGB image.
-\end{enumerate}
-The enhanced mask will be used to recursively train the network.
-
-\subsubsection{Recursive Mask Refinement}
-By combining the labels with the enhanced masks, a semantic segmentation 
-is obtained. The purpose is to assign the category label that describes the 
-content to the pixels belonging to the foreground. As a semantic segmentation 
-network it was decided to use the one called \emph{DeepLab} \cite{0876055502}. This network 
-is trained with the improved masks and has the purpose of generating more and more 
-precise masks, without noise, which will be used as a new training 
-set. Enhancing the mask is a recursive process that will end when the system 
-converges to the best representation of the mask. The masks are then used 
-as semantic labels to continue training the network.
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width = 1 \linewidth]{images/paper6/DeepLab.png}
-    \centering
-    \caption{The process of semantic mask generation.}
-    \label{fig:semanticWork}
-\end{figure}
-
-\subsubsection{Model Parameterization}
-In summary, to generate high-quality semantic segmentation masks, it is 
-required to take an image from the ImgNet dataset and submit it to the 
-following steps:
-\begin{enumerate}
-    \item Create a first mask ($ mask_c $) with a non-superivisoned network \cite{0876055520};
-    \item Improve maskc with the GrabCut model \cite{0876055542} to generate a new mask ($ mask_e $);
-    \item Train DeepLab network \cite{0876055502} with $ mask_e $;
-    \item Generate a better mask ($ mask_r $) using the original ImgNet image;
-    \item Enhance the generated mask ($ mask_e $) by applying the GrubCut method;
-    \item Repeat from step 3 until the best mask will be obtained.
-\end{enumerate}
-
-\subsubsection{Extended the Proposed Framework to Foreground Segmentation}
-In order to use the proposed framework in a foreground object recognition 
-problem, only the part concerning the enhanced of the mask must be replaced 
-with a code that allows to perform the required task. With an architecture 
-similar to \emph{FPN} \cite{0876055543}, the new network is called the \emph{Dilated Feature Pyramid 
-Network} (DFPN). This network has several dilated layers, in three branches, 
-added to enlarge the receptive field of the network (Fig \ref{fig:DFPN}). The features generated 
-by these layers are aggregated to make a prediction.
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width = 0.8 \linewidth]{images/paper6/DFPN.png}
-    \centering
-    \caption{DFPN architecture.}
-    \label{fig:DFPN}
-\end{figure}
-
-\subsection{EXPERIMENTS}
-The network is trained with the images and labels present in ImageNet, while 
-the evaluation of the model is carried out on the PASCAL VOC dataset.
-\subsubsection{Datasets}
-\begin{enumerate}
-    \item \emph{ImageNet}: contains about 100,000 labels (synset) annotated by the 
-    human, and each label has at least 1000 related images. Two datasets 
-    useful for training are formed by ImageNet, these are ImageNet-Sub1 
-    and ImageNet-Sub2. The first has a collection of images collected based 
-    on the selected category while the second contains images with categories 
-    that are not present in the VOC dataset that are present in 
-    ImageNet-Sub1.
-    \item \emph{VOC}: dataset containing 21 object categories including background. 
-    The collection is divided into 3 parts: training, validation and test. In 
-    order to be able to evaluate the mask, the results must be sent to the 
-    PASCAL VOC evaluation server. 20 image categories are chosen that 
-    approximate those of ImageNet as the training dataset.
-    \item \emph{MIT Object Discovery Dataset}: this dataset is useful for comparing the 
-    results obtained from segmenting objects in the foreground. There are 
-    at least three categories of objects in the collection.
-\end{enumerate}
-
-\subsubsection{Training Details for Recursive Mask Refinement}
-The Stochastic Gradient Descent mini-batch with a batch size of 12 images 
-is chosen among the parameters. Parameters such as learning rate, momentum 
-and Weight decay are set ad hoc. The training process consists of 5 
-rounds where for each of them the mask is continuously improved. The data 
-augumentation process is present in every training session.
-
-\subsubsection{Evaluation Metrics}
-The \emph{Intersection over Union} (IoU) averaged over 21 categories is used as an 
-evaluation index of the semantic segmentation and foreground segmentation. 
-This metric is particularly useful for evaluating the accuracy of the identification 
-of an object. Both the predicted mask and the ground truth mask 
-are required for its calculation. The IoU index is therefore calculated from 
-the ratio between the area of overlap and the area of union of the two masks. 
-Obviously, the higher this index is, the better the predicted mask will be.
-
-\subsubsection{Semantic Segmentation Results}
-\begin{enumerate}
-    \item \emph{Impact of the mask quality}: as shown in Table \ref{IoU}, the various processing 
-    steps lead to a constant increase in the IoU index. In particular, 
-    the value reached by the index is that relating to the first round of 
-    network training, therefore we proceed recursively with the training of 
-    the network so that it can produce a better mask.
-    \begin{table}[h!]
-        \centering
-        \begin{adjustbox}{max width=\textwidth}
-        \begin{tabular}{|c|c|}
-            \hline
-            Training Mask Type & IoU(\%)\\
-            \hline
-            Coarse Masks & 32.5 \\
-            Bounding Boxes & 35.2 \\
-            Enhanced Masks & 47.7 \\
-            Refined Masks & 50.4 \\
-            \hline
-        \end{tabular}
-        \end{adjustbox}
-        \caption{THe performance of semantic segmentation networks evalueted in the validation split of PASCAL VOC dataset in the mean IoU.}
-        \label{IoU}
-    \end{table}
-
-    \item \emph{Effectiveness of recursive refinement}: the evaluation of each refined 
-    mask takes place using two types of masks, with or without application 
-    of the GrabCut. Between two rounds the masks are improved 
-    with a post-processing process by three strategies: a) If the pixels in 
-    the foreground are less than 1\% and greater than 80\%, then this image 
-    will be discarded by the next training round. b) All the pixels 
-    of the original image, labeled with a category must correspond to the 
-    predicted pixels with the same category, otherwise these will be considered 
-    as background pixels. c) In recursive training, the GrubCut 
-    method is applied to the masks that the DeepLab model predicted to 
-    have improved masks. In figure \ref{fig:GrubCutApp} it can be seen that the application 
-    of GrubCut increases the IoU value and also the system saturates after 
-    5 training rounds.
-    \begin{figure}[h!]
-        \centering
-        \includegraphics[width = 0.8 \linewidth]{images/paper6/GrabCut.png}
-        \centering
-        \caption{Enhancement with GrubCut application}
-        \label{fig:GrubCutApp}
-    \end{figure}
-
-    \item \emph{Comparison with others}: The performance comparison is carried out on both the validation and test sets of the PASCAL VOC dataset (Fig.
-\ref{fig:IoU score comparison}).
-In the state of the art, models trained with methods based on object-level labels annotation obtain a better score (greater than 60\%) than models trained with methods that have an annotation of the type image-level labels.
-The proposed model, on the other hand, while using the image-level labels annotation method, achieves an average IoU score greater than 60\% on both the evaluation and test sets.
-However, there are several classes in which the model obtains a low IoU value (Fig.
-\ref{fig:classes}).
-    \begin{figure}[h!]
-        \centering
-        \includegraphics[width = 0.6 \linewidth]{images/paper6/comparison.png}
-        \centering
-        \caption{Comparison, in terms of IoU score, between different models.}
-        \label{fig:IoU score comparison}
-    \end{figure}
-    \begin{figure}[h!]
-        \centering
-        \includegraphics[width = 1 \linewidth]{images/paper6/classes.png}
-        \centering
-        \caption{Score of IoU in some classes.}
-        \label{fig:classes}
-    \end{figure}
-\end{enumerate}
-
-\subsubsection{Qualitative Results}
-Another purpose of the model was to carry out a semantic segmentation also on the different objects, belonging to different categories, present in a single image, in order to be able to distinguish them.
-A small example of multiple segmentation on different objects is shown in figure \ref{fig:segmentationCategories}.
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width = 1 \linewidth]{images/paper6/multiple segmentation.png}
-    \centering
-    \caption{Example of semantic segmentation on different categories.}
-    \label{fig:segmentationCategories}
-\end{figure}
-
-\subsubsection{Foreground Segmentations Results}

### 2021-04-13 papers/paper_7.tex
finish 7.1

@@
 
-\begin{flushleft}
+\begin{center}
     \author{
@@
     }
-\end{flushleft}
+\end{center}
 
@@
 \subsection{INTRODUCTION}
+Random noise distributions correspond to standard probabilistic distributions, such as the Gaussian, Poisson and other distributions.
+There have been many methods that attempt to clean up noisy images.
+The classical methods are based on the use of filters such as Gaussian, Gabor or median filters.
+Other tools such as the Variational method have been widely used.
+This method is based on reducing the cost function containing the fidelity term of the data, useful for calculating the difference between true and observed data, and the regularization terms.
+Another method used was that of TV regularization.
+Unfortunately this method fails to preserve texture detail.
+Nonlocal methods, on the other hand, are able to capture image details.
+These methods exploit the self-similarity properties that can be integrated into variational methods.
+Despite these methods, the function of the weights is difficult to determine.
+Methods based on deep learning have achieved good noise reduction performance.
+Many of these assume that the value can be removed by applying the L2 norm.
+According to the study carried out in the following article, in order to remove the mixed noise it is necessary to determine the type and level of noise in each pixel.
+The methods based on the variation, unlike the neural networks, require a single image and can integrate different techniques of regularization useful to be able to remove the single noise and the mixed noise.
+The complexity of these methods lies in being able to create a non-computationally complicated design.
+In the proposed article, the EM (Expectation-Maximization) algorithm is used to remove the noise, with the integration of a CNN process as regularization, in order to create a new variational method.
+The method is able to iteratively estimate the noise parameters useful for classifying the type and level of noise in each pixel.
+The work carried out is divided into four phases: regularization, synthesis, parameter estimation and error classification.

### 2021-04-13 papers/paper_7.tex
the proposed method paper7

@@
 \subsection{INTRODUCTION}
-Random noise distributions correspond to standard probabilistic distributions, such as the Gaussian, Poisson and other distributions.
-There have been many methods that attempt to clean up noisy images.
-The classical methods are based on the use of filters such as Gaussian, Gabor or median filters.
-Other tools such as the Variational method have been widely used.
-This method is based on reducing the cost function containing the fidelity term of the data, useful for calculating the difference between true and observed data, and the regularization terms.
-Another method used was that of TV regularization.
-Unfortunately this method fails to preserve texture detail.
+Random noise distributions correspond to standard probabilistic distributions, 
+such as the Gaussian, Poisson and other distributions. There have 
+been many methods that attempt to clean up noisy images. The classical 
+methods are based on the use of filters such as Gaussian, Gabor or median 
+filters. Other tools such as the Variational method have been widely used. 
+This method is based on reducing the cost function containing the fidelity 
+term of the data, useful for calculating the difference between true and observed 
+data, and the regularization terms. Another method used was that of 
+TV regularization. Unfortunately this method fails to preserve texture detail. 
 Nonlocal methods, on the other hand, are able to capture image details. 
-These methods exploit the self-similarity properties that can be integrated into variational methods.
-Despite these methods, the function of the weights is difficult to determine.
-Methods based on deep learning have achieved good noise reduction performance.
-Many of these assume that the value can be removed by applying the L2 norm.
-According to the study carried out in the following article, in order to remove the mixed noise it is necessary to determine the type and level of noise in each pixel.
-The methods based on the variation, unlike the neural networks, require a single image and can integrate different techniques of regularization useful to be able to remove the single noise and the mixed noise.
-The complexity of these methods lies in being able to create a non-computationally complicated design.
-In the proposed article, the EM (Expectation-Maximization) algorithm is used to remove the noise, with the integration of a CNN process as regularization, in order to create a new variational method.
-The method is able to iteratively estimate the noise parameters useful for classifying the type and level of noise in each pixel.
-The work carried out is divided into four phases: regularization, synthesis, parameter estimation and error classification.
+These methods exploit the self-similarity properties that can be integrated 
+into variational methods. Despite these methods, the function of the weights 
+is difficult to determine. Methods based on deep learning have achieved good 
+noise reduction performance. Many of these assume that the value can be 
+removed by applying the L2 norm. According to the study carried out in 
+the following article, in order to remove the mixed noise it is necessary to 
+determine the type and level of noise in each pixel. The methods based on 
+the variation, unlike the neural networks, require a single image and can 
+integrate different techniques of regularization useful to be able to remove 
+the single noise and the mixed noise. The complexity of these methods lies 
+in being able to create a non-computationally complicated design. In the 
+proposed article, the EM (Expectation-Maximization) algorithm is used to 
+remove the noise, with the integration of a CNN process as regularization, 
+in order to create a new variational method. The method is able to iteratively 
+estimate the noise parameters useful for classifying the type and level 
+of noise in each pixel. The work carried out is divided into four phases: 
+regularization, synthesis, parameter estimation and error classification.
+
+\subsection{RELATED WORK}
+\subsubsection{Mixed Noise Model}
+The mixed noise is:
+\begin{equation}
+    n = \left\{ \\
+    \begin{array}{cc}
+        n_1, & with~probability~r_1,\\
+        n_2, & with~probability~r_2,\\
+        \cdots, & \cdots\\
+        n_k, & with~probability~r_k,\\ 
+    \end{array}
+     \right\}
+\end{equation}
+where $ n_k $ is the \emph{k}-th noise component with probability density function (PDF) 
+$ p_k $ and $ r_k $ are the unknown mixture ratios and thei sum is equal to 1.
+
+\subsubsection{Weighted K-SVD Model}
+The following work is based on the method proposed in \cite{0884882814}. After obtaining 
+the value of the mixed-noise \emph{Probability Density Function} (PDF), and 
+assuming that the noise has a uniform distribution, we can derive the \emph{negative 
+log-likelihood} function (\ref{PDF}) useful as {\bfseries{fidelity term}} in the variational 
+method. 
+\begin{equation}\label{PDF}
+    L(u,\Theta) = - \sum_{x\in\Omega}\ln\sum_{k=1}^Kr_kp_k(u(x)-f(x))
+\end{equation}
+In order for this probability to be extended to more types of noise 
+distribution, it is necessary to perform an optimization that minimizes the 
+upper limit of the function (\ref{H function}). 
+\begin{eqnarray}\label{H function}
+    H(u,\Theta,w) & = & - \sum_{x\in\Omega}\sum_{k=1}\ln\left[r_kp_k(u(x)-f(x))\right]w_k \nonumber \\
+                  &   & + \sum_{x\in\Omega}\sum_{k=1}w_k(x)\ln{w_k(x)}  
+\end{eqnarray}
+To minimize H, a minimization of $ w $ must be performed, which is a probability 
+indicates the noise at each pixel, and an iterative minimization of the other 
+two variables $ u $ and $ \Theta $.
+
+\subsubsection{IRCNN}
+Another method \cite{0884882819} uses a CCN, based on the IRCNN model, to restore an 
+image in which Gaussian noise is present. In this model, patches based $ L^2 $ 
+residual loss functions are adopted. Unfortunately, if there are mixed-noises, 
+this method does not produce satisfactory results.
+
+\subsection{THE PROPOSED METHOD (EM-CNN)}
+Removal of mixed-noise can be done with the following model:
+\begin{equation}
+    (u^*, \Theta^*, w^*) = \argmin_x\left\{H(u,\Theta,w) + \lambda_1S(u)\right\}
+\end{equation}
+where $ S $ as regularizer, such \emph{Total Variation Regularization} (TV) while $ \lambda_1 $ 
+control the balance of the terms. By changing $u$ with an auxiliary function 
+$v$, and applying the \emph{augmented Lagrangian method} (ALM) \cite{0884882833}, the minimizations 
+on each component of $H$ ($u$, $\Theta$, $w$) change. The resolution of these 
+minimizations allows to divide the mixed-noise removal problem into Gaussian 
+noise removal (renewing $u$), choice of the fidelity term (renewing $v$), 
+noise reduction (updating the Lagragian multiplier $u$), parameter estimation 
+noise ($\Theta$ update) and error classification ($w$ update). The formula used by 
+the model is able to handle different types of Gaussian noises such as impulse 
+noise, mixed-noise Gaussian-impulse and many others. Each noise has 
+a certain probability function pk, so just change this value in (\ref{H function}). A CNN 
+can be used to learn Gaussian noise for different types of levels. In this paper 
+the CNN based denoiser \cite{0884882819} was used. The weight $w$ is useful for assigning 
+different fidelity terms to pixels contaminated by different levels of types of 
+noise. The minimization of $\Theta$ and $w$ are part of EM processes. Thanks to 
+these it is possible to extract information such as noise variations and the 
+classification of this in different classes.

### 2021-04-14 papers/paper_7.tex
continuiung Gaussian Mixture Model

@@
 \begin{eqnarray}\label{H function}
-    H(u,\Theta,w) & = & - \sum_{x\in\Omega}\sum_{k=1}\ln\left[r_kp_k(u(x)-f(x))\right]w_k \nonumber \\
+    \mathcal{H}(u,\Theta,w) & = & - \sum_{x\in\Omega}\sum_{k=1}\ln\left[r_kp_k(u(x)-f(x))\right]w_k \nonumber \\
                   &   & + \sum_{x\in\Omega}\sum_{k=1}w_k(x)\ln{w_k(x)}  
 \end{eqnarray}
-To minimize H, a minimization of $ w $ must be performed, which is a probability 
+To minimize $\mathcal{H}$, a minimization of $ w $ must be performed, which is a probability 
 indicates the noise at each pixel, and an iterative minimization of the other 
@@
 \subsection{THE PROPOSED METHOD (EM-CNN)}
+In the following paper a general variational model is proposed, formed by 
+the combination of a deep learning method and variational methods, with 
+regularized CNN to remove the mixed-noise problem, especially noises such 
+as the Gaussian mixture and the Gaussian-impulse.
+
+\subsubsection{General Model}
 Removal of mixed-noise can be done with the following model:
-\begin{equation}
-    (u^*, \Theta^*, w^*) = \argmin_x\left\{H(u,\Theta,w) + \lambda_1S(u)\right\}
+\begin{equation}\label{HFunction}
+    (u^*, \Theta^*, w^*) = \argmin_x\left\{H(u,\Theta,w) + \lambda_1\mathcal{J}(u)\right\}
 \end{equation}
-where $ S $ as regularizer, such \emph{Total Variation Regularization} (TV) while $ \lambda_1 $ 
+where $\mathcal{J}$ is a regularizer, such \emph{Total Variation Regularization} (TV) while $ \lambda_1 $ 
 control the balance of the terms. By changing $u$ with an auxiliary function 
 $v$, and applying the \emph{augmented Lagrangian method} (ALM) \cite{0884882833}, the minimizations 
-on each component of $H$ ($u$, $\Theta$, $w$) change. The resolution of these 
+on each component of $\mathcal{H}$ ($u$, $\Theta$, $w$) change. The resolution of these 
 minimizations allows to divide the mixed-noise removal problem into Gaussian 
@@
 these it is possible to extract information such as noise variations and the 
-classification of this in different classes.
+classification of this in different classes. In summary, the minimizations to 
+be calculated are the following:
+
+\begin{equation}\label{uMin}
+    u^{v+1} = \argmin_u \lambda_1\mathcal{J}(u)+\mathcal{H}(u,\Theta^v,w^v),
+\end{equation}
+\begin{equation}\label{ThetaMin}
+    \Theta^{v+1} = \argmin_\Theta \mathcal{H}(u^{v+1}, \Theta, w^v),
+\end{equation}
+\begin{equation}\label{wMin}
+    w^{v+1} = \argmin_{w\in{S}} \mathcal{H}(u^{v+1}, \Theta^{v+1},w)
+\end{equation}
+
+\subsubsection{Gaussian Mixture Model}
+A Gaussian mixture model is a probabilistic model that assumes all the data 
+points are generated from a mixture og finite number of Gaussian distributions 
+with unknown parameters. The distributions of Gaussian noises change 
+according to the assumed variance ($\sigma^2$) value. The new function $ \mathcal{H} $ will be 
+as follows:
+\begin{eqnarray}
+    \mathcal{H}(u,r,\sigma^2,w) & = & \frac{1}{2}\sum_{x\in\Omega}\sum_{k=1}^K\frac{(u(x)-f(x))^2}{\sigma^2_k}w_k(x)-\sum_{x\in\Omega}\sum_{k=1}^Kw_k(x)\ln{r_k}\nonumber \\
+                                &   & + \frac{1}{2}\sum_{x\in\Omega}\sum_{k=1}^Kw_k(x)\ln{\sigma^2_k}+\frac{1}{2}\sum_{x\in\Omega}\sum_{k=1}^Kw_k(x)\ln{w_k}(x)
+\end{eqnarray}
+The optimizations (\ref{uMin}) (\ref{ThetaMin}) (\ref{wMin}) of the parameters of (\ref{HFunction}) are adapted by 
+including the two new parameters $r$ and $\sigma^2$, parameters that are included in 
+$\Theta$.

### 2021-04-14 papers/paper_7.tex
finish 7.3.2

@@
 \begin{equation}\label{PDF}
-    L(u,\Theta) = - \sum_{x\in\Omega}\ln\sum_{k=1}^Kr_kp_k(u(x)-f(x))
+    \mathcal{L}(u,\Theta) = - \sum_{x\in\Omega}\ln\sum_{k=1}^Kr_kp_k(u(x)-f(x))
 \end{equation}
@@
 as follows:
-\begin{eqnarray}
+\begin{eqnarray}\label{HFunctionGMM}
     \mathcal{H}(u,r,\sigma^2,w) & = & \frac{1}{2}\sum_{x\in\Omega}\sum_{k=1}^K\frac{(u(x)-f(x))^2}{\sigma^2_k}w_k(x)-\sum_{x\in\Omega}\sum_{k=1}^Kw_k(x)\ln{r_k}\nonumber \\
@@
 \end{eqnarray}
-The optimizations (\ref{uMin}) (\ref{ThetaMin}) (\ref{wMin}) of the parameters of (\ref{HFunction}) are adapted by 
-including the two new parameters $r$ and $\sigma^2$, parameters that are included in 
-$\Theta$.
+The optimizations (\ref{uMin}) (\ref{ThetaMin}) (\ref{wMin}) of the parameters of (\ref{HFunctionGMM}) are adapted by 
+including the two new parameters $r$ and $\sigma^2$, enclosed in $\Theta$, which will be minimized 
+in turn. Through the optimization of these parameters it is possible to remove 
+the mixed-noise Gaussian. In summary, all the steps carried out are 
+illustrated in figure \ref{fig:EM-CNN}.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.7 \linewidth]{images/paper7/flowchart.png}
+    \centering
+    \caption{The flowchart of EM-CNN algorithm.}
+    \label{fig:EM-CNN}
+\end{figure}
+Image degradation occurs using the additive noise model: 
+$$ f = u + n $$
+where $f$ is the observed image (the one resulting from the combination of 
+noises), $u$ is the true image and $n$ is the introduced noise. The image $f$ will 
+be the input of the CNN network which, through its denoise \cite{0884882819}, will perform 
+a smoothing on the image obtaining a new image $u^{v+1}$. CNN applies two 
+operations on this image in parallel. The first is that of the noise put back 
+in which the noise present in the image f is extracted by simply subtracting 
+the image $u^{v+1}$. Subsequently, to calcutale the fidelity term, the EM algorithm 
+\cite{0884882814} is applied to this noise which has the task of estimating the error 
+and classifying it by minimizing the terms of \ref{HFunctionGMM}. The minimization of each 
+weight $w$ leads to a continuous updating of this parameter which translates 
+into greater precision in determining the noise on each individual pixel. The 
+estimation of the parameters allows to carry out the synthesis process, or to 
+select a new fidelity term, for each pixel, based on the estimates made on the 
+noise. The second operation is to apply the \emph{Total Variation Regularization} 
+(TV) \cite{0884882802} on the starting image $u^{v+1}$ useful for carrying out a good 
+restructuring of the image from noise and blurred data. The image $V^v$ with the 
+updated w weights, will be the new input of the CNN network that through 
+multiple iterative processes will improve until its convergence, or until the 
+fidelity term will no longer change. The output returned by the model will 
+consist of a restructured image ($u^*$) accompanied by the estimates of the 
+individual noises ($n_1^ *, n_2^*$) applied at the beginning.

### 2021-04-14 papers/paper_7.tex
finish 7.4.1

@@
 individual noises ($n_1^ *, n_2^*$) applied at the beginning.
+
+\subsubsection{Gaussian Noise Plus Impulse Noise}
+The overall noise can consist of several noise distributions. Previously, the 
+operations useful for obtaining information on a Gaussian noise distribution 
+have been defined. When the Gaussian distribution assumes random values 
+(called salt and pepper), and therefore not uniformly distributed, then the 
+optimization problem becomes more difficult. In order to find a solution, it 
+is necessary to approximate a part of the PDF concerning the random-value 
+noise by a Gaussian function, which means that it is possible to use the 
+Gaussian mixture noise model to optimize the Gaussian plus impulse noise.
+
+\subsection{EXPERIMENTAL RESULTS}
+The experiments are conducted on mixed-noise Gaussian noise and on Gaussian 
+plus impulse noise. The indices used to estimate the quality of the restructured
+images are the \emph{Signal-to-Noise Ratio} (PSNR) and the \emph{Structural 
+Similarity Index} (SSIM) \cite{0884882841}.
+
+\subsubsection{Gaussian Mixed Noise}
+The quality comparison is done with different methods already existing in 
+the state of the art. From figure \ref{fig:GMNComp} you can see the application of 
+each of these methods on an image in which there is the presence of mixed-noise. 
+The proposed method produces a restructured image with a better level of 
+texture detail.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = \linewidth]{images/paper7/GMN comparison.png}
+    \centering
+    \caption{Image reconstruction under Gaussain mixture noise comparison.}
+    \label{fig:GMNComp}
+\end{figure}
+
+To test the efficiency of the methods, several images belonging to a 
+BSD100 dataset \cite{0884882842} were taken on which there are two Gaussian noises ($n_1$ 
+and $n_2$) with different mixture $r_1, r_2$ and standard deviation ($\sigma$). By comparing the 
+results obtained in table \ref{indexCompare}, the proposed method achieves the highest values 
+in both indices compared to the two methods \cite{0884882815} \cite{0884882819} most common in the 
+state of the art.
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{|c||ccc|ccc|ccc|}
+        \hline
+            & \multicolumn{3}{c||}{$\sigma_1=5 ~~~\sigma_2=30 $} & \multicolumn{3}{c||}{$\sigma_1=10 ~~~\sigma_2=50 $} & \multicolumn{3}{c||}{$\sigma_1=15 ~~~\sigma_2=75 $}\\
+        \hline        
+        $r_1:r_2\rightarrow$ & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3\\
+        \hline 
+        \hline
+        \multirow{2}{*}{PGPD\cite{0884882815}} & 29.42 & 30.16 & 31.19 & 27.23 & 27.88 & 28.78 &25.64 & 26.26 & 27.14\\
+        & 0.8132 & 0.8349 & 0.8544 & 0.7404 & 0.7634 & 0.7874 & 0.6790 & 0.7044 & 0.7336\\
+        \hline
+        \multirow{2}{*}{IRCNN\cite{0884882819}} & 29.83 & 30.53 & 31.48 & 27.66 & 28.25 & 29.04 & 19.37 & 25.22 & 27.32\\
+        & 0.8262 & 0.8451 & 0.8664 & 0.7611 & 0.7789 & 0.7993 & 0.2948 & 0.6423 & 0.7426\\
+        \hline
+        \multirow{2}{*}{Proposed} & \bfseries{29.88} & \bfseries{31.26} & \bfseries{32.72} & \bfseries{28.01} & \bfseries{29.00} & \bfseries{30.37} & \bfseries{26.23} & \bfseries{27.41} & \bfseries{28.84}\\
+        & \bfseries{0.8273} & \bfseries{0.8785} & \bfseries{0.9094} & \bfseries{0.7801} & \bfseries{0.8112} & \bfseries{0.8528} & \bfseries{0.6931} & \bfseries{0.7613} & \bfseries{0.8077}\\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Average PSNR and SSIM values on BSD100 datasets of some methods.}
+    \label{indexCompare}
+\end{table}

### 2021-04-14 papers/paper_7.tex
finish 7.4.3

@@
 The experiments are conducted on mixed-noise Gaussian noise and on Gaussian 
-plus impulse noise. The indices used to estimate the quality of the restructured
+plus impulse noise. The indexs used to estimate the quality of the restructured
 images are the \emph{Signal-to-Noise Ratio} (PSNR) and the \emph{Structural 
@@
 BSD100 dataset \cite{0884882842} were taken on which there are two Gaussian noises ($n_1$ 
-and $n_2$) with different mixture $r_1, r_2$ and standard deviation ($\sigma$). By comparing the 
+and $n_2$) with different ratios $r_1, r_2$ and standard deviation ($\sigma$). By comparing the 
 results obtained in table \ref{indexCompare}, the proposed method achieves the highest values 
@@
 \end{table}
+
+\subsubsection{Gaussian Noise Plus Impulse Noise}
+To remove the “salt and pepper” noise, only one image was used on which 
+this type of noise was applied. Also for this type of noise, the evaluation is 
+made by changing the mixture ratio r and the sigma standard deviation with 
+different values. The work done by the proposed method, compared with the 
+other methods, is visible in figure \ref{fig:saltComp}. As for the values obtained of the PSNR 
+and SSIM indexs, these are visible in table \ref{GNPINIndex}.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = \linewidth]{images/paper7/salt.png}
+    \centering
+    \caption{Image reconstruction under Gaussain noise plus random-valued noise comparison.}
+    \label{fig:saltComp}
+\end{figure}
+
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{|c||ccc|ccc|ccc|}
+        \hline
+            & \multicolumn{3}{c||}{$\sigma_1=5$} & \multicolumn{3}{c||}{$\sigma_1=10$} & \multicolumn{3}{c||}{$\sigma_1=15$}\\
+        \hline        
+        $r\rightarrow$ & 0.1 & 0.2 & 0.3 & 0.1 & 0.2 & 0.3 & 0.1 & 0.2 & 0.3\\
+        \hline 
+        \hline
+        \multirow{2}{*}{Noisy} & 18.76 & 15.76 & 14.04 & 18.43 & 15.61 & 13.95 & 17.94 & 15.38 & 13.81\\
+        & 0.3545 & 0.2290 & 0.1662 & 0.3313 & 0.2216 & 0.1626 & 0.3040 & 0.2109 & 0.1571\\
+        \hline
+        \multirow{2}{*}{Two-phase\cite{0884882828}} & 25.40 & 24.77 & 24.13 & 24.34 & 23.94 & 23.45 & 23.32 & 23.02 & 22.67\\
+        & 0.6599 & 0.6313 & 0.5957 & 0.5116 & 0.4914 & 0.4655 & 0.4224 & 0.4058 & 0.3854\\
+        \hline
+        \multirow{2}{*}{ACWMF+K-SVD \cite{0884882844}\cite{0884882813}} & 26.07 & 25.27 & 24.54 & 25.50 & 24.91 & 23.13 & 24.64 & 24.19 & 23.67\\
+        & 0.7130 & 0.6761 & 0.6333 & 0.5902 & 0.5613 & 0.5291 & 0.4855 & 0.4625 & 0.4414\\
+        \hline    
+        \multirow{2}{*}{LSM-NLR \cite{0884882826}} & 29.48 & 26.97 & 24.55 & 29.43 & 27.08 & 24.43 & 28.51 & 26.06 & 23.98\\
+        & 0.6548 & 0.5774 & 0.4982 & 0.6420 & 0.5646 & 0.4770 & 0.6282 & 0.5458 & 0.4643\\
+        \hline
+        \multirow{2}{*}{$l_1-l_0$\cite{0884882829}} & 30.45 & 27.75 & 25.95 & 28.45 & 26.59 & 25.34 & 27.33 & 25.69 & 24.55\\
+        & 0.8962 & 0.7911 & 0.7312 & 0.7539 & 0.6748 & 0.6293 & 0.6793 & 0.6010 & 0.5744\\
+        \hline
+        \multirow{2}{*}{Proposed} & \bfseries{31.06} & \bfseries{30.44} & \bfseries{27.66} & \bfseries{30.97} & \bfseries{29.5} & \bfseries{27.41} & \bfseries{29.74} & \bfseries{28.09} & \bfseries{25.73}\\
+        & \bfseries{0.9214} & \bfseries{0.9157} & \bfseries{0.8497} & \bfseries{0.8943} & \bfseries{0.8749} & \bfseries{0.8316} & \bfseries{0.8530} & \bfseries{0.8222} & \bfseries{0.7750}\\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Average PSNR and SSIM values on one image of some methods.}
+    \label{GNPINIndex}
+\end{table}
+
+\subsubsection{Realistic Noise Removal}
+The model was also tested with the images present in the dataset provided 
+in \cite{0884882845}. From the following images only one of their cut out parts is taken 
+(Fig \ref{fig:crop}). This time the EM-CNN model was compared with different types 
+of existing denoising, including the IRCNN which is adopted by CNN of the 
+proposed model. Figure \ref{fig:cropRes} shows the results, in terms of PSNR, obtained on 
+each cropped image. From these results it can be seen that the proposed 
+model does not always manage to obtain the best result, but in any case its 
+PSNR average remains higher than the competing denoisers.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = \linewidth]{images/paper7/crop.png}
+    \centering
+    \caption{Cropped real noisy images.}
+    \label{fig:crop}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/paper7/crop result.png}
+    \centering
+    \caption{PSNR result of different methods on cropped real noisy images.}
+    \label{fig:cropRes}
+\end{figure}

### 2021-04-14 papers/paper_7.tex
finish paper7

@@
     \centering
-    \includegraphics[width = 0.8\linewidth]{images/paper7/crop result.png}
+    \includegraphics[width = 0.7\linewidth]{images/paper7/crop result.png}
     \centering
@@
 \end{figure}
+
+\subsection{CONCLUSION}
+Noise removal, as well as being carried out by the denoiser, is given by the 
+learning made by the CNN network on the new input images which, through 
+an iterative process, are gradually improved. This is possible only thanks to 
+the estimates derived from the EM algorithm and how this can classify the 
+various types of noise. Without this information, each input image would 
+not get the proper correction, thus generating incorrect output images.

### 2021-04-15 slides/slides_paper7.tex
slides paper7

\section{Paper 7}
\subsection{\emph{"Variational-Based Mixed Noise Removal With CNN Deep Learning Regularization"}}

\begin{frame}{INTRODUCTION}
    Random noise distributions correspond to standard probabilistic distributions, 
    such as the Gaussian, Poisson and other distributions. There have 
    been many methods that attempt to clean up noisy images. Other tools such as the Variational method have been widely used. 
    This method is based on reducing the cost function containing the fidelity 
    term of the data, useful for calculating the difference between true and observed 
    data, and the regularization terms. In the 
    proposed article, the EM (Expectation-Maximization) algorithm is used to 
    remove the noise, with the integration of a CNN process as regularization, 
    in order to create a new variational method.
\end{frame}

\begin{frame}{RELATED WORK - Variational Method Approach}
    To obtain the clean image is necessry minimizing a cost functional(\ref{cost}).
    \begin{block}{COST-FUNCTIONAL}
        \begin{equation}\label{cost}
            F(u) = E(u)+\lambda\mathcal{J}(u)
        \end{equation}
    \end{block}
    where $E(u)$ is the set of data fidelity terms belonging to each pixel of the 
    image $u$ useful to measure the discrepancy between the true and the 
    observed data and it can derived from the maximum likelihood estimation 
    of noise, task perfromed by the EM algorithm \footfullcite{0884882814}.  $\mathcal{J}$ is a regularizer while $ \lambda $ 
    control the balance of the terms
\end{frame}

\begin{frame}{RELATED WORK - What types of image noise?}
    The noises analyzed in this paper are mainly two categories of Gaussian 
    noises:
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{block}{GAUSSIAN MIXED-NOISE}
                $$
                \small
                n = \left\{
                    \begin{array}{cc}
                        n_1, & with~probability~r_1\\
                        n_2, & with~probability~r_2\\
                        \cdots, & \cdots\\
                        n_k, & with~probability~r_k\\ 
                    \end{array}
                    \right\}
                $$
            \end{block}  
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.47\linewidth}
            \begin{block}{GAUSSIAN RANDOM NOISE}
                $$
                \small
                n = \left\{
                    \begin{array}{cc}
                        n_1, & with~probability~1-r\\
                        n_2, & with~probability~r\\
                    \end{array}
                    \right\}
                $$
            \end{block} 
        \end{minipage}
    \end{minipage}
    where $ n_k $ is the \emph{k}-th noise component with probability density function (PDF) 
    $ p_k $ and $ r_k $ are the unknown mixture ratios and thei sum is equal to 
    1. Each type of noise has a standard deviation ($\sigma$) which indicates the 
    amount of noise distribution present.     
\end{frame}

### 2021-04-15 papers/paper_7.tex
slide paper7 architecture

@@
 of noise in each pixel. The work carried out is divided into four phases: 
-regularization, synthesis, parameter estimation and error classification.
+regularization, synthesis, parameter estimation and noise classification.
 
@@
 noise reduction (updating the Lagragian multiplier $u$), parameter estimation 
-noise ($\Theta$ update) and error classification ($w$ update). The formula used by 
+noise ($\Theta$ update) and noise classification ($w$ update). The formula used by 
 the model is able to handle different types of Gaussian noises such as impulse 
@@
 the image $u^{v+1}$. Subsequently, to calcutale the fidelity term, the EM algorithm 
-\cite{0884882814} is applied to this noise which has the task of estimating the error 
+\cite{0884882814} is applied to this noise which has the task of estimating the noise 
 and classifying it by minimizing the terms of \ref{HFunctionGMM}. The minimization of each 

### 2021-04-15 slides/slides_paper7.tex
slide paper7 architecture

@@
     in order to create a new variational method.
-\end{frame}
-
-\begin{frame}{RELATED WORK - Variational Method Approach}
-    To obtain the clean image is necessry minimizing a cost functional(\ref{cost}).
-    \begin{block}{COST-FUNCTIONAL}
-        \begin{equation}\label{cost}
-            F(u) = E(u)+\lambda\mathcal{J}(u)
-        \end{equation}
-    \end{block}
-    where $E(u)$ is the set of data fidelity terms belonging to each pixel of the 
-    image $u$ useful to measure the discrepancy between the true and the 
-    observed data and it can derived from the maximum likelihood estimation 
-    of noise, task perfromed by the EM algorithm \footfullcite{0884882814}.  $\mathcal{J}$ is a regularizer while $ \lambda $ 
-    control the balance of the terms
 \end{frame}
@@
 \end{frame}
+
+\begin{frame}{RELATED WORK - Variational Method Approach}
+    To obtain the clean image is necessry minimizing a cost functional(\ref{cost}).
+    \begin{block}{COST-FUNCTIONAL}
+        \begin{equation}\label{cost}
+            F(u) = E(u)+\lambda\mathcal{J}(u)
+        \end{equation}
+    \end{block}
+    where $E(u)$ is the set of data fidelity terms belonging to each pixel of the 
+    image $u$ useful to measure the discrepancy between the true and the 
+    observed data and it can derived from the maximum likelihood estimation 
+    of noise, task perfromed by the EM algorithm \footfullcite{0884882814}.  $\mathcal{J}$ is a regularizer while $ \lambda $ 
+    control the balance of the terms
+\end{frame}
+
+\begin{frame}{RELATED WORK - EM Algorithm (An Optimization problem)}
+    The EM algorithm is applied to this noise which has the task of estimating the noise 
+    and classifying it by minimizing the terms of \ref{HFunction}. The minimization of each 
+    weight $w$ leads to a continuous updating of this parameter which translates 
+    into greater precision in determining the noise on each individual pixel.
+    \begin{equation}\label{HFunction}
+        (u^*, \Theta^*, w^*) = \argmin_x\left\{H(u,\Theta,w) + \lambda_1\mathcal{J}(u)\right\}
+    \end{equation}
+    where $\Theta^*$ is a statistical parameters set contains noise parameters such as mixture ratios ($r$), means and variances ($\sigma^2$).
+\end{frame}
+
+\begin{frame}{THE PROPOSED METHOD (EM-CNN) - Architecture}
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            The convolutional neural network (CNN) performs the following tasks            
+            \begin{enumerate}
+                \item Smoothness (Denoiser)
+                \item Regularization (TV)
+                \item Synthesis (Best Choice)
+                \item Parameters estimation (EM)
+                \item Noise classification (EM)
+                \item Output (Restored image and Noise Estimation)
+            \end{enumerate} 
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.47\linewidth}
+            \begin{figure}[h!]
+                \centering
+                \includegraphics[width = 1 \linewidth]{images/paper7/flowchart.png}
+                \centering
+                \label{fig:EM-CNN}
+            \end{figure}
+        \end{minipage}
+    \end{minipage}
+\end{frame}

### 2021-04-15 papers/paper_7.tex
finish slides paper7

@@
 To test the efficiency of the methods, several images belonging to a 
-BSD100 dataset \cite{0884882842} were taken on which there are two Gaussian noises ($n_1$ 
+BSDS100 dataset \cite{0884882842} were taken on which there are two Gaussian noises ($n_1$ 
 and $n_2$) with different ratios $r_1, r_2$ and standard deviation ($\sigma$). By comparing the 

### 2021-04-15 slides/slides_paper7.tex
finish slides paper7

@@
 \end{frame}
+
+\begin{frame}{EXPERIMENTAL RESULTS - Gaussian mixed-noise}
+    The indexs used to estimate the quality of the restructured images are 
+    the \emph{Signal-to-Noise Ratio} (PSNR) and the \emph{Structural Similarity Index} 
+    (SSIM). The results obtained by comparing different methods with the 
+    proposed, in image reconstruction and Gaussian mixed-noise removal, one 
+    are visible in figure \ref{fig:GMNComp} and table \ref{indexCompare}. The set test images were taken from 
+    the BSDS100 dataset.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 0.8\linewidth]{images/paper7/GMN comparison.png}
+        \centering
+        \caption{Image reconstruction under Gaussain mixture noise comparison.}
+        \label{fig:GMNComp}
+    \end{figure}
+
+    \begin{table}[htbp]
+        \centering
+        \begin{adjustbox}{width=0.8\textwidth}
+        \begin{tabular}{|c||ccc|ccc|ccc|}
+            \hline
+                & \multicolumn{3}{c||}{$\sigma_1=5 ~~~\sigma_2=30 $} & \multicolumn{3}{c||}{$\sigma_1=10 ~~~\sigma_2=50 $} & \multicolumn{3}{c||}{$\sigma_1=15 ~~~\sigma_2=75 $}\\
+            \hline        
+            $r_1:r_2\rightarrow$ & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3\\
+            \hline 
+            \hline
+            \multirow{2}{*}{PGPD\cite{0884882815}} & 29.42 & 30.16 & 31.19 & 27.23 & 27.88 & 28.78 &25.64 & 26.26 & 27.14\\
+            & 0.8132 & 0.8349 & 0.8544 & 0.7404 & 0.7634 & 0.7874 & 0.6790 & 0.7044 & 0.7336\\
+            \hline
+            \multirow{2}{*}{IRCNN\cite{0884882819}} & 29.83 & 30.53 & 31.48 & 27.66 & 28.25 & 29.04 & 19.37 & 25.22 & 27.32\\
+            & 0.8262 & 0.8451 & 0.8664 & 0.7611 & 0.7789 & 0.7993 & 0.2948 & 0.6423 & 0.7426\\
+            \hline
+            \multirow{2}{*}{Proposed} & \bfseries{29.88} & \bfseries{31.26} & \bfseries{32.72} & \bfseries{28.01} & \bfseries{29.00} & \bfseries{30.37} & \bfseries{26.23} & \bfseries{27.41} & \bfseries{28.84}\\
+            & \bfseries{0.8273} & \bfseries{0.8785} & \bfseries{0.9094} & \bfseries{0.7801} & \bfseries{0.8112} & \bfseries{0.8528} & \bfseries{0.6931} & \bfseries{0.7613} & \bfseries{0.8077}\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Average PSNR and SSIM values on BSD100 datasets of some methods.}
+        \label{indexCompare}
+    \end{table}
+
+\end{frame}
+
+\begin{frame}{EXPERIMENTAL RESULTS - Gaussian random-noise}
+    As for the reconstruction of an image affected by random noise, also 
+    called salt and pepper noise, the results obtained from the comparison of 
+    different methods are visible in figure \ref{fig:saltComp} and in table \ref{GNPINIndex}. As in the previous 
+    experiment, the indexs are calculated by changing the mixed-ratio $r$ and 
+    standard deviation $\sigma$ values.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 0.7\linewidth]{images/paper7/salt.png}
+        \centering
+        \caption{Image reconstruction under Gaussain noise plus random-valued noise comparison.}
+        \label{fig:saltComp}
+    \end{figure}
+
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=0.7\textwidth}
+        \begin{tabular}{|c||ccc|ccc|ccc|}
+            \hline
+                & \multicolumn{3}{c||}{$\sigma_1=5$} & \multicolumn{3}{c||}{$\sigma_1=10$} & \multicolumn{3}{c||}{$\sigma_1=15$}\\
+            \hline        
+            $r\rightarrow$ & 0.1 & 0.2 & 0.3 & 0.1 & 0.2 & 0.3 & 0.1 & 0.2 & 0.3\\
+            \hline 
+            \hline
+            \multirow{2}{*}{Noisy} & 18.76 & 15.76 & 14.04 & 18.43 & 15.61 & 13.95 & 17.94 & 15.38 & 13.81\\
+            & 0.3545 & 0.2290 & 0.1662 & 0.3313 & 0.2216 & 0.1626 & 0.3040 & 0.2109 & 0.1571\\
+            \hline
+            \multirow{2}{*}{Two-phase\cite{0884882828}} & 25.40 & 24.77 & 24.13 & 24.34 & 23.94 & 23.45 & 23.32 & 23.02 & 22.67\\
+            & 0.6599 & 0.6313 & 0.5957 & 0.5116 & 0.4914 & 0.4655 & 0.4224 & 0.4058 & 0.3854\\
+            \hline
+            \multirow{2}{*}{ACWMF+K-SVD \cite{0884882844}\cite{0884882813}} & 26.07 & 25.27 & 24.54 & 25.50 & 24.91 & 23.13 & 24.64 & 24.19 & 23.67\\
+            & 0.7130 & 0.6761 & 0.6333 & 0.5902 & 0.5613 & 0.5291 & 0.4855 & 0.4625 & 0.4414\\
+            \hline    
+            \multirow{2}{*}{LSM-NLR \cite{0884882826}} & 29.48 & 26.97 & 24.55 & 29.43 & 27.08 & 24.43 & 28.51 & 26.06 & 23.98\\
+            & 0.6548 & 0.5774 & 0.4982 & 0.6420 & 0.5646 & 0.4770 & 0.6282 & 0.5458 & 0.4643\\
+            \hline
+            \multirow{2}{*}{$l_1-l_0$\cite{0884882829}} & 30.45 & 27.75 & 25.95 & 28.45 & 26.59 & 25.34 & 27.33 & 25.69 & 24.55\\
+            & 0.8962 & 0.7911 & 0.7312 & 0.7539 & 0.6748 & 0.6293 & 0.6793 & 0.6010 & 0.5744\\
+            \hline
+            \multirow{2}{*}{Proposed} & \bfseries{31.06} & \bfseries{30.44} & \bfseries{27.66} & \bfseries{30.97} & \bfseries{29.5} & \bfseries{27.41} & \bfseries{29.74} & \bfseries{28.09} & \bfseries{25.73}\\
+            & \bfseries{0.9214} & \bfseries{0.9157} & \bfseries{0.8497} & \bfseries{0.8943} & \bfseries{0.8749} & \bfseries{0.8316} & \bfseries{0.8530} & \bfseries{0.8222} & \bfseries{0.7750}\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Average PSNR and SSIM values on one image of some methods.}
+        \label{GNPINIndex}
+    \end{table}
+\end{frame}
+
+\begin{frame}{CONCLUSION}
+    Even reaching good performances, the proposed method does not always 
+    manage to obtain better results than those of competing methods. 
+    However, the average of the PSNR index achieved is the highest (Fig. \ref{fig:cropRes}).
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = \linewidth]{images/paper7/crop.png}
+        \centering
+        \caption{Cropped real noisy images.}
+        \label{fig:crop}
+    \end{figure}
+
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 0.7\linewidth]{images/paper7/crop result.png}
+        \centering
+        \caption{PSNR result of different methods on cropped real noisy images.}
+        \label{fig:cropRes}
+    \end{figure}
+
+\end{frame}

### 2021-04-15 papers/paper_8.tex
finish 8.1

\section{Visual Object Tracking via Multi-Stream Deep Similarity Learning Networks}

\begin{center}
    \author{
    Kunpeng Li,
    \emph{Student Member, IEEE},
    Yu Kong,
    \emph{Member, IEEE},
    Yunf Fu,
    \emph{Fellow, IEEE}
    }
\end{center}

\begin{center}
    \emph{IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL.29, 2020}
\end{center}

\subsection{INTRODUCTION}
The goal of visual tracking systems is to be able to obtain the position of 
the tracked target even in subsequent frames. The problems to be solved are 
those of occlusion, background clutter, illumination variations, deformation 
etc. The existing state-of-the-art models carry out training online exclusively. 
Some methods, based on pre-trained convolutional networks (CNN), track 
the object based on the background. In these networks, stochastic gradient 
descent is applied in order to update the entire network. However, these 
models appear to be too slow and do not work well in real-time. The following 
paper uses a model that compares similarities and is trained offline in order to 
predict the patch present in the next frame. The method, thanks to the use of 
the relative distance, is robust in the presence of phenomena that introduce 
the so called distractors. The purpose is to be able to compare the patch that 
identifies the target template (the object) with all the possible positions 
of the same region belonging to the next frame. In addition to tracking the 
object, the proposed model is a framework for EMDSLT tracking like the 
one shown in figure \ref{fig:EMDSLT}. Within it, two procedures are considered important: 
updating the model and self-recovery from failures. The network is composed 
of two types of structures, one that is responsible for dast-speed verification 
and production of the tracking results, while the second is responsible for re-verification 
and re-detection of the target object on the patches previously 
generated.
\begin{figure}[h!]
    \centering
    \includegraphics[width = \linewidth]{images/paper8/EMDSLT.png}
    \centering
    \caption{The framework of EMDSLT proposed method.}
    \label{fig:EMDSLT}
\end{figure}.

### 2021-04-15 papers/paper_8.tex
finish 8.2

@@
 \end{figure}.
+
+\subsection{RELATED WORK}
+Methods such as generative trackers have been developed for finding positions 
+in which to find the best candidate during the tracking process. Good 
+results have been achieved by compound trackers \cite{0893551105} \cite{0893551118}. Networks such as 
+RNNs \cite{0893551121} can be used to predict possible target positions in each frame. 
+However, these types of networks have not yet achieved satisfactory results. 
+Some methods instead train a CNN offline while the test is done online. Unfortunately, 
+these models are not fast. Other models instead if they fail a first 
+time, then they will always fail until the target returns to the search region. 
+Methods such as \cite{0893551129} \cite{0893551134} search for the target template in subsequent frames 
+in the same position, obtaining better performance than methods based on 
+similarity but nevertheless are not robust to distracting elements. The proposed 
+method instead takes into account both the background patches and 
+the target template patches in order to make comparisons on similarities.

### 2021-04-15 papers/paper_8.tex
finish 8.3.1

@@
 the target template patches in order to make comparisons on similarities.
+
+\subsection{METHODS}
+\subsubsection{Multi Stream Deep Similarity Learning Networks}
+A mulit-stream similarity learning network is used in this paper. In the 
+proposed framework there are various data streams (Fig. \ref{fig:EMDSLT}):
+\begin{enumerate}
+    \item Template Stream: the target template defined in the beginning frame;
+    \item Searching Stream: the search region;
+    \item Background Stream: background patches that sample around the target 
+    in the beginning frame.
+\end{enumerate}
+
+\subsubsection{Template-Searching-Background Loss}

### 2021-04-16 papers/paper_8.tex
finish 8.3.2

@@
 \subsubsection{Template-Searching-Background Loss}
+Several positive $X^+_i$, negative $X^-_i$ and background $B_{i-1,j}$ patches can be generated in an image.
+Patches are considered positive if they have a small cosine distance with the target template $T$, on the contrary, patches will be considered negative if they are closer to the background patches within the search region $S_i$.
+The loss function to be minimized is the following:
+\begin{equation}
+    L(T,\{X_{i,k}\}^N_{k=1}, \{B_{i-1}\}^M_{j=1}) = \sum_{k=1}^NL(T,X_{i,k}, \{B_{i-1,j}\}^M_{j=1})
+\end{equation}
+Where $T$ is the target template, $X_{i,k}$ is the $k-th$ candidate patch $X$ of frame $i$, $M$ is the number of background patches and $N$ is the number of candidate patches $X_{i,k}$.

### 2021-04-16 papers/paper_8.tex
finish 8.3.4

@@
 \subsubsection{Template-Searching-Background Loss}
-Several positive $X^+_i$, negative $X^-_i$ and background $B_{i-1,j}$ patches can be generated in an image.
-Patches are considered positive if they have a small cosine distance with the target template $T$, on the contrary, patches will be considered negative if they are closer to the background patches within the search region $S_i$.
-The loss function to be minimized is the following:
+Several positive $X^+_i$, negative $X^-_i$ and background $B_{i-1,j}$ patches can be 
+generated in an image. Patches are considered positive if they have a small 
+cosine distance with the target template $T$, on the contrary, patches will be 
+considered negative if they are closer to the background patches within the 
+search region $S_i$. The loss function to be minimized is the following:
 \begin{equation}
@@
 \end{equation}
-Where $T$ is the target template, $X_{i,k}$ is the $k-th$ candidate patch $X$ of frame $i$, $M$ is the number of background patches and $N$ is the number of candidate patches $X_{i,k}$.
+Where $T$ is the target template, $X_{i,k}$ is the $k-th$ candidate patch $X$ of frame 
+$i$, $M$ is the number of background patches and $N$ is the number of candidate 
+patches $X_{i,k}$.
+
+\subsubsection{Tracking Method}
+Background patches are obtained by sampling around the previous positions 
+of frame $i-1$. The background patches that have a high correlation with 
+the target template will be definitively chosen. Find these patches first, the 
+selected $X_i$ pateches will be the ones that will match the target template and 
+discriminate against the background patches. Ultimately, the choice of 
+patch $X_i$ comes down to an optimization problem.
+\begin{equation}
+    X_i = \argmin_{X_{i,k} \in S_i}d(T,X_{i,k}, \{B_{i-1,j}\}^M_{j=1})
+\end{equation}
+where $d(\cdot)$ is a distance function.
+
+\subsubsection{Tracking With Updating}
+As already mentioned, the two important aspects of the framework are to update the model and allow self-recovery when it is unable to track the target.
+In order to guarantee these two operations, a confidence assessment of the monitoring results must be carried out.
+The set of patches Xi, each of which belongs to each frame ($K = k_1$), is passed to the part of the network that performs the re-verification in order to return the "\emph{Trust Score s}" obtained based on the similarity with the target template .
+This score indicates the confidence level of the monitoring and can then be used to identify any errors that can be corrected with an update of the taget template.
+When the s score is less than a $\sigma$ threshold.
+then a failure has occurred.
+If a failure occurs, then the number of frames ($K = k_2$) would be increased by 1 and then re-detected, on the patches, which would return a new patch $X'$ with a new score $s'$.
+If $s'> \sigma$, then this will be the new tracking result ending the recovery process.
+When this occurs, the target template, calculated with the new formula (\ref{newX}) will be updated and then replaced with the last detected.
+In \ref{newX}, $m$ represents the matching function, $m(a,b)=f(a)^Tf(b)$, used to obtain the Trust Score.
+\begin{equation}\label{newX}
+    X'_i = \argmax_{X_{i,k} \in S_i}m(T,X_{i,k})
+\end{equation}

### 2021-04-17 papers/paper_8.tex
finish 8.4.2

@@
 \subsubsection{Tracking With Updating}
-As already mentioned, the two important aspects of the framework are to update the model and allow self-recovery when it is unable to track the target.
-In order to guarantee these two operations, a confidence assessment of the monitoring results must be carried out.
-The set of patches Xi, each of which belongs to each frame ($K = k_1$), is passed to the part of the network that performs the re-verification in order to return the "\emph{Trust Score s}" obtained based on the similarity with the target template .
-This score indicates the confidence level of the monitoring and can then be used to identify any errors that can be corrected with an update of the taget template.
-When the s score is less than a $\sigma$ threshold.
-then a failure has occurred.
-If a failure occurs, then the number of frames ($K = k_2$) would be increased by 1 and then re-detected, on the patches, which would return a new patch $X'$ with a new score $s'$.
-If $s'> \sigma$, then this will be the new tracking result ending the recovery process.
-When this occurs, the target template, calculated with the new formula (\ref{newX}) will be updated and then replaced with the last detected.
-In \ref{newX}, $m$ represents the matching function, $m(a,b)=f(a)^Tf(b)$, used to obtain the Trust Score.
+As already mentioned, the two important aspects of the framework are to 
+update the model and allow self-recovery when it is unable to track the target. 
+In order to guarantee these two operations, a confidence assessment of the 
+monitoring results must be carried out. The set of patches $X_i$ belonging to 
+each frame in $(K = k_1)$, is passed to the part of the network that performs 
+the re-verification in order to return the "\emph{Trust Score s}" obtained based on 
+the similarity with the target template. This score indicates the confidence 
+level of the monitoring and can then be used to identify any errors that can 
+be corrected with an update of the target template. When the $s$ score is less 
+than a $\sigma_1$ threshold, then a failure has occurred. If a failure occurs, then the 
+number of frames $K = k_2$ is set lower and then re-detection is performed, 
+which would return a new patch $X'_i$, calculated with the formula \ref{newX}, and a 
+new score $s'$. If $s'> \sigma_1$, then the new tracking patch will be $X'_i$. In \ref{newX}, $m$ 
+represents the matching function, $m(a,b)=f(a)^Tf(b)$, used to obtain 
+the Trust Score. If $s$ is greater than $\sigma_2$, then the target template $T$ is updated 
+with patches $X_i$.
 \begin{equation}\label{newX}
@@
 \end{equation}
+
+\subsection{EXPERIMENTS}
+\subsubsection{Network Architecture}
+The proposed CNN network is similar to that of AlexNet \cite{0893551108} with five convolutional 
+layers of which only the first two are followed by two max pool 
+layers. The batch normalization \cite{0893551138} and the ReLu layers are present after 
+each convolutional layer except the last.
+
+\subsubsection{Training Details}
+To train the model, the videos contained in the ImageNet dataset were used, 
+more precisely 90\% of the videos are used as a training set and the remaining 
+10\% as a validation set. The training cycles are 240K with mini-batch size 8. 
+The target template is set in each random frame of each training video. From 
+two other random adjacent frames, the background patches and the search 
+region are chosen. In the search region, a candidate patch $Xi$ is labeled 
+positive if its overlap with the ground truth bounding box is greater than 
+0.7, otherwise it is considered negative. As for the background patches, these 
+are selected if they have an overlap with the ground truth in the range 0.1 to 
+0.5. The number of frames $k_1$ is set to 10, while $k_2$ is equal to 1 (it 
+indicates the re-detection process will take place in sequence on each single 
+patch that has caused the tracking to fail), while the $\sigma_1$ and $\sigma_2$ thresholds 
+are set accordingly to 1.6 and 2.

### 2021-04-17 papers/paper_8.tex
finish 8.4.3

@@
 are set accordingly to 1.6 and 2.
+
+\subsubsection{Experimental Setup}
+The experiments were conducted on four different types of datasets: OTB-2013 
+\cite{0893551142}, OTB-100 \cite{0893551143}, VOT-2015 \cite{0893551144} and VOT-2016 \cite{0893551140}. The first two contain 
+a total of 150 bounding-box annotated videos and two metrics, precision 
+plots and success plots were used to assess the quality of the tracing. The 
+first metric reaches a high value when the distance between the bounding-box 
+(ground-truth) centers and the predicted one are less than a certain threshold, 
+while the second metric takes into account the overlap of the two components, 
+which is calculated with \emph{IoU} index. The last two datasets contain 
+a total of 100 videos and the metrics to evaluate the tracking are accuracy, 
+robustness and the expected average overlap (\emph{EAO}). To be considered good, 
+a tracker must achieve high accuracy and a high AEO score, while it must 
+achieve a low robustness score.

### 2021-04-17 papers/paper_8.tex
finish paper8

@@
 considered negative if they are closer to the background patches within the 
-search region $S_i$. The loss function to be minimized is the following:
+search region $S_i$. The loss-function calculation encourages the distance 
+between a positive patch and the background patches to be greater than that 
+between the positive patch and the target model.
 \begin{equation}
-    L(T,\{X_{i,k}\}^N_{k=1}, \{B_{i-1}\}^M_{j=1}) = \sum_{k=1}^NL(T,X_{i,k}, \{B_{i-1,j}\}^M_{j=1})
+    L(T,\{X_{i,k}\}^N_{k=1}, \{B_{i-1}\}^M_{j=1}) = log(1+e^{l_id_i})
 \end{equation}
@@
 $i$, $M$ is the number of background patches and $N$ is the number of candidate 
-patches $X_{i,k}$.
+patches $X_{i,k}$. $d(\cdot)$ is the distance function:
+\begin{equation}\label{distanceFunc}
+    d_i=\sum^M_{j=1} D(T, X_i) - D(X_i, B_{i-1,j})
+\end{equation}
+where $D$ is the cosine distance that describe the distance of two image patches 
+$X_1$ and $X_2$ and $l_i \in \{+1,-1\}$ is the ground truth label of $X_i$. Since the 
+loss function must be calculated for each patch, the shortest distance will 
+be chosen based on the values returned by the calculation of the following 
+loss-function (\ref{FinalLoss}).
+\begin{equation}\label{FinalLoss}
+    L(T,\{X_{i,k}\}^N_{k=1}, \{B_{i-1}\}^M_{j=1}) = \sum_{k=1}^NL(T,X_{i,k}, \{B_{i-1,j}\}^M_{j=1})
+\end{equation}
 
@@
 achieve a low robustness score.
+
+\subsubsection{Result and Analysis}
+\begin{enumerate}
+    \item \emph{Comparison with Recent Real-Time Trackers}: the performance of each tracker, including the one proposed, is shown below.
+For the OTB dataset, several metrics are used to evaluate its tracking quality.
+Among these metrics we have those of AUC and precision, while for the VOT dataset the metrics specified above are used (Fig.\ref{fig:PerfComp}).
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = \linewidth]{images/paper8/metrics.png}
+        \centering
+        \caption{Performance comparison with Recent Real-Time Trackers}
+        \label{fig:PerfComp}
+    \end{figure}
+    \item \emph{Attribute-Based Evaluation}: the presence of distracting elements leads 
+    many methods to fail to track them. In figure \ref{fig:AUCScore} it is possible to see the 
+    comparison, in terms of AUC score, reached by different methods on 
+    the OTB-2013 dataset, when these elements are present. The values 
+    in blue are the highest and are obtained from the best method, while 
+    those in red are placed in second position.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = \linewidth]{images/paper8/AUC.png}
+        \centering
+        \caption{AUC score on OTB-2013 dataset.}
+        \label{fig:AUCScore}
+    \end{figure}
+    \item \emph{Qualitative Evaluation}: The use of the Template-Searching-Background (TSB), allows you to use the background patches to train the model (Fig.\ref{fig:TSBMin}).
+This method helps to minimize the relative distance $d(\cdot)$ (\ref{distanceFunc}) which translated into other words means bringing the target template closer to the $X_i^+$ samples and at the same time moving the background distractors $B_i$ away from the positive sample.
+This method allows for better performance than existing state-of-the-art models.
+A visual example of comparison of the trackers made by the different methods, including the one proposed, is visible in figure \ref{fig:qualitativeTracking}.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = \linewidth]{images/paper8/TSB.png}
+        \centering
+        \caption{Template-Searching-Background to minimizes the relative distance.}
+        \label{fig:TSBMin}
+    \end{figure}
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = \linewidth]{images/paper8/qualitative.png}
+        \centering
+        \caption{Qualitative reuslt of seven trackers. The bounding box with an orange dotted line shows the ground-truth localization of the target object.}
+        \label{fig:qualitativeTracking}
+    \end{figure}
+\end{enumerate}
+
+\subsection{CONCLUSION}
+The proposed framework, from the results obtained in the benchmarks, seems 
+to be the best. The achievement of these results were possible thanks to the 
+integration of a verification and detecting method. The use of the TSB 
+method was fundamental, which, by reducing the relative distance between 
+the various patches, allowed for good model learning.

### 2021-04-17 slides/slides_paper8.tex
working on slides of paper8

\section{Paper 8}
\subsection{\emph{"Visual Object Tracking via Multi-Stream Deep Similarity Learning Networks"}}

\begin{frame}{INTRODUCTION}
    The goal of visual tracking systems is to be able to obtain the position of 
    the tracked target even in subsequent frames. The problems to be solved 
    are those of occlusion, background clutter, illumination variations, 
    deformation etc. The following paper uses a model that compares 
    similarities and is trained offline in order to predict the patch present in 
    the next frame. The method, thanks to the use of the relative distance, 
    is robust in the presence of phenomena that introduce the so called 
    \emph{distractors}.
\end{frame}

\begin{frame}{RELATED WORK}
    Some methods train a CNN offline while the test is done online. Unfortunately, 
    these models are not fast. Other models instead if they fail a first 
    time, then they will always fail until the target returns to the search region. 
    Other methods \footfullcite{0893551129} \footfullcite{0893551134} search for the target template in subsequent frames 
    in the same position, obtaining better performance than methods based on 
    similarity but nevertheless are not robust to distracting elements. The proposed 
    method instead takes into account both the \emph{background patches} and 
    the \emph{target template patches} in order to make comparisons on similarities.
\end{frame}

\begin{frame}{METHODS - EMDSLT Architecture}
    The proposed framework, called Ensemble Multi Deep Stream Similarity 
    Learnining Tracking (EMDSLT), is composed of some netwroks. Those 
    in blue are fully-convolutional networks while those in red are useful for 
    re-verification and re-detection operations, responsible for recovery from 
    failures and the template updating.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/EMDSLT.png}
        \centering
        \caption{The EMDSLT framework.}
        \label{fig:EMDSLT}
    \end{figure}
\end{frame}

\begin{frame}{METHODS - Streams}
    The target template \emph{T}, the patches $X_i^+$ positive and the background patches $B_{i-1,j}$, are extracted from the first convolutional networks. These elements are useful for calculating the \emph{Template-Searching-Background Loss} (TSB).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/streams.png}
        \centering
        \caption{Multi Deep Streams}
        \label{fig:streams}
    \end{figure}
\end{frame}

\begin{frame}{METHODS - \emph{Template-Searching-Background Loss} (TSB)}

\end{frame}

### 2021-04-17 slides/slides_paper8.tex
finish slides of paper8

@@
 \begin{frame}{METHODS - \emph{Template-Searching-Background Loss} (TSB)}
+    The use of the Template-Searching-Background (TSB), allows to use the 
+    background patches to train the model. This method helps to minimize 
+    the relative distance $d(\cdot)$ (\ref{distanceFunc}) which translated into other words means 
+    bringing the target template closer to the $X_i^+$ samples and at the same 
+    time moving the background distractors $B_i$ away from the positive 
+    sample.
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{block}{RELATIVE DISTANCE}
+                \begin{equation}\label{distanceFunc}
+                    d_i=\sum^M_{j=1} D(T, X_i) - D(X_i, B_{i-1,j})
+                \end{equation}
+            \end{block}  
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.47\linewidth}
+            \begin{figure}[h!]
+                \centering
+                \includegraphics[width =\linewidth]{images/paper8/TSB.png}
+                \centering
+            \end{figure}
+        \end{minipage}
+    \end{minipage}
+\end{frame}
 
+\begin{frame}{METHODS - Tracking With Updating}
+    To evaluate the correspondence of an $X_i^+$ patch, a \emph{Trust Score s} is calculated. The score $s$ will be compared with two thresholds $\sigma_1$ and $\sigma_2$.
+    If $s\leq\sigma_1$ then a new positive patch $X{'}_i^+$, and consequently a new score $s'$, will be recalculated which will be replaced with the previous patch $X_i^+$ when $s'\geq\sigma_1$.
+    If $s\geq\sigma_2$ then update the target template $T$ with $X_i^+$.
+    \begin{equation}\label{distanceFunc}
+        X_i = \argmin_{X_{i,k} \in S_i}d(T,X_{i,k}, \{B_{i-1,j}\}^M_{j=1})
+    \end{equation}
+    \begin{equation}\label{newX}
+        X'_i = \argmax_{X_{i,k} \in S_i}m(T,X_{i,k})
+    \end{equation}
 \end{frame}
+
+\begin{frame}{EXPERIMENTS}
+    The experiments were conducted on four different types of datasets: 
+    OTB-2013, OTB-100, VOT-2015 and VOT-2016. The metrics used to 
+    evaluate the performance of all existing methods, including the one 
+    proposed, are accuracy, Area-Under-the-Curve (AUC), 
+    Expected-Average-Overlap (EAO) and robustness.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = \linewidth]{images/paper8/metrics.png}
+        \centering
+    \end{figure}
+\end{frame}
+
+\begin{frame}{EXPERIMENTS - AUC score on distractors}
+    Target tracking can be onerous when there are elements such as 
+    distractors in the scene. These lead most trackers to fail. The 
+    re-verification and re-detecting operations were essential to reduce this 
+    problem. In the table, the values in blue are the highest and are obtained 
+    from the best method, while those in red are placed in second position.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = \linewidth]{images/paper8/AUC.png}
+        \centering
+    \end{figure}
+\end{frame}
+
+\begin{frame}{CONCLUSION}
+    The proposed framework, from the results obtained in the benchmarks, seems 
+    to be the best. The achievement of these results were possible thanks to the 
+    integration of a verification and detecting method. The use of the TSB 
+    method was fundamental, which, by reducing the relative distance between 
+    the various patches, allowed for good model learning.
+\end{frame}

### 2021-04-17 papers/paper_9.tex
start paper9

\section{Similar Face Recognition Using the IE-CNN Model}

\begin{center}
    \author{
    An-Ping Song,
    Qian Hu,
    Xue-Hai Ding,
    Xin-Yi Di,
    Zi-Heng Song
    }
\end{center}

\begin{center}
    \emph{DIGITAL OBJECT IDENTIFIER}
\end{center}

\subsection{INTRODUCTION}

### 2021-04-17 papers/paper_9.tex
finish 9.3

@@
 \subsection{INTRODUCTION}
+Currently there are few datasets that provide a set of images with faces of 
+similar people, moreover there are few methods tested to be able to verify 
+the level of similarity. Two types of work are carried out in the following paper. 
+The first is based on proposing a procedure for creating a large dataset of 
+similar faces that requires a small amount of man-force to label the content. 
+In the second work, instead, an IE-CNN model is built which has the task 
+of improving the internal and external features of the face, increasing the 
+precision of face matching.
+
+\subsection{RELATED WORK}
+Unlike objects that may have a similar shape or color, the human face may 
+have similar external (located at head, chin and ears) or internal (eyes, nose 
+and mouth) structural features. However, many recognition algorithms tend 
+to discard external features and only work with internal ones. To understand 
+the importance of using both categories of features, just look at the image \ref{fig:features} 
+where there are similar faces (internal features) but different physical structures 
+of the skull (external features), or the opposite. The proposed model 
+(\emph{IE-CNN}) deals with improving facial features using a CNN network.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/paper9/importance.png}
+    \centering
+    \caption{(a) Shows the importance of internal features and (b) shows the importance of external features. The values are the cosine distances.}
+    \label{fig:features}
+\end{figure}
+
+\subsection{DATASET COLLECTION}
+The creation of the proposed similar-face dataset (SFD) consists of several steps.
+\begin{enumerate}
+    \item \emph{Collecting The Suitable Data Source}: the dataset used to collect the faces are LFW and CASIA-WebFace.
+The first contains a set of images of faces collected from the network, while the second has faces appropriately selected and labeled.
+    \item \emph{Determining the Similarity Between Two Faces Images}: to measure the similarity of two faces, the calculation of the distance $L2$ on image vectors is used.
+    \item \emph{Generating the Similar FaceDataset (SFD)}:if vectors with a short distance are found, then this distance will be stored.
+Based on the distance value, this can be associated with a grade type.
+The images belonging to the same grade, and therefore with the same distance, will be grouped.
+\end{enumerate}

### 2021-04-18 papers/paper_9.tex
finish 9.4.4

@@
 \begin{enumerate}
-    \item \emph{Collecting The Suitable Data Source}: the dataset used to collect the faces are LFW and CASIA-WebFace.
-The first contains a set of images of faces collected from the network, while the second has faces appropriately selected and labeled.
-    \item \emph{Determining the Similarity Between Two Faces Images}: to measure the similarity of two faces, the calculation of the distance $L2$ on image vectors is used.
-    \item \emph{Generating the Similar FaceDataset (SFD)}:if vectors with a short distance are found, then this distance will be stored.
-Based on the distance value, this can be associated with a grade type.
-The images belonging to the same grade, and therefore with the same distance, will be grouped.
+    \item \emph{Collecting The Suitable Data Source}: the dataset used to collect the 
+    faces are LFW and CASIA-WebFace. The first contains a set of images 
+    of faces collected from the network, while the second has faces 
+    appropriately selected and labeled.
+    \item \emph{Determining the Similarity Between Two Faces Images}: to measure 
+    the similarity of two faces, the calculation of the distance $L2$ on image 
+    vectors is used.
+    \item \emph{Generating the Similar FaceDataset (SFD)}:if vectors with a short distance 
+    are found, then this distance will be stored. Based on the distance 
+    value, this can be associated with a grade type. The images belonging 
+    to the same grade, and therefore with the same distance, will be 
+    grouped.
 \end{enumerate}
+
+\subsection{NETWORK ARCHITECTURE AND TRAINING}
+\subsubsection{IE-CNN Module}
+The IE-CNN network takes care of having to extract the external and internal 
+fetures and to do this there are two modules arranged on two different 
+branches, one called EI-CNN branch and the other called trunk branch. The 
+latter produces an output $T (x)$ where $x$ represents the input that is weighed 
+down by a mask $F (x)$ of the same size. The result obtained represents 
+the input of the algorithm $H (x)$. The IE-CNN branch has a number of 
+convolutional layers $p$ equal to 3, while in the other branch the number of 
+convolutional layers $q$ is equal to 2. For the construction of the trunk branch 
+a pre-activation Residual Unit is used \cite{0902694026}, while in the other branch 
+a customized large-size pre-activation Residual Unit is used. Other optimizations 
+have been added for the model to achieve good performance.
+
+\subsubsection{Pre-Activation Residual Unit}
+IE-CNN training is carried out using the Stochastic Gradient Descent (SGD). 
+Batch normalization and the ReLu activation function are used and both 
+operate before the convolution operation with the aim of speeding up training 
+and reducing the problem of covariates shift.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/paper9/architecture.png}
+    \centering
+    \caption{(a) Structure of pre-activation residual unit (b) the large-size one}
+    \label{fig:ResidualUnit}
+\end{figure}
+
+\subsubsection{Architecture}
+The IE-CNN branch structure is the one shown in figure \ref{fig:IE-CNN ARCHITECTURE}. The local pathway 
+is used to extract internal features and to improve fine-grained recognition 
+performance. The global pathway instead captures the external features. 
+The integration of all these features is carried out with a max-out merger 
+strategy.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/paper9/IE-CNN.png}
+    \centering
+    \caption{IE-CNN branch.}
+    \label{fig:IE-CNN ARCHITECTURE}
+\end{figure}
+
+\subsubsection{Framework of the proposed training method}
+The proposed model maps each image in a Euclidean space where, through 
+the use of the distance L2, its similarity will be established. Following the 
+\emph{LMNN} method \cite{0902694039}, three sets of images are created:
+\begin{enumerate}
+    \item $x^o$ (\emph{original}): represents the image of the face of a single individual;
+    \item $x^p$ (\emph{positive}): represents the remaining images of the same individual;
+    \item $x^n$ (\emph{positive}): represent the images of the faces of the other different 
+    individuals.
+\end{enumerate}
+The aim is to have smaller Euclidean distances between $x^o$ and $x^p$. The 
+input of the network consists of mini-batches, composed of images of positive 
+and negative faces, composed of a few images useful for obtaining a better 
+convergence during the descent of the stochastic gradient. In order to select 
+the best set triples useful for training, the strategy to be used is to consider 
+a $\theta$ margin in which the negative images $x^n$  will be found. Positive and 
+negative image sets that have maximum distance will be chosen. 
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.4\linewidth]{images/paper9/SET.png}
+    \centering
+    \caption{High-dimensional space.}
+    \label{fig:HDS}
+\end{figure}
+
+The following are the steps performed on each original image $x^o$:
+\begin{enumerate}
+    \item Pre-processing: performed by a pre-trained CNN;
+    \item Features enchancement: both external and internal;
+    \item Mapping: in high-dimensional space.
+\end{enumerate}

### 2021-04-18 papers/paper_9.tex
finish 9.5.3

@@
 \end{enumerate}
+
+\subsection{EXPERIMENTAL RESULTS AND ANALYSIS}
+\subsubsection{Experiment on feature map fusion in IE-CNN branch}
+There are two methods for merging the outputs generated by the two pathways. 
+The first, called $f_1$, performs a concatenation, while the second, called 
+$f_2$, performs an element-wise sum. Table \ref{testAccuracyIE-CNN} shows the test accuracy, adopting 
+the two merger strategies, on the two LFW and CASIA-WebFace datasets. 
+As we can see, $f_1$ achieves the best score but on the other hand, due to the 
+increase in parameters, this fusion method is time-consuming and requires a 
+high computational cost.
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{|c|c|c|c|}
+        \hline
+        \bfseries{Fusion Strategy} & \bfseries{Operate Type} & \bfseries{LFW} &\bfseries{CASIA-WebFace}\\
+        \hline
+        $f_1$ & concatenate & \bfseries{96.23} & \bfseries{84.35}\\
+        \hline
+        $f_2$ & element-wise sum & 94.80 & 83.83\\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{The test accuracy (\%) on LFW and CASIA-WebFace of IE-CNN branch with different fusion strategy.}
+    \label{testAccuracyIE-CNN}
+\end{table}
+
+\subsubsection{Experimental Evaluation Index}
+In order to evaluate the proposed method, two metrics are used: sensitivity (true positive rate) and accuracy.
+Another custom evaluation method used is that of \emph{Top1 \& Top5 precision}.
+In this metric $N$ represents the total number of images of a single individual, $N_1$ represents the number of images most similar (Grade1) while $N_5$ represent the least similar images (Grade5), therefore the precision is calculated as below:
+\begin{equation}
+    Precision_{top1}= \frac{N_1}{N}
+\end{equation}
+\begin{equation}
+    Precision_{top5}= \frac{N_5}{N}
+\end{equation}
+
+\subsubsection{Experiments on LFW and CASIA-WebFace}
+Another framework that has achieved good results in the field of similarity 
+recognition is \emph{Inception-Resnet-v2} \cite{0902694022}. The performance of this method was 
+compared with that of the proposed method. The triples used to train the 
+models are identical (same original images, positive and negative). The number 
+of images taken are divided into positive and negative. The accuracy and 
+sensitivity achieved by both methods is visible in the image \ref{fig:compareV2}. Looking at 
+the results, the accuracy and sensitivity achieved by the model are higher 
+than those achieved by v1.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/paper9/comparisonV2.png}
+    \centering
+    \caption{Comparison between v2 and the proposed methods on LFW and CASIA-WebFace datasets.}
+    \label{fig:compareV2}
+\end{figure}

### 2021-04-18 papers/paper_9.tex
finish paper 9

@@
 \end{figure}
+
+\subsubsection{Top1\&Top5 Precision Experiments Under Different Global Scopes}
+Comparisons were also made on the two personal Top1 \& Top5 precision 
+metrics. The results obtained by both methods are those shown in table \ref{T12}.
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{|c|cc|cc|}
+        \hline
+        \multirow{2}{*}{Method} & \multicolumn{2}{c|}{LFW} & \multicolumn{2}{c|}{CASIA-WebFace}\\
+        & Top5-acc & Top1-acc & Top5-acc & Top1-acc\\
+        \hline
+        v2 & 96.96 & 93.63 & 85.97 & 78.24\\
+        \hline
+        proposed & \bfseries{99.20} & \bfseries{98.86} & \bfseries{93.31} & \bfseries{84.92}\\
+        \hline    
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Top1\&Top5 Precision (\%) between two methods.}
+    \label{T12}
+\end{table}
+
+\subsubsection{Experiments On Similar Fase Dataset (SFD)}
+In this experiment, the performance of another method called DeepID2+ \cite{0902694017} 
+was also verified. The reference dataset in this case is just SFD. The experiment 
+is conducted with images in which there are similar faces, divided by 
+degrees. Also in this case accuracy and sensitivity are the metrics considered. 
+In table \ref{SFDCompMeth} you can see the results obtained by all the models. As we 
+can see, the lower the similarity level (towards grade 5), the higher the levels 
+of accuracy and true positive rate achieved by the methods. The proposed 
+method, however, managed to obtain the best performances also in this experiment. 
+his Thighlights the importance of using external features that are 
+not considered by the other methods.
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{max width=\textwidth}
+    \begin{tabular}{|c|ccccc|}
+        \hline
+        \multirow{2}{*}{Method} & \multicolumn{5}{c|}{Similar Face Dataset (SFD)}\\
+        & \RN{1} & \RN{2} & \RN{3} & \RN{4} & \RN{5}\\
+        \hline
+        DeepID2+ acc. & 49.73 & 59.75 & 58.64 & 64.37 & 66.33\\
+        DeepID2+ tpr. & 71.77 & 78.08 & 76.28 & 81.77 & 83.17\\
+        \hline
+        v2 acc. & 42.81 & 54.75 & 55.64 & 66.97 & 68.22\\
+        v2 tpr. & 63.33 & 70.00 & 65.33 & 71.67 & 68.08\\
+        \hline
+        proposed acc. & \bfseries{78.29} & \bfseries{83.19} & \bfseries{82.19} & \bfseries{86.11} & \bfseries{86.40}\\
+        proposed tpr. & \bfseries{79.17} & \bfseries{83.33} & \bfseries{79.67} & \bfseries{85.67} & \bfseries{84.67}\\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Comparison abount v2, DeepID+ and proposd methods on SFD dataset}
+    \label{SFDCompMeth}
+\end{table}
+
+\subsubsection{Supplementary Experiment on SFD}
+The last experiment is carried out only between the v2 method, which does 
+not use external features, and the one proposed. The aim is to see which of 
+the two can best distinguish the similarities of faces. The values shown in the 
+image \ref{fig:fei} represent the L2 distance between the upper and lower image. It can 
+be seen that for v2, in all three images, the same face always appears, while 
+the proposed method, thanks to the combination of external and internal 
+features, manages to distinguish both people.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/paper9/features.png}
+    \centering
+    \caption{The importance of external and internal features.}
+    \label{fig:fei}
+\end{figure}
+
+\subsection{CONCLUSION}
+What appears strange is that the greater the similarity between two faces, 
+the lower the recognition accuracy achieved by all the models. Even if the 
+addition of external and internal features represent a benefit for the purpose 
+of recognition, at the computation level this operation turns out to be expensive 
+in the training phase even if it is lightened by the use of mini-batches 
+(triple) and the various optimizations of the network.

### 2021-04-18 slides/slides_paper9.tex
slide paper9

\section{Paper 9}
\subsection{\emph{"Similar Face Recognition Using the IE-CNN Model"}}

\begin{frame}{INTRODUCTION}
    Currently there are few datasets that provide a set of images with faces of 
    similar people, moreover there are few methods tested to be able to verify 
    the level of similarity. Two types of work are carried out in the following paper. 
    The first is based on proposing a procedure for creating a large dataset of 
    similar faces that requires a small amount of man-force to label the content. 
    In the second work, instead, an IE-CNN model is built which has the task 
    of improving the internal and external features of the face, increasing the 
    precision of face matching.
\end{frame}

\begin{frame}{RELATED WORK}
    Internal and external features are particularly important in recognizing a 
    subject. The proposed method uses both of them unlike the other 
    recognition algorithms. If used separately, the algorithm could associate 
    two different individuals with the same identity.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.6\linewidth]{images/paper9/importance.png}
        \centering
        \caption{(a) Shows the importance of internal features and (b) shows the importance of external features. The values are the cosine distances.}
        \label{fig:features}
    \end{figure} 
\end{frame}

\begin{frame}{DATASET COLLECTION}
    One of the purposes of this paper is to create a dataset containing similar faces called dataset-similar-face (DSF), in order to test the proposed IE-CNN recognition model with other models. To create the dataset, the following steps were performed:
    \begin{enumerate}
        \item \emph{Collecting The Suitable Data Source}: from LFW and CASIA-WebFace datasets.
        \item \emph{Determining the Similarity Between Two Faces Images}: with distance $L2$ on image vectors.
        \item \emph{Generating the Similar FaceDataset (SFD)}: with images classified in different Grades.
    \end{enumerate}
\end{frame}

\begin{frame}{NETWORK ARCHITECTURE AND TRAINING}
    This paper proposes IE-CNN model which contains two modules to 
    extract internal (local pathway) and external (global pathway) features. 
    The outputs, generated by both pathways, will be merged with a 
    concatenation operation to create a single feature map.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.8\linewidth]{images/paper9/IE-CNN.png}
        \centering
        \caption{IE-CNN Architecture.}
        \label{fig:IE-CNN ARCHITECTURE}
    \end{figure}
\end{frame}

### 2021-04-18 papers/paper_9.tex
finish slide paper9

@@
 \subsubsection{Experimental Evaluation Index}
-In order to evaluate the proposed method, two metrics are used: sensitivity (true positive rate) and accuracy.
-Another custom evaluation method used is that of \emph{Top1 \& Top5 precision}.
-In this metric $N$ represents the total number of images of a single individual, $N_1$ represents the number of images most similar (Grade1) while $N_5$ represent the least similar images (Grade5), therefore the precision is calculated as below:
+In order to evaluate the proposed method, two metrics are used: sensitivity 
+(true positive rate) and accuracy. Another custom evaluation method used 
+is that of \emph{Top1 \& Top5 precision}. In this metric $N$ represents the total 
+number of images of a single individual, $N_1$ represents the number of images 
+most similar (Grade1) while $N_5$ represent the least similar images (Grade5), 
+therefore the precision is calculated as below:
 \begin{equation}
@@
 in the training phase even if it is lightened by the use of mini-batches 
-(triple) and the various optimizations of the network.
+(triplet) and the various optimizations of the network.

### 2021-04-18 slides/slides_paper9.tex
finish slide paper9

@@
 \begin{frame}{DATASET COLLECTION}
-    One of the purposes of this paper is to create a dataset containing similar faces called dataset-similar-face (DSF), in order to test the proposed IE-CNN recognition model with other models.
-To create the dataset, the following steps were performed:
+    One of the purposes of this paper is to create a dataset containing similar 
+    faces called similar-face-dataset (SFD), in order to test the proposed 
+    IE-CNN recognition model with other models. To create the dataset, the 
+    following steps were performed:
     \begin{enumerate}
@@
 
-\begin{frame}{NETWORK ARCHITECTURE AND TRAINING}
+\begin{frame}{IE-CNN NETWORK - ARCHITECTURE}
     This paper proposes IE-CNN model which contains two modules to 
@@
 \end{frame}
+
+\begin{frame}{IE-CNN NETWORK - TRAINING}
+    Triplets are used to train the network, each consisting of:
+    \begin{enumerate}
+        \item $x^o$ (\emph{original}): represents the image of the face of a single individual;
+        \item $x^p$ (\emph{positive}): represents the remaining images of the same individual;
+        \item $x^n$ (\emph{positive}): represent the images of the faces of the other different 
+        individuals.
+    \end{enumerate}
+    The aim is to have smaller Euclidean distances between $x^o$ and $x^p$. The 
+    search for these triplets can be traced back to an optimization problem.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width = 0.3\linewidth]{images/paper9/SET.png}
+        \centering
+        \caption{High-dimensional space.}
+        \label{fig:HDS}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{EXPERIMENTAL - LFW and CASIA-WebFace datasets}
+    \begin{minipage}{\linewidth}
+        \centering
+        \begin{minipage}{0.45\linewidth}
+            \begin{figure}[h!]
+                \centering
+                \includegraphics[width = \linewidth]{images/paper9/comparisonV2.png}
+                \centering
+                \caption{Comparison between v2 and the proposed methods on LFW and CASIA-WebFace datasets.}
+                \label{fig:compareV2}
+            \end{figure}
+            \begin{table}[h!]
+                \centering
+                \begin{adjustbox}{max width=\textwidth}
+                \begin{tabular}{|c|cc|cc|}
+                    \hline
+                    \multirow{2}{*}{Method} & \multicolumn{2}{c|}{LFW} & \multicolumn{2}{c|}{CASIA-WebFace}\\
+                    & Top5-acc & Top1-acc & Top5-acc & Top1-acc\\
+                    \hline
+                    v2 & 96.96 & 93.63 & 85.97 & 78.24\\
+                    \hline
+                    proposed & \bfseries{99.20} & \bfseries{98.86} & \bfseries{93.31} & \bfseries{84.92}\\
+                    \hline    
+                \end{tabular}
+                \end{adjustbox}
+                \label{T12}
+            \end{table}
+        \end{minipage}
+        \hspace{0.05\linewidth}
+        \begin{minipage}{0.45\linewidth}
+            In order to evaluate the proposed method, two metrics are used: sensitivity 
+            (true positive rate) and accuracy. Another custom evaluation method used 
+            is that of \emph{Top1 \& Top5 precision} (\%) (high is better). The 
+            comparison is made with the Inception-Resnet-v2 model on the LFW and 
+            CASIA-WebFace datasets.
+        \end{minipage}
+    \end{minipage}
+
+\end{frame}
+
+\begin{frame}{EXPERIMENTAL - Similar Face Dataset (SFD)}
+    In this experiment, the performance of another method called DeepID2+ 
+    was also verified. The reference dataset in this case is just SFD. The experiment 
+    is conducted with images in which there are similar faces, divided by 
+    degrees. Also in this case accuracy and sensitivity are the metrics considered.
+    \begin{table}[h!]
+        \centering
+        \begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{|c|ccccc|}
+            \hline
+            \multirow{2}{*}{Method} & \multicolumn{5}{c|}{Similar Face Dataset (SFD)}\\
+            & \RN{1} & \RN{2} & \RN{3} & \RN{4} & \RN{5}\\
+            \hline
+            DeepID2+ acc. & 49.73 & 59.75 & 58.64 & 64.37 & 66.33\\
+            DeepID2+ tpr. & 71.77 & 78.08 & 76.28 & 81.77 & 83.17\\
+            \hline
+            v2 acc. & 42.81 & 54.75 & 55.64 & 66.97 & 68.22\\
+            v2 tpr. & 63.33 & 70.00 & 65.33 & 71.67 & 68.08\\
+            \hline
+            proposed acc. & \bfseries{78.29} & \bfseries{83.19} & \bfseries{82.19} & \bfseries{86.11} & \bfseries{86.40}\\
+            proposed tpr. & \bfseries{79.17} & \bfseries{83.33} & \bfseries{79.67} & \bfseries{85.67} & \bfseries{84.67}\\
+            \hline
+        \end{tabular}
+        \end{adjustbox}
+        \caption{Comparison abount v2, DeepID+ and proposd methods on SFD dataset}
+        \label{SFDCompMeth}
+    \end{table}
+\end{frame}
+
+\begin{frame}{CONCLUSION}
+    What appears strange is that the greater the similarity between two faces, 
+    the lower the recognition accuracy achieved by all the models. Even if the 
+    addition of external and internal features represent a benefit for the purpose 
+    of recognition, at the computation level this operation turns out to be expensive 
+    in the training phase even if it is lightened by the use of mini-batches 
+    (triplet) and the various optimizations of the network.
+\end{frame}

### 2021-04-19 papers/paper_10.tex
finish 10.1

\section{Convolutional Neural Networks for Risso’s Dolphins Identification}

\begin{center}
    \author{
    Rosalia Maglietta,
    Vito Renò,
    Rocco Cacioppoli,
    Emanuele Seller,
    Stefano Bellomo,
    Francesca Cornelia Santacesaria,
    Roberto Colella,
    Giulia Cipriano,
    Ettore Stella,
    Karin Hartman,
    Carmelo Fanizza,
    Giovanni Dimauro,
    \emph{(Member, IEEE)},
    Roberto Carlucci
    }
\end{center}

\begin{center}
    \emph{DIGITAL OBJECT IDENTIFIER}
\end{center}

\subsection{INTRODUCTION}
Photo identification is a technique that can be used on marine species in 
order to safeguard the environment and the various existing species. The 
marine species on which this study is based are cetaceans, in particular the 
Risso's dolphin species Grampus Griseus (Fig. \ref{fig:Risso}). This species is the least 
known and is present in greater numbers in Mediterranean waters. In order to 
recognize a dolphin, the scars present on their body and on the dorsal fin are 
used, representing the "fingerprints" useful for identifying them. To achieve 
this, the RUSPool algorithm is used which aims to perform an intelligent 
merge, through a custom filter, of the m RUSBoost classifiers. Subsequently, 
a new methodology called Neural Network Pool (NNPool) will be used, also 
useful for recognizing only the Risso species of dolphins. This algorithm is 
composed of a pool of CNNs useful for achieving the final goal. The chosen 
output will be dictated by the major voting of all these networks. Finally, 
the results obtained will be compared with those obtained by the RusPool 
algorithm, used for the same purpose.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper10/Risso.png}
    \centering
    \caption{Risso’s dolphins Grampus Griseus}
    \label{fig:Risso}
\end{figure}

### 2021-04-19 papers/paper_10.tex
finish 10.2.2

@@
 \end{figure}
+
+\subsection{MATERIAL AND METHODS}
+\subsubsection{Survey Area and Data Collection}
+A dataset was created containing all the sightings of dolphins that took place 
+in the years between 2013 and 2018, in the Gulf of Taranto. The collection 
+contains a total of 93 different labeled Risso dolphins, but sadly only 23 of 
+these were selected as each has at least 15 images on each side of the fin. 
+Through the use of an $f_R$ mask filter, 70\% of each image consists of the 
+dolphin fin alone, excluding external elements such as the sea. This filter 
+led to consider a new dataset containing 433 images belonging to the 23 
+dolphins. The $D_{NN}$ dataset used to train CNNs contains images that have 
+not been pre-processed by the $f_R$ filter. This latest dataset is made up of 
+582 images belonging to 28 different dolphins. A validation dataset was also 
+created containing 300 images of known and unknown Risso's dolphins.
+
+\subsubsection{RUSBoost Methodology}
+The RUSBoost algorithm has the task of identifying each dolphin and predicting 
+its label. The application of this algorithm can be schematized in 
+figure \ref{fig:RUSBoost}. The architecture consists of 3 main phases:
+\begin{enumerate}
+    \item \emph{Pre-processing}: creation of the black and white image containing the 
+    extracted fin.
+    \item \emph{Features Extraction}: build the 3-dimensional super-SIFT descriptor. 
+    \item \emph{Classification}: application of the RUSBoost algorithm.
+\end{enumerate}
+RUSBoost consists of two other types of algorithms: Random Under-Sampling 
+(RUS) and Adaboost \cite{0907875811}. RUSBoost training takes place by carrying out 
+cross-validation, one-vs-all, on a set of labeled data of the 23 dolphins considered.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/paper10/RUSBoost.png}
+    \centering
+    \caption{Experimental methodology based on RUSBoost.}
+    \label{fig:RUSBoost}
+\end{figure}
+
+\subsubsection{RUSPool}

### 2021-04-19 papers/paper_10.tex
finish 10.2.4

@@
 (RUS) and Adaboost \cite{0907875811}. RUSBoost training takes place by carrying out 
-cross-validation, one-vs-all, on a set of labeled data of the 23 dolphins considered.
+cross-validation, one against all, on each of the 23 dolphins taken into consideration, 
+therefore $M_i$ classifiers will be created, with $i = 1,2,...,23$.
 \begin{figure}[h!]
@@
 \subsubsection{RUSPool}
+The RUSPool algorithm aims to identify known dolphins among all and unknown 
+ones. This task is done by using the previous 23 already trained 
+RUSBoosts classifiers (Fig. \ref{fig:RUSPool Arch}). Therefore, each image given as input to RUSPool 
+will have n super-SIFT descriptors associated with it and this new sample is 
+supplied as input to the RUSBoosts classifiers. The result returned by each 
+classifier will represent the prediction that a dolphin has been recognized or 
+not. The result obtained from the difference in these probabilities, if greater 
+than a threshold equal to $0.11$, will be taken into consideration, discarding 
+all other cases of uncertainty. The final output will be a vector $R$ where its 
+elements $r_i$ represent the percentage of positive predictions for each classifier 
+$M_i$ (Fig. \ref{fig:ri}). A filter is applied on the vector R to obtain the 
+prediction of the identity of a dolphin given in input.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.5\linewidth]{images/paper10/RUSPool Architecture.png}
+    \centering
+    \caption{RUSPool Architecture.}
+    \label{fig:RUSPool Arch}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.4\linewidth]{images/paper10/ri.png}
+    \centering
+    \caption{Example of RUSPool output. $r_i$ is the bumber of positive predicitons of the $M_i$ classifiers.}
+    \label{fig:ri}
+\end{figure}
+
+\subsubsection{Convolutional Neural Network}
+A convolutional neural network (CNN) is used. Its architecture is composed 
+of a triple sequence of Conv-ReLu-MaxPool layers (Fig. \ref{CNNDol}). The number of 
+parameters and images useful for training the network is less than the most 
+widespread neural networks in the state of the art, thus reducing the problem 
+of overfitting. This architecture forms the previous NNPool network. The 
+dataset used is the one previously mentioned DNN.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/paper10/NNPool Architecture.png}
+    \centering
+    \caption{CNN Architecture build for each dolphin.}
+    \label{fig:CNNDol}
+\end{figure}
+
+\subsubsection{NNPool}

### 2021-04-20 papers/paper_10.tex
finish paper 10

@@
 dolphin fin alone, excluding external elements such as the sea. This filter 
-led to consider a new dataset containing 433 images belonging to the 23 
+led to consider a new dataset $D_R$ containing 433 images belonging to the 23 
 dolphins. The $D_{NN}$ dataset used to train CNNs contains images that have 
@@
 A convolutional neural network (CNN) is used. Its architecture is composed 
-of a triple sequence of Conv-ReLu-MaxPool layers (Fig. \ref{CNNDol}). The number of 
+of a triple sequence of Conv-ReLu-MaxPool layers (Fig. \ref{fig:CNNDol}). The number of 
 parameters and images useful for training the network is less than the most 
@@
     \centering
-    \includegraphics[width = 0.8\linewidth]{images/paper10/NNPool Architecture.png}
+    \includegraphics[width = 0.7\linewidth]{images/paper10/NNPool Architecture.png}
     \centering
@@
 \subsubsection{NNPool}
+The proposed strategy is called NNPool. This strategy is based on the composition 
+of several CNN networks equal to the number of dolphins present in 
+the $D_{NN}$ dataset. The output generated by NNPool is a probability vector \emph{P} 
+(Fig. \ref{fig:NNPool output}) where, if there is only one probability $p_i\in P > 51\%$ , then the new 
+photo given in input will be labeled as known, otherwise it will be labeled as 
+unknown.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.4\linewidth]{images/paper10/NNPool output.png}
+    \centering
+    \caption{Example of NNPool output. $p_i$ is the probabilities of the fin given in input to belong to the dolphin reported to the $CNN_i$.}
+    \label{fig:NNPool output}
+\end{figure}
+
+\subsubsection{Evaluation Metrics}
+The metrics used to evaluate the performance of the proposed model are as follows:
+\begin{enumerate}
+    \item \emph{Accuracy}: percentage of correct predictions.
+    \item \emph{Sensitivity}: percentage of positive labels considered as positive.
+    \item \emph{Specificity}: percentage of negative labels considered as negative.
+\end{enumerate}
+Images labeled as negative will correspond to unknown classes.
+
+\subsection{EXPERIMENTS AND RESULTS}
+To compare the results obtained by NNPool you must first create the RUSBoost 
+model. This model uses the $D_R$ dataset on which the Cross-Validation 
+technique is used to train the model. The quality of each image can affect 
+the model. To solve this problem, a method called Perception based Image 
+Quality Evaluator (PIQE scores) is used which determines the type of quality 
+(Excellent, Good, Fair, Poor, Bad) based on the score obtained on each 
+image (Low is better). The results obtained by RUSBoost are those shown 
+in figure \ref{fig: RUSBoostPerf}. Unfortunately, the performance of RUSBoost depends on 
+the number of images available for training and the quality of each of them. The 
+RUSPool model is then created to compare its performance. This time the 
+$D_v$ dataset is used. The accuracy, sensitivity and specificity values achieved 
+are visible in table \ref{RUSPoolPerf}. At this point, the performance of CNN networks on 
+the $D_{NN}$ dataset is also evaluated. To evaluate the performance of a CNN 
+network, and therefore of NNpool, the Cross-Validation strategy is used with 
+a number of $n_{cv}$ cycles equal to 10 on a dataset divided into 2/3 of training 
+set and 1/3 of test set. The results are averaged across all the $n_{cv}$. Figure \ref{fig: CNNNNPool perfromance} 
+shows the results obtained by every CNN network of NNPool which demonstrate 
+its superiority over RUSBoost. Since there are dolphins made up of 
+a different number of images, when the quantity of images exceeds 3.5\% the 
+sensitivity increases, otherwise it decreases. The strong point of the CNN 
+network is that it achieves good performance both in case there are many 
+low quality images and in case there are few high quality images. As for the 
+performances achieved by NNPool, these exceed that of RUSPool. Also regarding 
+the training and classification time (recognition of a single unknown 
+image), NNPool is less time-consuming than RUSPool.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/paper10/RUSBoost performance.png}
+    \centering
+    \caption{Performances of RUSBoost.}
+    \label{fig: RUSBoostPerf}
+\end{figure}
+\begin{table}[htbp]
+    \centering
+    \begin{adjustbox}{width=0.6\textwidth}
+    \begin{tabular}{|cccc|}
+        \hline
+        & Accuracy & Sensitivity & Specificity\\
+        \hline
+        RUSPool & 0.78 & 0.58 & 0.81\\
+        NNPool & 0.87 & 0.70 & 0.90\\
+        \hline
+    \end{tabular}
+    \end{adjustbox}
+    \caption{RUSPool and NNPool performance on the validation data set $D_v$}
+    \label{RUSPoolPerf}
+\end{table}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width = 0.8\linewidth]{images/paper10/NNPool performance.png}
+    \centering
+    \caption{Performances of every CNN network in NNPool.}
+    \label{fig: CNNNNPool perfromance}
+\end{figure}
+
+\subsection{CONCLUSION}
+In conclusion, it can be said that, among all the methods compared, the 
+proposed CNN network has better performances and more advantages. One 
+of the first is the non-interaction of the user, while following there is the factor 
+of the training and classification speed. Unfortunately, like many CNN-based 
+methods, the problem of the number of images, and their quality, still remains 
+open in fact by providing a low number of images, all with low quality, the 
+proposed algorithm will tend to have low performance in terms classification 
+of dolphins.

### 2021-04-20 slides/slides_paper10.tex
finish slides paper 10

\section{Paper 10}
\subsection{\emph{"Convolutional Neural Networks for Risso’s Dolphins Identification"}}

\begin{frame}{INTRODUCTION}
    Photo identification is a technique that can be used on marine species in 
    order to safeguard the environment and the various existing species. The 
    marine species on which this study is based are cetaceans, in particular the 
    Risso's dolphin species Grampus Griseus (Fig. \ref{fig:Risso}). In order to 
    recognize a dolphin, the scars present on their body and on the dorsal fin are 
    used, representing the "fingerprints" useful for identifying them. To 
    achieve this, a new network model called NNPool is introduced.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.5\linewidth]{images/paper10/Risso.png}
        \centering
        \caption{Risso’s dolphins Grampus Griseus}
        \label{fig:Risso}
    \end{figure}
\end{frame}

\begin{frame}{MATERIAL AND METHODS}
    The following work comes from the evolution of two other previously 
    created methods that use two different classification algorithms: 
    \emph{RUSBoost} \footfullcite{0907875812} and \emph{RUSPool}\footfullcite[]{0907875814}. Each model, including the one proposed, is 
    trained on a specific dataset, each of which represents the update of the 
    other. The datasets are as follows:
    \begin{enumerate}
        \item $D_R$: consisting of 433 images, used for training RUSBoost method;
        \item $D_V$: consisting of 300 images, used for training RUSPool method;
        \item $D_{NN}$: consisting of 582 images, used for training NNPool method;
    \end{enumerate}
    Each dataset contains more than one image belonging to the single 
    dolphin. Each of them is divided into training sets and test sets of 
    labeled images.
\end{frame}

\begin{frame}{MATERIAL AND METHODS - RUSBoost}
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.47\linewidth}
            RUSBoost consists of two other types of algorithms: Random Under-Sampling 
            (RUS) and Adaboost. RUSBoost training takes place by carrying out 
            cross-validation, one against all, on each of the 23 dolphins taken into consideration.
            \begin{enumerate}
                \item \emph{Pre-processing}: creation of the black and white image containing the 
                extracted fin.
                \item \emph{Features Extraction}: build the 3-dimensional super-SIFT descriptor. 
                \item \emph{Classification}: application of the RUSBoost algorithm.
            \end{enumerate}  
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width =\linewidth]{images/paper10/RUSBoost model.png}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}
\end{frame}

\begin{frame}{MATERIAL AND METHODS - RUSPool}
    The RUSPool algorithm aims to identify known dolphins among all and unknown 
    ones. This task is done by using the previous 23 already trained 
    RUSBoosts classifiers. Therefore, each image given as input to RUSPool 
    will have n super-SIFT descriptors associated with it and this new sample is 
    supplied as input to the RUSBoosts classifiers. The result returned by each 
    classifier will represent the prediction that a dolphin has been recognized or 
    not.In the output vector $R$, if there is an $r_i$ greater than a certain threshold, then the dolphin will be classified as known.
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.47\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width =\linewidth]{images/paper10/RUSPool Architecture.png}
                \centering
            \end{figure}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width = 0.5\linewidth]{images/paper10/ri.png}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}

\end{frame}

\begin{frame}{MATERIAL AND METHODS - NNPool}
    The proposed network architecture consists of 28 CNN networks, each of which is trained in recognizing a specific dolphin. If there is a single probability $p_i\in P > 51\%$ in the output vector $P$, then this input dolphin will be classified as known. Each song on the CNN network has the following architecture:
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.47\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width = \linewidth]{images/paper10/NNPool Architecture.png}
                \centering
                \caption{CNN Architecture build for each dolphin.}
                \label{fig:CNNDol}
            \end{figure} 
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width = 0.5\linewidth]{images/paper10/NNPool output.png}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}    
\end{frame}

\begin{frame}{EXPERIMENTS AND RESULTS - Metrics}
    The metrics used to evaluate the performance of the proposed model are as follows:
    \begin{enumerate}
        \item \emph{Accuracy}: percentage of correct predictions.
        \item \emph{Sensitivity}: percentage of positive labels considered as positive.
        \item \emph{Specificity}: percentage of negative labels considered as negative.
        \item \emph{PIQE}: determines the type of quality (Excellent, Good, Fair, Poor, Bad) (Low score is better).
    \end{enumerate}
    Images labeled as negative will correspond to unknown classes.
\end{frame}

\begin{frame}{EXPERIMENTS AND RESULTS - RUSPool Vs. NNPool}
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width = \linewidth]{images/paper10/RUSBoost performance.png}
                \centering
                \caption{Performances of every RUSBoost classifiers in RUSPool method.}
                \label{fig: RUSBoostPerf}
            \end{figure}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width =\linewidth]{images/paper10/NNPool performance.png}
                \centering
                \caption{Performances of every CNN network in NNPool method.}
                \label{fig: CNNNNPool perfromance}
            \end{figure}
        \end{minipage}
    \end{minipage}   
\end{frame}

\begin{frame}{CONCLUSION}
    In conclusion, it can be said that, among all the methods compared, the 
    proposed CNN network has better performances and more advantages. 
    One of the first is the non-interaction of the user, while following there is 
    the factor of the training and classification speed. Even having better 
    performance than RUSPool (Tab. \ref{RUSPoolPerf}), NNPool's CNNs networks have the 
    problem of the number of images and their quality, in fact by providing a 
    low number of images, all with low quality, the proposed algorithm will 
    tend to have low performance in terms classification of dolphins. The 
    strong point of the CNN network is that it achieves good performance 
    both in case there are many low quality images and in case there are few 
    high quality images.
    \begin{table}[htbp]
        \centering
        \begin{adjustbox}{width=0.6\textwidth}
        \begin{tabular}{|cccc|}
            \hline
            & Accuracy & Sensitivity & Specificity\\
            \hline
            RUSPool & 0.78 & 0.58 & 0.81\\
            NNPool & 0.87 & 0.70 & 0.90\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{RUSPool and NNPool performance.}
        \label{RUSPoolPerf}
    \end{table}
\end{frame}

### 2021-04-20 Introduction.tex
finish introduction

\section*{INTRODUCTION}
In recent years, the field of computer vision is becoming more and more important 
due to its various applications exercised in different areas such as 
intelligent surveillance and monitoring, recognition, self-driving cars, warehouse 
management, health and medicine, sports, drones and robotics. The 
goal of computer vision is to allow the computer to see, identify and process 
images, or videos, as it happens in human vision, providing adequate output. 
It is a multidisciplinary field that could be considered as a subfield of 
Artificial Intelligence (AI) and Machine Learning (ML). Computer vision is 
shifting from statistical methods to deep learning neural networks methods. 
Deep Learning (DL) is used in the domain of digital image processing to solve 
difficult problems. DL is largely based on Artificial Neural Networks (ANNs), 
a paradigm inspired by the functioning of the human brain. Just like the latter, 
it is made up of many computing cells, called "neurons", whose task 
is to carry out operations and interact with each other to make a decision. 
DL methods, such as Convolutional Neural Networks (CNNs, or ConvNet), 
improve prediction performance by using datasets and abundant computing 
resources. Thanks to their integration, it was possible to carry out visual 
recognition activities, based on the classification of images, localization, detection 
and semantic segmentation, all thanks to the use of kernels (also 
known as filters), which go to extract features useful in a given context. This 
has made CNN networks the main topic of deep learning algorithms in computer 
vision. Compression techniques based on the use of CNN networks and 
computer vision are widespread. These methods have the task of preserving 
space on existing media through the use of encodings with or without loss of 
quality. Object detection, for computer vision, is also one of the key factors 
in understanding the scene. In this regard, many segmentation algorithms 
have been proposed which aim to separate the foreground objects from the 
background. As with objects, recognition of a subject can also take place 
in multiple ways. Among these methods appear those that have the task 
of recognizing the gait of an individual and predicting information relating 
to identity, age and gender. Face recognition appears to be a difficult challenge 
when they appear to be similar. Also for this purpose, some methods 
have been designed to have models capable of distinguishing similar subjects 
from less similar ones. To date, the challenges that we try to overcome in 
computer vision, but especially in convolutional networks, are those related 
precisely to the images, their availability, useful for training the models, their 
quality and the possible associated labels. Unfortunately, there are still very 
few datasets with images useful for a particular purpose and many of their 
images appear to be of low quality. Multiple solutions have been found for 
this problem, one of the simplest, but expensive, is to use equipment such as 
good stereo cameras, high resolution cameras and tripods. Another solution 
to this problem is to use algorithms capable of improving images through the 
use of noise reduction or color costancy research techniques. The following 
paper is divided into ten sections where in each of these new methodologies 
are explained compared with those already existing in the state of the art, 
used in the field of computer vision. In order of presentation, the topics 
covered are: \emph{Salient structure, Superpixel, Compression, Color Constancy, 
Gait Recognition, Semantic Segmentation, Noise Removal, Tracking, Face 
Recognition and Identification}.

### 2021-04-20 Introduction.tex
finish

@@
 a paradigm inspired by the functioning of the human brain. Just like the latter, 
-it is made up of many computing cells, called "neurons", whose task 
+it is made up of many computing cells, called \emph{neurons}, whose task 
 is to carry out operations and interact with each other to make a decision. 

### 2021-04-21 slides/slides_paper1.tex
some update

@@
     The results obtained on different datasets \footfullcite{PASCAL-S, ECSSD, ASD}, were compared with those 
-    btained by the systems already existing at the state of the art.
+    obtained by the systems already existing at the state of the art.
     \begin{figure}[htbp]

### 2021-04-21 slides/slides_paper5.tex
some update

@@
 \begin{frame}{PROPOSED APPROACH - Identity Authentication}
-    Unlike the acknowledgment, the authentication problem aims to see if 
+    Unlike the recognition, the authentication problem aims to see if 
     two different inputs belong to the same subject. To do this, it is necessary 
@@
                     \end{adjustbox}
-                    \caption{Accuracy and F1-score (1 Task, + Sensor).}
+                    \caption{Accuracy and F1-score (+ Task, + Sensor).}
                     \label{table accuracy and F1 (+ Task, + Sensor)}

### 2021-04-21 slides/slides_paper9.tex
some update

@@
     The first is based on proposing a procedure for creating a large dataset of 
-    similar faces that requires a small amount of man-force to label the content. 
+    similar faces that requires a small amount of person-power to label the content. 
     In the second work, instead, an IE-CNN model is built which has the task 

### 2021-04-21 slides/slides_paper1.tex
add 1 slide to paper1

--- 2021-04-11 slides/slides_paper1.tex
@@
 
-\begin{frame}[t]{EXPERIMENTS}
-    The results obtained on different datasets \footfullcite{PASCAL-S, ECSSD, ASD}, were compared with those 
-    btained by the systems already existing at the state of the art.
+\begin{frame}{EXPERIMENTS - Fixation Prediction}
+    The fixation prediction indicates the likelihood with which a human is 
+    looking at a given position in the scene. There are several metrics that are 
+    used to evaluate the prediction such as Natural Scanpath Saliency (NSS) 
+    and ROC (AUC). In the following article the ROC method is mainly used, 
+    on three types of datasets, to compare the proposed system with others already 
+    existing at the state of the art, as shown in Fig. \ref{fig: ROC}.
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width = 1 \linewidth]{images/paper1/ROC.png}
+        \centering
+        \caption{ROC comparison.}
+        \label{fig: ROC}
+    \end{figure}
+    The computation of the CBSP takes into account this {\bfseries{center bias}}, 
+    without however losing the information on the other objects in the scene.
+\end{frame}
+
+\begin{frame}[t]{EXPERIMENTS - Salient Object Detection}
+    To compare the performance of the salient object detection, metrics such 
+    as Precision, Recall, F-score, Weighted F-score and MAE (Mean Absolute 
+    Error) were used. In precision and recall, HS and RF are the best, but in 
+    the F-score, CGVS($t_2$) whit center bias, is best. Without center bias, CGVS 
+    would achieve lower performance (CGVS'').
     \begin{figure}[htbp]
@@
         \caption{Metrics comparison.}
-        \label{fig: metrics}
     \end{figure}

### 2021-04-22 slides/slides_paper3.tex
some update
some fixes

@@
             \end{figure}
-            \begin{block}{Parameter optimizations}
+            \begin{block}{Parameters optimizations}
                 \small $$ \hat{\theta_1} = \argmin\limits_{\theta_1}||Re(\hat{\theta_2},Cr(\theta_1,x))-x||^2 $$
@@
             \end{figure}
-            \begin{block}{Parameter optimizations}
+            \begin{block}{Parameters optimizations}
                 \small $$ \hat{\theta_2} = \argmin\limits_{\theta_2}||Re(\hat{\theta_2},\hat{x}_m)-x||^2 $$
@@
     The performance comparison is made by citing various techniques present 
-    at the state of the art. A compression quality index ({\bfseries\emph{PSNR}}) and ù
+    at the state of the art. A compression quality index ({\bfseries\emph{PSNR}}) and 
     an image similarity index ({\bfseries\emph{SSIM}}) are used. What is really important to note 
@@
     the already used codecs such as \emph{JPEG}, \emph{JPEG2000} and \emph{BPG}, at different 
-    bit rates (\emph{bpp}) and quality factors (\emph{QS}). As for the execution times, in 
+    bit rates (\emph{bpp}) and quality factors (\emph{QF}). As for the execution times, in 
     terms of CPU / GPU, the proposed algorithm is faster than those already 

### 2021-04-22 slides/slides_paper4.tex
some update
some fixes

@@
     The only information available on the light source are: the "\emph{Spectral 
-    Power Distributions}" (SPD) and the "\emph{Spectral Reflectance}" (SR)
+    Power Distributions}" (SPD) and the "\emph{Spectral Reflectance}" (SR).
     Thanks to this information, we can obtain the existing chromaticity in the image 
@@
 \begin{frame}{EXPERIMENTAL RESULTS - Supervised methods}
-    Color constancy can also be calculated from convolutional neural networks (\emph{CCNs}) such as the one proposed in \footfullcite{0807099125}
+    Color constancy can also be calculated from convolutional neural 
+    networks (\emph{CNNs}) such as the one proposed in \footfullcite{0807099125}. 
     \begin{figure}[htbp]
@@
         \centering
-        \caption{Camera Independence with CCM on $ 1^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
+        \caption{Camera Independence with CCM. Mean, Median and Maximum RAE of CNN. ($T_r$:N, V:M is the best configuration)}
         \label{fig:CNNtec1}
@@
                 \includegraphics[width=\linewidth]{images/paper4/25tech2.png}
-                \caption{\small Camera Independence on $ 2^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
+                \caption{\small Camera and Scene Independence. Mean, Median and Maximum RAE of CNN. ($T_r$:N+M, V:C, $T_e$: C$2^{nd}$)}\label{fig:1}
             \end{figure}
@@
                 \centering
-                \includegraphics[width=0.8\linewidth]{images/paper4/25tech3.png}
-                \caption{\small Camera Independence on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
+                \includegraphics[width=0.7\linewidth]{images/paper4/25tech3.png}
+                \caption{\small Camera  and Scene Independence from Single camera. Mean, Median and Maximum RAE of CNN. ($T_r$+V: C$2^{nd}$)}\label{fig:1}
                 \centering
@@
     an algorithm, or a model based on CNN, in the search of camera/scene-independece. 
-    Achieving this goal can also be done using a CNN if the CMM process is 
+    Achieving this goal can also be done using a CNN if the CCM process is 
     applied to its input set. It is necessary to specify that, in order to 

### 2021-04-22 slides/slides_paper7.tex
some update
some fixes

@@
 
-\begin{frame}{RELATED WORK - What types of image noise?}
+\begin{frame}{RELATED WORK - What types of image noises?}
     The noises analyzed in this paper are mainly two categories of Gaussian 
@@
     where $ n_k $ is the \emph{k}-th noise component with probability density function (PDF) 
-    $ p_k $ and $ r_k $ are the unknown mixture ratios and thei sum is equal to 
+    $ p_k $ and $ r_k $ are the unknown mixture ratios and their sum is equal to 
     1. Each type of noise has a standard deviation ($\sigma$) which indicates the 
@@
     proposed, in image reconstruction and Gaussian mixed-noise removal, one 
-    are visible in figure \ref{fig:GMNComp} and table \ref{indexCompare}. The set test images were taken from 
+    are visible in figure \ref{fig:GMNComp} and table \ref{indexCompare}. The test set images were taken from 
     the BSDS100 dataset.
@@
         \centering
-        \includegraphics[width = 0.7\linewidth]{images/paper7/crop result.png}
+        \includegraphics[width = 0.6\linewidth]{images/paper7/crop result.png}
         \centering

### 2021-04-22 slides/slides_paper8.tex
some fixes

@@
     The proposed framework, called Ensemble Multi Deep Stream Similarity 
-    Learnining Tracking (EMDSLT), is composed of some netwroks. Those 
+    Learnining Tracking (EMDSLT), is composed of some networks. Those 
     in blue are fully-convolutional networks while those in red are useful for 

### 2021-04-23 papers/paper_8.tex
finish slides of paper8
finish 9.3
some fixes

@@
     \label{fig:EMDSLT}
-\end{figure}.
+\end{figure}
 
@@
     the OTB-2013 dataset, when these elements are present. The values 
-    in blue are the highest and are obtained from the best method, while 
-    those in red are placed in second position.
+    in red are the highest and are obtained from the best method, while 
+    those in blue are placed in second position.
     \begin{figure}[h!]
@@
     \end{figure}
-    \item \emph{Qualitative Evaluation}: The use of the Template-Searching-Background (TSB), allows you to use the background patches to train the model (Fig.\ref{fig:TSBMin}).
-This method helps to minimize the relative distance $d(\cdot)$ (\ref{distanceFunc}) which translated into other words means bringing the target template closer to the $X_i^+$ samples and at the same time moving the background distractors $B_i$ away from the positive sample.
-This method allows for better performance than existing state-of-the-art models.
-A visual example of comparison of the trackers made by the different methods, including the one proposed, is visible in figure \ref{fig:qualitativeTracking}.
+    \item \emph{Qualitative Evaluation}: The use of the Template-Searching-Background 
+    (TSB), allows you to use the background patches to train the model 
+    (Fig.\ref{fig:TSBMin}). This method helps to minimize the relative distance $d(\cdot)$ (\ref{distanceFunc}) 
+    which translated into other words means bringing the target template 
+    closer to the $X_i^+$ samples and at the same time moving the background 
+    distractors $B_i$ away from the positive sample. This method allows for 
+    better performance than existing state-of-the-art models. A visual example 
+    of comparison of the trackers made by the different methods, 
+    including the one proposed, is visible in figure \ref{fig:qualitativeTracking}.
     \begin{figure}[h!]
@@
 The proposed framework, from the results obtained in the benchmarks, seems 
-to be the best. The achievement of these results were possible thanks to the 
-integration of a verification and detecting method. The use of the TSB 
-method was fundamental, which, by reducing the relative distance between 
-the various patches, allowed for good model learning.
+to be the best in solving the problem of distractors. The achievement of these 
+results were possible thanks to the integration of a verification and detecting 
+method. The use of the TSB method was fundamental, which, by reducing 
+the relative distance between the various patches, allowed for good model 
+learning.

### 2021-04-23 slides/slides_paper5.tex
some fixes

@@
     must be translated into probabilities that will be useful in order to 
-    calculate two indices (Area Under Curve (AUC), Equal-Error-Rate 
+    calculate two indexs (Area Under Curve (AUC), Equal-Error-Rate 
     (EER)) that will be useful for evaluating the CNN network.
@@
                 \end{adjustbox}
-                \caption{Accuracy and F1-score (1 Task, 1 Sensor).}
+                \caption{Accuracy and F1-score (1 Task, 1 Sensor). 3 Tasks - 2 Sensors - 6 CNNs.}
                 \label{table accuracy and F1 (1 Task - 1 Sensor)}
@@
                 \end{adjustbox}
-                \caption{Accuracy and F1-score (1 Task, + Sensor).}
+                \caption{Accuracy and F1-score (1 Task, + Sensor). 1 CNN for each Task.}
                 \label{table accuracy and F1 (1 Task, + Sensor)}
@@
                     \end{adjustbox}
-                    \caption{Accuracy and F1-score (+ Task, 1 Sensor).}
+                    \caption{Accuracy and F1-score (+ Task, 1 Sensor). 2 CNNs, one for each 3 Tasks.}
                     \label{table accuracy and F1 (more Task - 1 Sensor)}
@@
                     \end{adjustbox}
-                    \caption{Accuracy and F1-score (+ Task, + Sensor).}
+                    \caption{Accuracy and F1-score (+ Task, + Sensor). Only 1 CNN for all Tasks.}
                     \label{table accuracy and F1 (+ Task, + Sensor)}
